### 2020-10-14 paper/paper_v1.tex
standard commit

\documentclass[aps,prb,reprint,noeprint,superscriptaddress]{revtex4-2}
\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{braket}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{comment}

\usepackage{float}
\usepackage[
    pdftitle={},
    pdfauthor={},
    colorlinks=true,
    unicode=true,
    pdfborder={0 0 0},
    allcolors=blue
]{hyperref}

\renewcommand{\vec}[1]{\bm{#1}}
\newcommand{\im}{\mathrm{i}}
\newcommand{\e}{\mathrm{e}}
\renewcommand{\Im}{\operatorname{\mathsf{Im}}}
\renewcommand{\Re}{\operatorname{\mathsf{Re}}}
\newcommand{\vk}{{\vec k}}
\newcommand{\vq}{{\vec q}}
\newcommand{\VV}[2]{\begin{pmatrix}#1\\#2\end{pmatrix}}
\newcommand{\VVT}[2]{\begin{pmatrix}#1 & #2\end{pmatrix}}
\newcommand{\VVV}[3]{\begin{pmatrix}#1\\#2\\#3\end{pmatrix}}
\newcommand{\VVVT}[3]{\begin{pmatrix}#1 & #2 & #3\end{pmatrix}}
\newcommand{\MM}[4]{\begin{pmatrix}#1 & #2 \\ #3 & #4\end{pmatrix}}

\begin{document}

\title{Time-resolved optical conductivity and Higgs oscillations\\in two-band dirty superconductors}

\author{Paul Froese}
\affiliation{Max Planck Institute for Solid State Research,
70569 Stuttgart, Germany}
\affiliation{Quantum Matter Institute, University of British Columbia, Vancouver V6T 1Z4, Canada}

\author{Rafael Haenel}
\affiliation{Max Planck Institute for Solid State Research,
70569 Stuttgart, Germany}
\affiliation{Quantum Matter Institute, University of British Columbia, Vancouver V6T 1Z4, Canada}

\author{Dirk Manske}
\affiliation{Max Planck Institute for Solid State Research,
70569 Stuttgart, Germany}

\author{Lukas Schwarz}
\affiliation{Max Planck Institute for Solid State Research,
70569 Stuttgart, Germany}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
...
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item Ultrafast spectroscopy
	\item Collective modes in superconductors: Higgs, Goldstone (shifted to plasma energy due to Anderson-Higgs)
	\item In two-band superconductors: Additional out-of-phase Leggett mode, can couple to Higgs in nonequilibrium
	\item Difficulties excitation Higgs mode, in clean-limit only weak coupling
	\item In dirty superconductors: Coupling is enhanced
	\item This work: 1) Higgs oscillations in two-band sc. with bands in different limits, 2) Nonequilibrium optical conductivity, 3) Leggett mode in dirty-limit, 4) Prediction for MgB$_2$
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model}
\label{sec:model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item In this section show only the final formula, all derivation into the appendix A as the equations are similar to the Murotani paper.
	\item Show Hamiltonian, gap equation, Mattis-Bardeen replacement, general approach for calculating time evolution...
	\item I suggest putting the (final) equations for current, optical conductivity, $\delta\Delta(t)$ into the respective section, but in principle we could also put all equations in this section and show only the results in the following sections

	\item Used parameters (take general parameters for section III and IV where no Leggett mode occurs, Leggett mode is discussed later separately and MgB$_2$ will be also discussed later. Show the used parameters in these section)
	\item Implementation details? Are there any subtle points?
\end{itemize}

\begin{eqnarray}
	H_{BCS} = \sum_{i\mathbf{k}\sigma} c_{i\mathbf{k}\sigma}^\dagger
	c_{i\mathbf{k}\sigma} + \sum_{i\mathbf{k}}^{}
	\left( \Delta_i c_{i\mathbf{-k}\uparrow }^\dagger
	c_{i\mathbf{k}\downarrow }^\dagger  \right)
\end{eqnarray}

\begin{eqnarray}
	H_{\text{p-p}} = -\sum_{i\mathbf{kk'}\sigma}^{}
	\mathbf{J}_{i\mathbf{kk'}} \cdot \mathbf{A} \,
	c_{i\mathbf{k}\sigma}^\dagger  c_{i\mathbf{k}'\sigma} +
	\sum_{i\mathbf{k}\sigma}^{} \frac{s_i e^2}{2m_i} \mathbf{A}^2 \,
	c_{i\mathbf{k}\sigma}^\dagger c_{i\mathbf{k}\sigma}
\end{eqnarray}

\section{Single-band superconductivity}
\begin{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Higgs oscillations}
\label{sec:higgs_oscillations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item Equation for Current
	\item Equation for optical conductivity
	\item Present and discuss equilibrium optical conductivity in Fig. 1 for the four different limit cases, used in the rest of the paper
\end{itemize}

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/two_band_cond.png}
    \caption{\label{fig:two_band_cond}%
    Equilibrium optical conductivity of a two-band superconductor with gaps in different impurity scattering limits (clean-clean case rescaled as response is much smaller?)}
\end{figure}%

\begin{itemize}
	\item Equation for $\delta\Delta(t)$
	\item Show and discuss Higgs oscillations in Fig. 2 of the four cases with a suitable pump pulse (refer to appendix B for details about the pump pulse)
\end{itemize}

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/gap_osci.png}
    \caption{\label{fig:gap_osci}%
    Higgs oscillations excited by a pump pulse with enough bandwidth to cover both gaps for the different impurity scattering limits shown in Fig.~\ref{fig:two_band_cond}}
\end{figure}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nonequilibrium optical conductivity}
\label{sec:noneq_cond}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item Equation for nonequilibrium optical conductivity with two pulses. Maybe here more details (instead of appendix), as this is not covered by the Murotani paper
	\item Show and discuss nonequlibrium conductivity in Fig. 3.
	\item More figures of nonequilibrium conductivity? Suggestions: Imaginary part, maybe appendix. Nice 3d plot. Oscillations along cuts.
\end{itemize}

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/noneq_cond.png}
    \caption{\label{fig:noneq_cond}%
    Nonequilibrium optical conductivity of a pump-probe experiment for the different impurity scattering limits shown in Fig.~\ref{fig:two_band_cond}}
\end{figure}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Leggett mode}
\label{sec:leggett_mode}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item Definition, equation of Leggett mode
	\item Parameters for Fig.4 where Leggett mode occurs
	\item Discuss Fig. 4
	\item Maybe rethink what exactly to show in Fig. 4
	\item New plot of time-resolved conductivity showing Leggett mode?
\end{itemize}

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/leggett_oscillations.png}
    \caption{\label{fig:leggett_oscillations}%
    Induced amplitude (Higgs) and out-of-phase (Leggett) oscillations of a two-band superconductor for different impurity scattering rates}
\end{figure}%

\begin{itemize}
	\item Discuss Fig. 5 for varying coupling strength and compare with clean limit result
\end{itemize}

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/leggett_coupling.png}
    \caption{\label{fig:leggett_coupling}%
    Frequency of Leggett mode as function of interband coupling strength in the dirty limit}
\end{figure}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MgB$_2$}
\label{sec:mgb2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item Parameters which match MgB$_s$
	\item Show prediction in Fig. 6 of equilibrium conductivity, Higgs oscillations, nonequilibrium conductivity
\end{itemize}

\begin{figure}[H]
    \centering
    %\includegraphics[width=\columnwidth]{figures/mgb2.png}
    \Huge{TODO}
    \caption{\label{fig:mgb2}%
    Result with parameters for MgB$_2$ a) Equilibrium optical conductivity, b) Higgs oscillations, c) pump-probe conductivity and spectra}
\end{figure}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
...
\end{acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{literature}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{comment}
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Derivation of nonequilibrium optical conductivity}
\label{sec:derivation_noneq_cond}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item Put here all equations and derivations of the main results
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Influence of pump pulse frequency}
\label{sec:influence_pump_pulse_freq}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item Discuss influence of pump pulse frequency and bandwith to excite only one or both Higgs mode
	\item Show result in Fig. 7
\end{itemize}

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/influence_pump_pulse_freq.png}
    \caption{\label{fig:influence_pump_pulse_freq}%
    Influence of pump pulse frequency}
\end{figure}%

\end{document}

### 2020-10-14 pulse-shape/pulse_shape.py

@@ -1,0 +1,105 @@
+#%%
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy import integrate
+from scipy import interpolate
+import scipy
+from scipy.fftpack import fft, fftfreq, fftshift
+
+def fft(t,f, inverse=False):
+    T = max(t) - min(t)
+    Nt = len(t)
+    dt = T/Nt
+    xw = np.arange(Nt) * 2 * np.pi / T
+
+    if inverse:
+        xw = np.concatenate([xw[:Nt//2]+2*np.pi/dt, xw[Nt//2:]])
+        idx = np.argsort(xw)
+        xw = xw[idx]
+        f = f[idx]
+        fw = scipy.ifft(f, axis=0)/np.sqrt(Nt)*Nt
+    else:
+        fw = scipy.fft(fftshift(f), axis=0)/np.sqrt(Nt)
+        xw = np.concatenate([xw[:Nt//2], xw[Nt//2:]-2*np.pi/dt])
+        idx = np.argsort(xw)
+        xw = xw[idx]
+        fw = fw[idx]
+    return xw, fw
+
+# 1 time unit = 6.58285E-2 ps
+u_t = 6.58285E-2
+u_e = 10
+meV_to_THz = 0.2417990504024
+
+d0 = 0.13
+
+ps = np.loadtxt('pulse_shape.csv', delimiter=',')
+t_pulse = ps[:,0]
+e_pulse = ps[:,1]
+e_pulse /= np.max(np.abs(e_pulse))
+t_pulse /= u_t
+
+x = t_pulse
+y = e_pulse
+plt.figure('data')
+plt.clf()
+plt.plot(x,y)
+
+
+def Efield(t, tau, te, dt, w, A0):
+    # return A_pump(t) + A_probe(t)
+    """ Returns the vector potential at time t """
+    return A0*np.exp(-(t-te-dt)**2/(2*tau**2)) \
+        * ( (t-te-dt)/tau**2 * np.cos(w*(t-dt)) + w * np.sin(w*(t-dt)) )
+
+def A(t):
+# return A_pump(t) + A_probe(t)
+    """ Returns the vector potential at time t """
+    return A0*np.exp(-(t-te)**2/(2*tau**2))*np.cos(w*t) \
[…]

### 2020-10-14 pulse_shape.py

@@ -1,0 +1,180 @@
+#%%
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy import integrate
+from scipy import interpolate
+import scipy
+from scipy.fftpack import fft, fftfreq, fftshift
+
+def rfft(t,f, inverse=False):
+    T = max(t) - min(t)
+    Nt = len(t)
+    dt = T/Nt
+    xw = np.arange(Nt) * 2 * np.pi / T
+
+    if inverse:
+        xw = np.concatenate([xw[:Nt//2]+2*np.pi/dt, xw[Nt//2:]])
+        idx = np.argsort(xw)
+        xw = xw[idx]
+        f = f[idx]
+        fw = scipy.ifft(f, axis=0)/np.sqrt(Nt)*Nt
+    else:
+        fw = scipy.fft(fftshift(f), axis=0)/np.sqrt(Nt)
+        xw = np.concatenate([xw[:Nt//2], xw[Nt//2:]-2*np.pi/dt])
+        idx = np.argsort(xw)
+        xw = xw[idx]
+        fw = fw[idx]
+    return xw, fw
+
+def running_mean(x, N):
+    cumsum = np.cumsum(np.insert(x, 0, 0))
+    return (cumsum[N:] - cumsum[:-N]) / float(N)
+
+def nm(x):
+    return x / np.max(np.abs(x))
+
+ps = np.loadtxt('..\\material_parameters_Matsunaga\\pulse_shape.csv', delimiter=',')
+rm = 20
+
+t_pulse = running_mean(ps[:,0],rm)
+
+b = 0.3
+smooth = (np.tanh((t_pulse-1.5)/b)+1)/2
+smooth2 = (-np.tanh((t_pulse-7.5)/b)+1)/2
+
+e_pulse = running_mean(ps[:,1],rm)*smooth*smooth2
+e_pulse /= np.max(np.abs(e_pulse))
+
+# 1 time unit = 0.438856 ps
+t_pulse /= 0.438856
+
+A0=1
+a_pulse = -scipy.integrate.cumtrapz(e_pulse,t_pulse, initial=0)
+shift = 0
[…]

### 2020-10-14 singleband/BCS/BCS.py

@@ -1,0 +1,105 @@
+#%%
+import numpy as np
+from scipy import integrate
+import matplotlib.pyplot as plt
+
+hbar=1
+kb=1
+e=1
+
+u_temp = 116.032
+u_en = 10
+meV_to_THz = 0.2417990504024
+
+d0 = np.array([0.13])
+# U = np.array([[0.459]])
+# d0  = np.array([0.20])
+# U = np.array([[0.506]])
+# d0  = np.array([0.23])
+# U = np.array([[0.524]])
+
+us = [np.array([[0.459]]), np.array([[0.506]]), np.array([[0.524]])]
+
+m=np.array([0.78])
+ef=np.array([100])
+wd = 5.5
+
+
+s=np.array([1])
+T=4/u_temp
+B = 1/(kb*T)
+
+nb = len(m)
+kf = np.sqrt(2*m*ef)/hbar
+vf = kf/m
+n = kf**3/(3*np.pi**2)
+N0 = m*kf/(2*np.pi**2)
+
+Ne = 1000
+ep = np.linspace(-wd, wd, Ne)
+
+
+def d0_integrand(x, d):
+    # This is an auxiliary function used in find_d0 to calculate an integral
+    return 0.5*1/np.sqrt(x**2+d**2)*np.tanh(B/2*np.sqrt(x**2+d**2))
+
+
+def find_d0(UN0, d_last):
+    alpha = 0.05
+    # this function finds the initial gap(s) given U*N(0). Works in the single or multiband case
+    if nb == 2:
+        d = np.array([1, 1])
+        integral = np.zeros(2)
+        for j in [0, 1]:
+            integral[j] = integrate.quad(d0_integrand, -wd, wd, (d[j],))[0]
+        d_new = np.sum(UN0*d*integral, axis=1)
+
+        while (d != d_new).all(): # seems like convergence of gap is based on machine precision
+            d = d_new
+            integral = np.zeros(2)
+            for j in [0, 1]:
+                integral[j] = integrate.quad(d0_integrand, -wd, wd, (d[j],))[0]
+            d_new = np.sum(UN0*d*integral, axis=1)
+        return d_new
+    elif nb == 1:
+        d = d_last
+        d_new = UN0*d*integrate.quad(d0_integrand, -wd, wd, (d,))[0]
[…]

### 2020-10-14 singleband/conductivity-dirty/higgs_matsunaga.py

@@ -1,0 +1,579 @@
+import numpy as np
+from numpy import sqrt
+# import matplotlib as mpl
+# mpl.use('Agg')
+import matplotlib.pyplot as plt
+from scipy import integrate
+from scipy import interpolate
+from scipy.fftpack import fft, fftfreq, fftshift
+import scipy
+import time
+import pickle
+import sys
+import os
+import gc
+
+code_version = {
+    "1.0": "first version",
+    "1.1": "pulse shape modified, now parameter te, te_pr"
+}
+#%%
+# ncpus = int(os.environ.get('SLURM_CPUS_PER_TASK', default=1))       # number of CPUs
+job_ID = int(os.environ.get('SLURM_ARRAY_JOB_ID', default=-1))       # job ID
+task_ID = int(os.environ.get('SLURM_ARRAY_TASK_ID', default=-1)) # task ID
+task_count = int(os.environ.get('SLURM_ARRAY_TASK_COUNT', default=1))
+task_count = 64
+
+if task_ID != -1:
+    exec("from {} import params".format(sys.argv[1]))
+    params = params[task_ID::task_count]
+else:
+    from parameters import params
+    params = [ params[0] ]
+
+    params = [
+        {
+            "Ne": 850,
+            "tmin": -2*(2*np.pi),
+            "tmax": 30*(2*np.pi),
+            "Nt": 3000,
+            "T": 0.56, #0.22
+            "wd":  10,
+            "s": np.array([1]),
+            "m": np.array([1.0]),
+            "ef": np.array([500]),
+            "g": np.array([10]),
+            "U": np.array([[0.2082]]),
+            "A0": -1,
+            "tau": 0.81,
+            "w":  0.36,
+            "te": -4.21,
+            "A0_pr": -0.1,
+            "tau_pr": 0.81,
+            "w_pr": 0.36,
+            "t_delay": 9,
+            "te_pr": -4.21
+        }
+    ]
+
+
+for p in params:
+    Ne = p["Ne"]
+    tmin= p["tmin"]
+    tmax= p["tmax"]
+    Nt=p["Nt"]
+
[…]

### 2020-10-14 singleband/conductivity-dirty/parameters.py

@@ -1,0 +1,92 @@
+import numpy as np
+
+params_ = [
+    {
+        "Ne": [550],
+        "tmin": [-2*(2*np.pi)],
+        "tmax": [12*(2*np.pi)],
+        "Nt": 3000,
+        "T": [0.22],#,0.5,0.54,0.56],
+        "wd":  [10],
+        "s": np.array([1]),
+        "m": [ np.array([1.0]) ],
+        "ef": [ np.array([500]) ],
+        "g": [ np.array([10]) ],#,np.array([0.00001]),np.array([1]),np.array([2]) ],
+        "U": [ np.array([[0.2082]]) ],
+        "A0": [-1,0],
+        "tau": [0.81],
+        "w":  [0.36],
+        "A0_pr": [-0.08],
+        "te": -4.21,
+        "tau_pr": [0.81],
+        "w_pr": [0.36],
+        "t_delay": np.linspace(8*np.pi,12*np.pi,64),
+        "te_pr": -4.21
+    },
+    {
+        "Ne": [550],
+        "tmin": [-2*(2*np.pi)],
+        "tmax": [12*(2*np.pi)],
+        "Nt": 3000,
+        "T": [0.22],#,0.5,0.54,0.56],
+        "wd":  [10],
+        "s": np.array([1]),
+        "m": [ np.array([1.0]) ],
+        "ef": [ np.array([500]) ],
+        "g": [ np.array([10]) ],#,np.array([0.00001]),np.array([1]),np.array([2]) ],
+        "U": [ np.array([[0.2082]]) ],
+        "A0": [-1],
+        "tau": [0.81],
+        "w":  [0.36],
+        "A0_pr": [0],
+        "te": -4.21,
+        "tau_pr": [0.81],
+        "w_pr": [0.36],
+        "t_delay": np.linspace(8*np.pi,12*np.pi,64),
+        "te_pr": -4.21
+    }
+]
+
+
+params = []
+for p in params_:
+    for A0 in p["A0"]:
+        for A0_pr in p["A0_pr"]:
+            for Ne in p["Ne"]:
+                for tmin in p["tmin"]:
+                    for tmax in p["tmax"]:
+                        for T in p["T"]:
+                            for wd in p["wd"]:
+                                for m in p["m"]:
+                                    for ef in p["ef"]:
+                                        for U in p["U"]:
+                                            for tau in p["tau"]:
+                                                for w in p["w"]:
+                                                    for tau_pr in p["tau_pr"]:
[…]

### 2020-10-14 singleband/conductivity-dirty/higgs_matsunaga.py
standard commit

@@ -19,17 +19,21 @@ code_version = {
 }
 #%%
 # ncpus = int(os.environ.get('SLURM_CPUS_PER_TASK', default=1))       # number of CPUs
-job_ID = int(os.environ.get('SLURM_ARRAY_JOB_ID', default=-1))       # job ID
-task_ID = int(os.environ.get('SLURM_ARRAY_TASK_ID', default=-1)) # task ID
-task_count = int(os.environ.get('SLURM_ARRAY_TASK_COUNT', default=1))
-task_count = 64
+if len(sys.argv) > 1:
+    job_ID = int(sys.argv[1])
+    task_ID = int(sys.argv[1])
+    task_count = int(sys.argv[2])+1
+else:
+    job_ID = -1
+    task_ID = -1
+    task_count = 1
 
 if task_ID != -1:
     exec("from {} import params".format(sys.argv[1]))
     params = params[task_ID::task_count]
 else:
-    from parameters import params
-    params = [ params[0] ]
+    #from parameters import params
+    #params = [ params[0] ]
 
     params = [
         {

### 2020-10-14 singleband/conductivity-dirty/mega_script.sh

@@ -1,0 +1,34 @@
+#!/bin/bash
+
+MAX=63
+for i in `seq 0 1 ${MAX}`
+do
+	FILENAME=job_file_${i}.ll
+	echo "# @ shell=/bin/bash" > $FILENAME
+
+	echo "# Script for LoadLeveler job steps" >> $FILENAME
+
+	echo "# @ job_name = h-imp" >> $FILENAME
+	echo "# @ error  = error_${i}.err" >> $FILENAME
+	echo "# @ output = log_${i}.out" >> $FILENAME
+	echo "# @ job_type = MPICH" >> $FILENAME
+	echo "# @ node_usage = shared" >> $FILENAME
+
+	echo "# @ node = 1" >> $FILENAME
+	echo "# @ tasks_per_node = 1" >> $FILENAME
+	echo "# @ environment = COPY_ALL" >> $FILENAME
+	echo "# @ notification = never" >> $FILENAME
+	echo "# @ notify_user =" >> $FILENAME
+	echo "# @ class = 20core" >> $FILENAME
+	echo "# @ queue" >> $FILENAME
+
+	echo "# exit on error" >> $FILENAME
+	echo "set -e" >> $FILENAME
+
+	echo "export OMP_NUM_THREADS=1" >> $FILENAME
+
+	echo "python3 higgs_matsunaga.py ${i} ${MAX}" >> $FILENAME
+
+
+	llsubmit $FILENAME >> log.out
+done

### 2020-10-14 pulse-shape/pulse_shape.py
standard commit

@@ -58,22 +58,20 @@ def A(t):
     return A0*np.exp(-(t-te)**2/(2*tau**2))*np.cos(w*t) \
         +  A0_pr*np.exp(-(t-te-t_delay)**2/(2*tau_pr**2))*np.cos(w_pr*(t-t_delay))
 
-tau = 5.37
-te = -40.11
-dt = 100
-w = 3.78E-2
-A0 = -20.55
 
 tau = 5.37
-te = -39
+te = -40
 dt = 100
-w = 0.04
-A0 = -24
+dt = 0
+w = 0.038
+A0 = -25
 
-plt.plot(t_pulse, Efield(t_pulse, tau, te, dt, w, A0))
-t = np.linspace(min(t_pulse), max(t_pulse), 1000)
+t = np.linspace(-75, max(t_pulse), 1000)
+plt.plot(t, Efield(t, tau, te, dt, w, A0))
 E_fit = Efield(t, tau, te, dt, w, A0)
+plt.xlim((min(t), max(t)))
 
+#%%
 from scipy.optimize import curve_fit
 
 popt, pcov = curve_fit(Efield, x,y, p0=[tau, te, dt, w, A0])

### 2020-10-14 singleband/BCS/BCS.py

@@ -12,13 +12,13 @@ u_en = 10
 meV_to_THz = 0.2417990504024
 
 d0 = np.array([0.13])
-# U = np.array([[0.459]])
+# U = np.array([[0.46]])
 # d0  = np.array([0.20])
-# U = np.array([[0.506]])
+# U = np.array([[0.5]])
 # d0  = np.array([0.23])
-# U = np.array([[0.524]])
+# U = np.array([[0.525]])
 
-us = [np.array([[0.459]]), np.array([[0.506]]), np.array([[0.524]])]
+us = [np.array([[0.459]]), np.array([[0.5]]), np.array([[0.524]])]
 
 m=np.array([0.78])
 ef=np.array([100])
@@ -92,13 +92,13 @@ for j in np.arange(3):
 #%%
 plt.figure(figsize=(3,2))
 plt.plot(temps*u_temp, 2*gaps*u_en*meV_to_THz, 'k')
-plt.ylim((0,d0[0]*3.3*2*u_en*meV_to_THz))
+plt.ylim((0,d0[0]*2*2*u_en*meV_to_THz))
 plt.xlabel('T (K)')
 plt.ylabel('$2\Delta$ (THz)')
 plt.tight_layout()
 plt.savefig('BCS.pdf')
 import pickle
-f1 = open(f'BCS.pickle', 'w')
+f1 = open(f'BCS.pickle', 'ab')
 pickle.dump(temps*u_temp, f1)
 pickle.dump(2*gaps*u_en*meV_to_THz, f1)
 f1.close()

### 2020-10-14 singleband/conductivity-dirty/higgs_matsunaga.py

@@ -19,7 +19,7 @@ code_version = {
 }
 #%%
 # ncpus = int(os.environ.get('SLURM_CPUS_PER_TASK', default=1))       # number of CPUs
-if len(sys.argv) > 1:
+if len(sys.argv) == 3:
     job_ID = int(sys.argv[1])
     task_ID = int(sys.argv[1])
     task_count = int(sys.argv[2])+1
@@ -32,33 +32,33 @@ if task_ID != -1:
     exec("from {} import params".format(sys.argv[1]))
     params = params[task_ID::task_count]
 else:
-    #from parameters import params
-    #params = [ params[0] ]
+    from parameters import params
+    params = [ params[0] ]
 
-    params = [
-        {
-            "Ne": 850,
-            "tmin": -2*(2*np.pi),
-            "tmax": 30*(2*np.pi),
-            "Nt": 3000,
-            "T": 0.56, #0.22
-            "wd":  10,
-            "s": np.array([1]),
-            "m": np.array([1.0]),
-            "ef": np.array([500]),
-            "g": np.array([10]),
-            "U": np.array([[0.2082]]),
-            "A0": -1,
-            "tau": 0.81,
-            "w":  0.36,
-            "te": -4.21,
-            "A0_pr": -0.1,
-            "tau_pr": 0.81,
-            "w_pr": 0.36,
-            "t_delay": 9,
-            "te_pr": -4.21
-        }
-    ]
+    # params = [
+    #     {
+    #         "Ne": 850,
+    #         "tmin": -2*(2*np.pi),
+    #         "tmax": 30*(2*np.pi),
+    #         "Nt": 3000,
+    #         "T": 0.56, #0.22
+    #         "wd":  10,
+    #         "s": np.array([1]),
+    #         "m": np.array([1.0]),
+    #         "ef": np.array([500]),
+    #         "g": np.array([10]),
+    #         "U": np.array([[0.2082]]),
+    #         "A0": -1,
+    #         "tau": 0.81,
+    #         "w":  0.36,
+    #         "te": -4.21,
+    #         "A0_pr": -0.1,
+    #         "tau_pr": 0.81,
+    #         "w_pr": 0.36,
[…]

### 2020-10-14 singleband/conductivity-dirty/mega_script.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-MAX=63
+MAX=159
 for i in `seq 0 1 ${MAX}`
 do
 	FILENAME=job_file_${i}.ll

### 2020-10-14 singleband/conductivity-dirty/parameters_old.py

@@ -1,51 +1,28 @@
 import numpy as np
 
-u_temp = 116.032
-
 params_ = [
     {
-        "Ne": [600],
-        "tmin": [-75],
-        "tmax": [450],
-        "Nt": 3000,
-        "T": [4/u_temp],#,0.5,0.54,0.56],
-        "wd":  [2],
+        "Ne": [130],
+        "tmin": [-2*(2*np.pi)],
+        "tmax": [2*(2*np.pi)],
+        "Nt": 500,
+        "T": [0.02],#,0.5,0.54,0.56],
+        #"wd":  [10],
+        "wd":  [16.66],
         "s": np.array([1]),
         "m": [ np.array([0.78]) ],
-        "ef": [ np.array([100]) ],
-        "g": [ np.array([x]) for x in [0.00001, 0.05,0.1,0.15,0.2,0.23, 0.25, 0.27, 0.3, 0.35, 0.4]],
-        "U": [ np.array([[0.46]]) ],
-        "A0": [-25],
-        "tau": [5.37],
-        "w":  [0.04],
-        "A0_pr": [0],
-        "te": -40,
-        "tau_pr": [5.37],
-        "w_pr": [0.04],
-        "t_delay": [0],
-        "te_pr": -40
-    },
-    {
-        "Ne": [600],
-        "tmin": [-75],
-        "tmax": [450],
-        "Nt": 3000,
-        "T": [4/u_temp],#,0.5,0.54,0.56],
-        "wd":  [2],
-        "s": np.array([1]),
-        "m": [ np.array([0.78]) ],
-        "ef": [ np.array([100]) ],
-        "g": [ np.array([x]) for x in [0.00001, 0.05,0.1,0.15,0.2,0.23, 0.25, 0.27, 0.3, 0.35, 0.4]],
-        "U": [ np.array([[0.46]]) ],
-        "A0": [-25],
-        "tau": [5.37],
-        "w":  [0.04],
-        "A0_pr": [-2.5],
-        "te": -40,
-        "tau_pr": [5.37],
-        "w_pr": [0.04],
-        "t_delay": np.linspace(50,200,128),
-        "te_pr": -40
+        "ef": [ np.array([666.66]) ],
+        "g": [ np.array([10]) ],#,np.array([0.00001]),np.array([1]),np.array([2]) ],
+        "U": [ np.array([[0.185]]) ],
+        "A0": [-1],
+        "tau": [0.81],
[…]

### 2020-10-15 singleband/conductivity-dirty/higgs_matsunaga.py
a

@@ -18,18 +18,12 @@ code_version = {
     "1.1": "pulse shape modified, now parameter te, te_pr"
 }
 #%%
-# ncpus = int(os.environ.get('SLURM_CPUS_PER_TASK', default=1))       # number of CPUs
-if len(sys.argv) == 3:
-    job_ID = int(sys.argv[1])
-    task_ID = int(sys.argv[1])
-    task_count = int(sys.argv[2])+1
-else:
-    job_ID = -1
-    task_ID = -1
-    task_count = 1
+job_ID = int(sys.argv[1])
+task_ID = int(sys.argv[1])
+task_count = int(sys.argv[2])+1
 
 if task_ID != -1:
-    exec("from {} import params".format(sys.argv[1]))
+    from parameters import params
     params = params[task_ID::task_count]
 else:
     from parameters import params

### 2020-10-15 singleband/conductivity-dirty/mega_script.sh
a

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-MAX=159
+MAX=138
 for i in `seq 0 1 ${MAX}`
 do
 	FILENAME=job_file_${i}.ll

### 2020-10-15 singleband/conductivity-dirty/parameters.py

@@ -13,7 +13,7 @@ params_ = [
         "s": np.array([1]),
         "m": [ np.array([0.78]) ],
         "ef": [ np.array([100]) ],
-        "g": [ np.array([x]) for x in [0.00001, 0.05,0.1,0.15,0.2,0.23, 0.25, 0.27, 0.3, 0.35, 0.4]],
+        "g": [ np.array([x]) for x in np.array([2,3,4,5,6,7,8,9,10])*0.1258396834202397*2 ],
         "U": [ np.array([[0.46]]) ],
         "A0": [-25],
         "tau": [5.37],
@@ -35,7 +35,7 @@ params_ = [
         "s": np.array([1]),
         "m": [ np.array([0.78]) ],
         "ef": [ np.array([100]) ],
-        "g": [ np.array([x]) for x in [0.00001, 0.05,0.1,0.15,0.2,0.23, 0.25, 0.27, 0.3, 0.35, 0.4]],
+        "g": [ np.array([x]) for x in np.array([5,10])*0.1258396834202397*2 ],
         "U": [ np.array([[0.46]]) ],
         "A0": [-25],
         "tau": [5.37],

### 2020-10-15 singleband/conductivity-dirty/mega_script.sh
a

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-MAX=138
+MAX=140
 for i in `seq 0 1 ${MAX}`
 do
 	FILENAME=job_file_${i}.ll

### 2020-10-15 singleband/conductivity-dirty/parameters.py

@@ -13,7 +13,8 @@ params_ = [
         "s": np.array([1]),
         "m": [ np.array([0.78]) ],
         "ef": [ np.array([100]) ],
-        "g": [ np.array([x]) for x in np.array([2,3,4,5,6,7,8,9,10])*0.1258396834202397*2 ],
+        "g": [ np.array([x]) for x in
+              np.array([0.000001,0.00001,0.0001,0.001,0.01,0.05,0.1,0.15,0.2,0.3,0.4,0.45,0.5,0.55,0.6,0.7,0.8,0.9,0.95,1,1.05,1.1,1.2,1.3, 20])*0.1258396834202397*2 ],
         "U": [ np.array([[0.46]]) ],
         "A0": [-25],
         "tau": [5.37],
@@ -35,7 +36,7 @@ params_ = [
         "s": np.array([1]),
         "m": [ np.array([0.78]) ],
         "ef": [ np.array([100]) ],
-        "g": [ np.array([x]) for x in np.array([5,10])*0.1258396834202397*2 ],
+        "g": [ np.array([20])*0.1258396834202397*2 ],
         "U": [ np.array([[0.46]]) ],
         "A0": [-25],
         "tau": [5.37],

### 2020-10-15 pulse-shape/pulse_shape.py
a

@@ -55,15 +55,15 @@ def Efield(t, tau, te, dt, w, A0):
 def A(t):
 # return A_pump(t) + A_probe(t)
     """ Returns the vector potential at time t """
-    return A0*np.exp(-(t-te)**2/(2*tau**2))*np.cos(w*t) \
-        +  A0_pr*np.exp(-(t-te-t_delay)**2/(2*tau_pr**2))*np.cos(w_pr*(t-t_delay))
+    return A0*np.exp(-(t-te)**2/(2*tau**2))*np.cos(w*t) # \
+        # +  A0_pr*np.exp(-(t-te-t_delay)**2/(2*tau_pr**2))*np.cos(w_pr*(t-t_delay))
 
 
 tau = 5.37
 te = -40
 dt = 100
 dt = 0
-w = 0.038
+w = 0.04
 A0 = -25
 
 t = np.linspace(-75, max(t_pulse), 1000)
@@ -71,6 +71,41 @@ plt.plot(t, Efield(t, tau, te, dt, w, A0))
 E_fit = Efield(t, tau, te, dt, w, A0)
 plt.xlim((min(t), max(t)))
 
+#%% fig 1 - pulse
+plt.rcParams.update({'font.size': 13})
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+plt.figure('pulse-t', figsize=(4.5,1.8))
+plt.clf()
+t = np.linspace(-75, 500, 1000)
+plt.plot(t*u_t, Efield(t, tau, te, dt, w, A0), 'k')
+plt.xlim((-4.5,20))
+plt.ylabel('$E(t)$')
+plt.xlabel('$t$ (ps)')
+plt.tight_layout()
[…]

### 2020-10-15 singleband/BCS/BCS.py

@@ -2,6 +2,8 @@
 import numpy as np
 from scipy import integrate
 import matplotlib.pyplot as plt
+import pickle
+
 
 hbar=1
 kb=1
@@ -38,6 +40,7 @@ N0 = m*kf/(2*np.pi**2)
 Ne = 1000
 ep = np.linspace(-wd, wd, Ne)
 
+#%%
 
 def d0_integrand(x, d):
     # This is an auxiliary function used in find_d0 to calculate an integral
@@ -103,3 +106,18 @@ pickle.dump(temps*u_temp, f1)
 pickle.dump(2*gaps*u_en*meV_to_THz, f1)
 f1.close()
 # plt.xlim((8,9))
+
+#%%
+f1 = open(f'BCS.pickle', 'rb')
+a=pickle.load(f1)
+b=pickle.load(f1)
+f1.close()
+
+plt.figure(figsize=(1.8,1.3))
+plt.plot(a, b[:,0], 'k')
+plt.ylim((0,0.8))
+plt.xlim((0,10))
+plt.xlabel('T (K)')
+plt.ylabel('$2\Delta$ (THz)')
+plt.tight_layout()
+plt.savefig('BCS-1.pdf', transparent=True)

### 2020-10-18 multiband/gap-oscillations/higgs_mgb2.py
a

@@ -1,0 +1,792 @@
+#%%
+import numpy as np
+from numpy import sqrt
+# import matplotlib as mpl
+# mpl.use('Agg')
+import matplotlib.pyplot as plt
+from scipy import integrate
+from scipy import interpolate
+from scipy.fftpack import fft, fftfreq, fftshift
+import scipy
+import time
+import pickle
+import sys
+import os
+import gc
+
+code_version = {
+    "1.0": "first version",
+    "1.1": "pulse shape modified, now parameter te, te_pr",
+    "1.2": "U calculated from gap and v (gap and v are input parameters)"
+}
+if len(sys.argv)==3:
+    job_ID = int(sys.argv[1])
+    task_ID = int(sys.argv[1])
+    task_count = int(sys.argv[2])+1
+else:
+    job_ID = -1
+    task_ID = -1
+    task_count = -1
+
+
+if task_ID != -1:
+    from parameters import params
+    params = params[task_ID::task_count]
+else:
+    from parameters import params
+    params = [ params[0] ]
+
+    u_temp = 116.032
+    params_ = [
+        {
+            "Ne": [500],
+            "tmin": [-80],
+            "tmax": [230],
+            # "tmax": [450],
+            "Nt": 3000,
+            "T": [1/u_temp],#,0.5,0.54,0.56],
+            "wd":  [5],
+            "s": np.array([1,-1]),
+            "m": [ np.array([0.85, 1.38]) ],
+            "ef": [ np.array([290, 70]) ],
+            "g": [ np.array([10,10]), np.array([0.00001,10]), np.array([10,0.00001]), np.array([0.00001,0.00001]) ],
+            "pre_d0": np.array([0.3,0.7]),
+            "v": np.linspace(0,0.3,10),
+            "A0": [1],
+            "tau": [6,5,3,2,1],
+            "w":  [0],
+            "A0_pr": [0],
+            "te": 0,
+            "tau_pr": [5.37],
+            "w_pr": [0.04],
+            "t_delay": [0],
+            "te_pr": -40
+        },
+        {
+            "Ne": [500],
+            "tmin": [-80],
+            "tmax": [230],
+            # "tmax": [450],
+            "Nt": 3000,
+            "T": [1/u_temp],#,0.5,0.54,0.56],
+            "wd":  [5],
+            "s": np.array([1,-1]),
+            "m": [ np.array([0.85, 1.38]) ],
[…]

### 2020-10-18 multiband/gap-oscillations/mega_script.sh

@@ -1,0 +1,34 @@
+#!/bin/bash
+
+MAX=319
+for i in `seq 0 1 ${MAX}`
+do
+	FILENAME=job_file_${i}.ll
+	echo "# @ shell=/bin/bash" > $FILENAME
+
+	echo "# Script for LoadLeveler job steps" >> $FILENAME
+
+	echo "# @ job_name = h-imp" >> $FILENAME
+	echo "# @ error  = error_${i}.err" >> $FILENAME
+	echo "# @ output = log_${i}.out" >> $FILENAME
+	echo "# @ job_type = MPICH" >> $FILENAME
+	echo "# @ node_usage = shared" >> $FILENAME
+
+	echo "# @ node = 1" >> $FILENAME
+	echo "# @ tasks_per_node = 1" >> $FILENAME
+	echo "# @ environment = COPY_ALL" >> $FILENAME
+	echo "# @ notification = never" >> $FILENAME
+	echo "# @ notify_user =" >> $FILENAME
+	echo "# @ class = 28core" >> $FILENAME
+	echo "# @ queue" >> $FILENAME
+
+	echo "# exit on error" >> $FILENAME
+	echo "set -e" >> $FILENAME
+
+	echo "export OMP_NUM_THREADS=1" >> $FILENAME
+
+	echo "python3 higgs_mgb2.py ${i} ${MAX}" >> $FILENAME
+
+
+	llsubmit $FILENAME >> log.out
+done

### 2020-10-18 multiband/gap-oscillations/parameters.py

@@ -1,0 +1,146 @@
+import numpy as np
+
+u_temp = 116.032
+params_ = [
+    {
+        "Ne": [500],
+        "tmin": [-80],
+        "tmax": [230],
+        # "tmax": [450],
+        "Nt": 3000,
+        "T": [1/u_temp],#,0.5,0.54,0.56],
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10,10]), np.array([0.00001,10]), np.array([10,0.00001]), np.array([0.00001,0.00001]) ],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": np.linspace(0,0.3,10),
+        "A0": [1],
+        "tau": [6,5,3,2,1],
+        "w":  [0],
+        "A0_pr": [0],
+        "te": 0,
+        "tau_pr": [5.37],
+        "w_pr": [0.04],
+        "t_delay": [0],
+        "te_pr": -40
+    },
+    {
+        "Ne": [500],
+        "tmin": [-80],
+        "tmax": [230],
+        # "tmax": [450],
+        "Nt": 3000,
+        "T": [1/u_temp],#,0.5,0.54,0.56],
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10,10]), np.array([0.00001,10]), np.array([10,0.00001]), np.array([0.00001,0.00001]) ],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": np.linspace(0,0.3,10),
+        "A0": [1],
+        "tau": [6.5],
+        "w":  [1],
+        "A0_pr": [0],
+        "te": 0,
+        "tau_pr": [5.37],
+        "w_pr": [0.04],
+        "t_delay": [0],
+        "te_pr": -40
+    },
+    {
+        "Ne": [500],
+        "tmin": [-80],
+        "tmax": [250],
+        # "tmax": [450],
+        "Nt": 2000,
+        "T": [1/u_temp],#,0.5,0.54,0.56],
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
[…]

### 2020-10-19 multiband/gap-oscillations/higgs_mgb2.py
a

@@ -19,7 +19,7 @@ code_version = {
     "1.1": "pulse shape modified, now parameter te, te_pr",
     "1.2": "U calculated from gap and v (gap and v are input parameters)"
 }
-if len(sys.argv)==3:
+if True:#len(sys.argv)==3:
     job_ID = int(sys.argv[1])
     task_ID = int(sys.argv[1])
     task_count = int(sys.argv[2])+1
@@ -32,7 +32,10 @@ else:
 if task_ID != -1:
     from parameters import params
     params = params[task_ID::task_count]
+    print('parameters loaded')
 else:
+    print('parameters not loaded')
+    pass
     from parameters import params
     params = [ params[0] ]
 

### 2020-10-19 paper/paper_v1.tex
a

@@
 \usepackage{comment}
-
+\usepackage{siunitx}
 \usepackage{float}
@@
 
-\author{Paul Froese}
+\author{Rafael Haenel}
 \affiliation{Max Planck Institute for Solid State Research,
@@
 
-\author{Rafael Haenel}
+\author{Paul Froese}
 \affiliation{Max Planck Institute for Solid State Research,
@@
 	\item Difficulties excitation Higgs mode, in clean-limit only weak coupling
-	\item In dirty superconductors: Coupling is enhanced
+	\item In dirty superconductors: Coupling is enhanced. Activation of
+		$\mathbf{p} \cdot \mathbf{A}$ term by momentum-converation
+		braking impurity scattering.
+	\item Discussion of Matthis Bardeen theory.
 	\item This work: 1) Higgs oscillations in two-band sc. with bands in different limits, 2) Nonequilibrium optical conductivity, 3) Leggett mode in dirty-limit, 4) Prediction for MgB$_2$
 \end{itemize}
+
+This article is organized as follows. In Sec. \ref{sec:model} we briefly review
+key aspects of the model as introduced by Murotani and Shimano []. We then
+discuss the case of a single-band superconductor in a pump-probe scenario and
+additionally with an assymetric supercurrent-inducing probe pulse in Sec.
+\ref{sec:singleband}. We then extend these results to the two-band case in Sec.
+\ref{sec:multiband} where we give explicit experimental predicitons for
+pump-probe characterization of collective modes in MgB$_2$.
 
@@
 \begin{eqnarray}
-	H_{BCS} = \sum_{i\mathbf{k}\sigma} c_{i\mathbf{k}\sigma}^\dagger
+	H_{\text{BCS}} = \sum_{i\mathbf{k}\sigma}  
+	\varepsilon_{i\mathbf{k}}c_{i\mathbf{k}\sigma}^\dagger
 	c_{i\mathbf{k}\sigma} + \sum_{i\mathbf{k}}^{}
 	\left( \Delta_i c_{i\mathbf{-k}\uparrow }^\dagger
-	c_{i\mathbf{k}\downarrow }^\dagger  \right)
+	c_{i\mathbf{k}\downarrow }^\dagger  \right) \,,
 \end{eqnarray}
 
-\begin{eqnarray}
+where $\varepsilon_{i\mathbf{k}} = s_i \left(\mathbf{k}^2/2m_i -
+\varepsilon_{F_i}\right)$ and the superconducting order parameter is self-consistently determined by 
+$\Delta_i = \sum_{j\mathbf{k}}^{}U_{ij} \langle c_{j-\mathbf{k}\downarrow
+}c_{j\mathbf{k}\uparrow }\rangle$.
+
+\begin{eqnarray*}
 	H_{\text{p-p}} = -\sum_{i\mathbf{kk'}\sigma}^{}
@@
 	c_{i\mathbf{k}\sigma}^\dagger c_{i\mathbf{k}\sigma}
-\end{eqnarray}
+\end{eqnarray*}
+
+\begin{eqnarray*}
+	\langle \left|\mathbf{e} \cdot
+	\mathbf{J}_{i\mathbf{kk'}}\right|^2\rangle_{\text{Av}}
+	&=& \int \frac{d\Omega_\mathbf{k}}{4\pi} \frac{d\Omega_\mathbf{k}'}{4\pi}
+	\left|\mathbf{e} \cdot \mathbf{J}_{i\mathbf{kk'}}\right|^2
+	\\
+	&\approx& \frac{(e v_{F_i})^2}{3 \pi N_i(0)} 
+	\frac{\gamma_i}{(\varepsilon-\varepsilon')^2 + \gamma_i^2}
+\end{eqnarray*}
+
+Discussion of $A, A^2$.
+
+The full Hamiltonian is given by $H = H_{BCS} + H_{p-p}$.
+
+Shortcoming of the model. Momentum-angle averaging removes information about
+polarization, momentum of photon. The gap oscillates with its equilibrium value
+and not $\Delta_{\infty}$. Also, the results are an expansion in $A$ up to third
+order. Specifically, the gap in only included up to second order (the only
+nonzero term) which makes it hard to say when this approximation becomes
+invalid. The dependence of the gap on fluence is linear up to this order.
 
 \section{Single-band superconductivity}
-\begin{comment}
+\label{sec:singleband}
+
+Motivated by the experiment of Matsunaga et al. [] we choose parameters
+$\Delta_{\text{eq}}=\SI{1.3}{\milli\electronvolt}$,
+$\varepsilon_{F}=\SI{1}{\electronvolt}$, $m=0.78 m_e$, $s=1$ that reflect
+measurements and ab-initio calculations on NbN [DFT-reference].
+The Debye energy for NbN is order order of $\omega_D = \SI{5}{\milli\electronvolt}$, but
+for better numerical resolvability we choose $\omega_D =
+\SI{2}{\milli\electronvolt}$.
+
+A characteristic property of a pump pulse is its pulse length $\tau$ in units of the natural
+timescale of the superconductor, $\hbar/\Delta$. For $\tau \ll \hbar / \Delta$
+the superconductor is \textit{quenched}, while it is adiabatically driven in the
+opposite limit of $\tau \gg  \hbar / \Delta$. Here, we investigate a quench
+scenario with $\hbar\tau/\Delta=x$ by fitting the pulse form $A(t) = A_0 \exp\left( -(t-t')^2/2\tau^2
+\right)\cos \Omega t$ to the reported data of [Matsunaga]. The resulting
+electrical field waveform is shown in panel A of Fig. \ref{fig:singleband-gap}.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\columnwidth]{figures/fig1.pdf}
+	\caption{(A) Pulse field $E(t)$ realizing a qunech. (B) Spectral
+	composition $|A(\omega)|$. The gray shaded area illustrates the
+quasi-particle continuum. (C) Spectral compositon $A^2(\omega)$ of the second
+order component $A^2(t)$ responsible for excitation of collective modes. The
+peak around zero frequency corresponds to a DFG process while the peak at finite
+$\SI{1.2}{\tera\hertz}$ is a SFC process. (C) Evolution of the magnitude of the
+order parameter $\left|2\Delta(t)\right|$ for impuritiy strength varying from
+$\gamma/2\Delta=0.5$ to $20$ and Fourier spectrum of the gap oscillations (D).
+(E) Relaxation value $\Delta_{\infty}$ and amplitude of oscillation show a very
+similar dependence as a function of disorder strength which has maximum effect
+at around $\gamma \approx \Delta$.}
+
+$\Delta_{\infty}$ is given by the overlap of the pulse with the density of
+states of the quasiparticel continuum, 
+$$\Delta_{\infty} \propto
+\int_{}^{}d\omega N(\omega) A(\omega) \approx N(\varepsilon_F)
+\int_{\varepsilon_F}^{\infty}d\omega A(\omega)$$.
+\label{fig:singleband-gap}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\columnwidth]{figures/fig2.pdf}
+	\caption{Real part $\sigma'$ (A,C) and imaginary part $\sigma''$ (B,D)
+		of optical conductivities to first order in $A$ 
+	for various impurity scattering rates at $T=\SI{4}{\kelvin}$ (A,B) and
+various temperatures at $\gamma/2\Delta=10$. $\sigma'$ show a characteristic
+conductivity gap below $T_C$ and both $\sigma'$, $\sigma''$ diverge in the
+static limit.}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\columnwidth]{figures/fig3.pdf}
+	\caption{(A,B) Conductivity spectra for sweeped pump-probe delay $\delta
+	t_{\text{p-p}}$ to third order in $A$. (C) False-color plot of
+$\sigma' $ which was average-subtracted and normalized to show the oscillations.
+A phase shift occurs across the resonance at $2\Delta_{\text{eq}}$ of the quench pulse
+frequency. (D) Fourier spectrum of panel (C) showing that frequency of
+conductivity oscillation is peaked at $2\Delta_{\text{eq}}$.}
+\end{figure}
+%\begin{comment}
+\section{Multi-band superconductivity}
+\label{sec:multiband}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+Leggett mode has been potentially measured in between the two gaps. Discuss this
+and also refer to Schnyder Nature Comm. Figure out the parameter regime that
+inverted the gaps. Reproduce (or see what was wrong) with Murotani who also
+choose parameters such that the Leggett mode is inside the gap.
+
 \begin{figure}[H]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{comment}
+%\end{comment}
 \appendix

### 2020-10-19 multiband/gap-oscillations/higgs_mgb2.py

@@ -17,7 +17,7 @@ import gc
 code_version = {
     "1.0": "first version",
     "1.1": "pulse shape modified, now parameter te, te_pr",
-    "1.2": "U calculated from gap and v (gap and v are input parameters)"
+    "1.2": "U calculated from gap and v (gap and v are input parameters), r21e r21o saved"
 }
 if len(sys.argv)==3:
     job_ID = int(sys.argv[1])

### 2020-10-19 multiband/gap-oscillations/higgs_mgb2.py
standard commit

@@ -205,7 +205,7 @@ for p in params:
     # gscale=np.array([10])
     g = p["g"]
     pre_d0 = p["pre_d0"]
-    v = p["v"]
+    v_legget = p["v"]
     #pump parameters
     A0 = p["A0"]
     tau = p["tau"]
@@ -360,7 +360,7 @@ for p in params:
 
     B = 1/(kb*0.000001)
     ep = np.linspace(-wd, wd, Ne)
-    U = find_U(v, pre_d0, integrate.simps(0.5*1/np.sqrt(ep**2+pre_d0.reshape(2,1)**2)*np.tanh(B/2*np.sqrt(ep**2+pre_d0.reshape(2,1)**2)),ep))
+    U = find_U(v_legget, pre_d0, integrate.simps(0.5*1/np.sqrt(ep**2+pre_d0.reshape(2,1)**2)*np.tanh(B/2*np.sqrt(ep**2+pre_d0.reshape(2,1)**2)),ep))
     UN0 = U*N0[:, np.newaxis]
     print('U=',U)
     print('UN0=',UN0)
@@ -736,7 +736,7 @@ for p in params:
             #'gscale': gscale,
             'g': g,
             'U': U,
-            'v':v,
+            'v':v_legget,
             'd_eq0_T0': d_eq0_T0,
             'd_eq0': d_eq0,
             'd_eq': d_eq,
@@ -793,3 +793,4 @@ for p in params:
 # plot(t,np.sum(r21o[:,1,:Ne//2],axis=1).real)
 # plot(t,np.sum(r21e[:,0,:Ne//2],axis=1).real)
 # plot(t,np.sum(r21e[:,1,:Ne//2],axis=1).real)
+

### 2020-10-19 2dspectroscopy/pump-probe-THG/array_submit.sh
standard commit

@@ -1,0 +1,13 @@
+#!/bin/bash
+#SBATCH --array=0-63
+#SBATCH -p nodes # partition (queue)
+#SBATCH -N 1 # number of nodes
+#SBATCH -n 1 # number of cores
+#SBATCH --mem 5000 # memory pool for all cores
+#SBATCH -t 2-20:00 # time (D-HH:MM)
+#SBATCH -o message.out # STDOUT
+#SBATCH -e error.err # STDERR
+export OMP_NUM_THREADS=1
+module purge
+module add anaconda3
+python3 higgs_matsunaga.py parameters

### 2020-10-19 2dspectroscopy/pump-probe-THG/higgs_matsunaga.py

@@ -1,0 +1,600 @@
+#%%
+import numpy as np
+from numpy import sqrt
+# import matplotlib as mpl
+# mpl.use('Agg')
+import matplotlib.pyplot as plt
+from scipy import integrate
+from scipy import interpolate
+from scipy.fftpack import fft, fftfreq, fftshift
+import scipy
+import time
+import pickle
+import sys
+import os
+import gc
+
+code_version = {
+    "1.0": "first version",
+    "1.1": "pulse shape modified, now parameter te, te_pr"
+}
+if True:
+    job_ID = int(sys.argv[1])
+    task_ID = int(sys.argv[1])
+    task_count = int(sys.argv[2])+1
+else:
+    job_ID = -1
+    task_ID = -1
+    task_count = -1
+
+if task_ID != -1:
+    from parameters import params
+    params = params[task_ID::task_count]
+else:
+    from parameters import params
+    params = [ params[0] ]
+
+    # params = [
+    #     {
+    #         "Ne": 850,
+    #         "tmin": -2*(2*np.pi),
+    #         "tmax": 30*(2*np.pi),
+    #         "Nt": 3000,
+    #         "T": 0.56, #0.22
+    #         "wd":  10,
+    #         "s": np.array([1]),
+    #         "m": np.array([1.0]),
+    #         "ef": np.array([500]),
+    #         "g": np.array([10]),
+    #         "U": np.array([[0.2082]]),
+    #         "A0": -1,
+    #         "tau": 0.81,
+    #         "w":  0.36,
+    #         "te": -4.21,
+    #         "A0_pr": -0.1,
+    #         "tau_pr": 0.81,
+    #         "w_pr": 0.36,
+    #         "t_delay": 9,
+    #         "te_pr": -4.21
+    #     }
+    # ]
+
+
+for p in params:
+    Ne = p["Ne"]
+    tmin= p["tmin"]
+    tmax= p["tmax"]
+    Nt=p["Nt"]
+
+    t_points = np.linspace(tmin, tmax, Nt)
+
+
+    #superconductor parameters
+    T = p["T"]
+    wd = p["wd"]
+    s = p["s"]
[…]

### 2020-10-19 2dspectroscopy/pump-probe-THG/mega_script.sh

@@ -1,0 +1,34 @@
+#!/bin/bash
+
+MAX=159
+for i in `seq 0 1 ${MAX}`
+do
+	FILENAME=job_file_${i}.ll
+	echo "# @ shell=/bin/bash" > $FILENAME
+
+	echo "# Script for LoadLeveler job steps" >> $FILENAME
+
+	echo "# @ job_name = h-imp" >> $FILENAME
+	echo "# @ error  = error_${i}.err" >> $FILENAME
+	echo "# @ output = log_${i}.out" >> $FILENAME
+	echo "# @ job_type = MPICH" >> $FILENAME
+	echo "# @ node_usage = shared" >> $FILENAME
+
+	echo "# @ node = 1" >> $FILENAME
+	echo "# @ tasks_per_node = 1" >> $FILENAME
+	echo "# @ environment = COPY_ALL" >> $FILENAME
+	echo "# @ notification = never" >> $FILENAME
+	echo "# @ notify_user =" >> $FILENAME
+	echo "# @ class = 20core" >> $FILENAME
+	echo "# @ queue" >> $FILENAME
+
+	echo "# exit on error" >> $FILENAME
+	echo "set -e" >> $FILENAME
+
+	echo "export OMP_NUM_THREADS=1" >> $FILENAME
+
+	echo "python3 higgs_matsunaga.py ${i} ${MAX}" >> $FILENAME
+
+
+	llsubmit $FILENAME >> log.out
+done

### 2020-10-19 2dspectroscopy/pump-probe-THG/parameters.py

@@ -1,0 +1,94 @@
+import numpy as np
+
+u_temp = 116.032
+x=1
+params_ = [
+    {
+        "Ne": [500],
+        "tmin": [-75],
+        "tmax": [450],
+        "Nt": 3000,
+        "T": [1/u_temp],#,0.5,0.54,0.56],
+        "wd":  [1],
+        "s": np.array([1]),
+        "m": [ np.array([0.78]) ],
+        "ef": [ np.array([100]) ],
+        "g": [ np.array([5])*0.1258396834202397*2 ],
+        "U": [ np.array([[0.46]]) ],
+        "A0": [-25],
+        "tau": [5.37/x],
+        "w":  [0.04*x],
+        "A0_pr": [0.1,0],
+        "te": -40/x,
+        "tau_pr": [60],
+        "w_pr": [0.3, 0.27],
+        "t_delay": np.linspace(80,200,80),
+        "te_pr": 0
+    },
+    {
+        "Ne": [500],
+        "tmin": [-75],
+        "tmax": [450],
+        "Nt": 3000,
+        "T": [1/u_temp],#,0.5,0.54,0.56],
+        "wd":  [1],
+        "s": np.array([1]),
+        "m": [ np.array([0.78]) ],
+        "ef": [ np.array([100]) ],
+        "g": [ np.array([5])*0.1258396834202397*2 ],
+        "U": [ np.array([[0.46]]) ],
+        "A0": [0],
+        "tau": [5.37/x],
+        "w":  [0.04*x],
+        "A0_pr": [0.1],
+        "te": -40/x,
+        "tau_pr": [60],
+        "w_pr": [0.3, 0.27],
+        "t_delay": np.linspace(80,200,80),
+        "te_pr": 0
+    }
+]
+
+
+params = []
+for p in params_:
+    for A0 in p["A0"]:
+        for A0_pr in p["A0_pr"]:
+            for Ne in p["Ne"]:
+                for tmin in p["tmin"]:
+                    for tmax in p["tmax"]:
+                        for T in p["T"]:
+                            for wd in p["wd"]:
+                                for m in p["m"]:
+                                    for ef in p["ef"]:
+                                        for U in p["U"]:
+                                            for tau in p["tau"]:
+                                                for w in p["w"]:
+                                                    for tau_pr in p["tau_pr"]:
+                                                        for w_pr in p["w_pr"]:
+                                                            for g in p["g"]:
+                                                                for t_delay in p["t_delay"]:
+                                                                    params.append({
[…]

### 2020-10-20 singleband/conductivity-dirty/parameters1.py
standard commit

@@ -1,0 +1,94 @@
+import numpy as np
+
+u_temp = 116.032
+
+params_ = [
+    {
+        "Ne": [600],
+        "tmin": [-75],
+        "tmax": [450],
+        "Nt": 3000,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [2],
+        "s": np.array([1]),
+        "m": [ np.array([0.78]) ],
+        "ef": [ np.array([100]) ],
+        "g": [ np.array([x]) for x in [0.00001, 0.05,0.1,0.15,0.2,0.23, 0.25, 0.27, 0.3, 0.35, 0.4]],
+        "U": [ np.array([[0.46]]) ],
+        "A0": [-25],
+        "tau": [5.37],
+        "w":  [0.04],
+        "A0_pr": [0],
+        "te": -40,
+        "tau_pr": [5.37],
+        "w_pr": [0.04],
+        "t_delay": [0],
+        "te_pr": -40
+    },
+    {
+        "Ne": [600],
+        "tmin": [-75],
+        "tmax": [450],
+        "Nt": 3000,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [2],
+        "s": np.array([1]),
+        "m": [ np.array([0.78]) ],
+        "ef": [ np.array([100]) ],
+        "g": [ np.array([x]) for x in [0.00001, 0.05,0.1,0.15,0.2,0.23, 0.25, 0.27, 0.3, 0.35, 0.4]],
+        "U": [ np.array([[0.46]]) ],
+        "A0": [-25],
+        "tau": [5.37],
+        "w":  [0.04],
+        "A0_pr": [-2.5],
+        "te": -40,
+        "tau_pr": [5.37],
+        "w_pr": [0.04],
+        "t_delay": np.linspace(50,200,128),
+        "te_pr": -40
+    }
+]
+
+
+params = []
+for p in params_:
+    for A0 in p["A0"]:
+        for A0_pr in p["A0_pr"]:
+            for Ne in p["Ne"]:
+                for tmin in p["tmin"]:
+                    for tmax in p["tmax"]:
+                        for T in p["T"]:
+                            for wd in p["wd"]:
+                                for m in p["m"]:
+                                    for ef in p["ef"]:
+                                        for U in p["U"]:
+                                            for tau in p["tau"]:
+                                                for w in p["w"]:
+                                                    for tau_pr in p["tau_pr"]:
[…]

### 2020-10-20 singleband/conductivity-dirty/parameters2.py

@@ -1,0 +1,94 @@
+import numpy as np
+
+u_temp = 116.032
+
+params_ = [
+    {
+        "Ne": [600],
+        "tmin": [-75],
+        "tmax": [450],
+        "Nt": 3000,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [2],
+        "s": np.array([1]),
+        "m": [ np.array([0.78]) ],
+        "ef": [ np.array([100]) ],
+        "g": [ np.array([x]) for x in np.array([2,3,4,5,6,7,8,9,10])*0.1258396834202397*2 ],
+        "U": [ np.array([[0.46]]) ],
+        "A0": [-25],
+        "tau": [5.37],
+        "w":  [0.04],
+        "A0_pr": [0],
+        "te": -40,
+        "tau_pr": [5.37],
+        "w_pr": [0.04],
+        "t_delay": [0],
+        "te_pr": -40
+    },
+    {
+        "Ne": [600],
+        "tmin": [-75],
+        "tmax": [450],
+        "Nt": 3000,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [2],
+        "s": np.array([1]),
+        "m": [ np.array([0.78]) ],
+        "ef": [ np.array([100]) ],
+        "g": [ np.array([x]) for x in np.array([5,10])*0.1258396834202397*2 ],
+        "U": [ np.array([[0.46]]) ],
+        "A0": [-25],
+        "tau": [5.37],
+        "w":  [0.04],
+        "A0_pr": [-2.5],
+        "te": -40,
+        "tau_pr": [5.37],
+        "w_pr": [0.04],
+        "t_delay": np.linspace(50,200,128),
+        "te_pr": -40
+    }
+]
+
+
+params = []
+for p in params_:
+    for A0 in p["A0"]:
+        for A0_pr in p["A0_pr"]:
+            for Ne in p["Ne"]:
+                for tmin in p["tmin"]:
+                    for tmax in p["tmax"]:
+                        for T in p["T"]:
+                            for wd in p["wd"]:
+                                for m in p["m"]:
+                                    for ef in p["ef"]:
+                                        for U in p["U"]:
+                                            for tau in p["tau"]:
+                                                for w in p["w"]:
+                                                    for tau_pr in p["tau_pr"]:
+                                                        for w_pr in p["w_pr"]:
+                                                            for g in p["g"]:
+                                                                for t_delay in p["t_delay"]:
+                                                                    params.append({
[…]

### 2020-10-20 singleband/temp-dependence/higgs_matsunaga.py

@@ -1,0 +1,563 @@
+import numpy as np
+from numpy import sqrt
+# import matplotlib as mpl
+# mpl.use('Agg')
+import matplotlib.pyplot as plt
+from scipy import integrate
+from scipy import interpolate
+from scipy.fftpack import fft, fftfreq, fftshift
+import scipy
+import time
+import pickle
+import sys
+import os
+import gc
+
+code_version = {
+    "1.0": "first version",
+    "1.1": "pulse shape modified, now parameter te, te_pr"
+}
+#%%
+job_ID = int(sys.argv[1])
+task_ID = int(sys.argv[1])
+task_count = int(sys.argv[2])+1
+
+if task_ID != -1:
+    from parameters import params
+    params = params[task_ID::task_count]
+else:
+    from parameters import params
+    params = [ params[0] ]
+
+    # params = [
+    #     {
+    #         "Ne": 850,
+    #         "tmin": -2*(2*np.pi),
+    #         "tmax": 30*(2*np.pi),
+    #         "Nt": 3000,
+    #         "T": 0.56, #0.22
+    #         "wd":  10,
+    #         "s": np.array([1]),
+    #         "m": np.array([1.0]),
+    #         "ef": np.array([500]),
+    #         "g": np.array([10]),
+    #         "U": np.array([[0.2082]]),
+    #         "A0": -1,
+    #         "tau": 0.81,
+    #         "w":  0.36,
+    #         "te": -4.21,
+    #         "A0_pr": -0.1,
+    #         "tau_pr": 0.81,
+    #         "w_pr": 0.36,
+    #         "t_delay": 9,
+    #         "te_pr": -4.21
+    #     }
+    # ]
+
+
+for p in params:
+    Ne = p["Ne"]
+    tmin= p["tmin"]
+    tmax= p["tmax"]
+    Nt=p["Nt"]
+
+    t_points = np.linspace(tmin, tmax, Nt)
+
+
+    #superconductor parameters
+    T = p["T"]
+    wd = p["wd"]
+    s = p["s"]
+    nb = len(s) #nb=number of bands
+    m= p["m"]
+    ef= p["ef"]
+    # gscale=np.array([10])
[…]

### 2020-10-20 singleband/temp-dependence/mega_script.sh

@@ -1,0 +1,34 @@
+#!/bin/bash
+
+MAX=17
+for i in `seq 0 1 ${MAX}`
+do
+	FILENAME=job_file_${i}.ll
+	echo "# @ shell=/bin/bash" > $FILENAME
+
+	echo "# Script for LoadLeveler job steps" >> $FILENAME
+
+	echo "# @ job_name = h-imp" >> $FILENAME
+	echo "# @ error  = error_${i}.err" >> $FILENAME
+	echo "# @ output = log_${i}.out" >> $FILENAME
+	echo "# @ job_type = MPICH" >> $FILENAME
+	echo "# @ node_usage = shared" >> $FILENAME
+
+	echo "# @ node = 1" >> $FILENAME
+	echo "# @ tasks_per_node = 1" >> $FILENAME
+	echo "# @ environment = COPY_ALL" >> $FILENAME
+	echo "# @ notification = never" >> $FILENAME
+	echo "# @ notify_user =" >> $FILENAME
+	echo "# @ class = 20core" >> $FILENAME
+	echo "# @ queue" >> $FILENAME
+
+	echo "# exit on error" >> $FILENAME
+	echo "set -e" >> $FILENAME
+
+	echo "export OMP_NUM_THREADS=1" >> $FILENAME
+
+	echo "python3 higgs_matsunaga.py ${i} ${MAX}" >> $FILENAME
+
+
+	llsubmit $FILENAME >> log.out
+done

### 2020-10-20 singleband/temp-dependence/parameters.py

@@ -1,0 +1,72 @@
+import numpy as np
+
+u_temp = 116.032
+
+params_ = [
+    {
+        "Ne": [600],
+        "tmin": [-75],
+        "tmax": [450],
+        "Nt": 3000,
+        "T": np.arange(1,18)/u_temp,#,0.5,0.54,0.56],
+        "wd":  [2],
+        "s": np.array([1]),
+        "m": [ np.array([0.78]) ],
+        "ef": [ np.array([100]) ],
+        "g": [ np.array([10])*0.1258396834202397*2 ],
+        "U": [ np.array([[0.46]]) ],
+        "A0": [-25],
+        "tau": [5.37],
+        "w":  [0.04],
+        "A0_pr": [0],
+        "te": -40,
+        "tau_pr": [5.37],
+        "w_pr": [0.04],
+        "t_delay": [0],
+        "te_pr": -40
+    }
+]
+
+
+params = []
+for p in params_:
+    for A0 in p["A0"]:
+        for A0_pr in p["A0_pr"]:
+            for Ne in p["Ne"]:
+                for tmin in p["tmin"]:
+                    for tmax in p["tmax"]:
+                        for T in p["T"]:
+                            for wd in p["wd"]:
+                                for m in p["m"]:
+                                    for ef in p["ef"]:
+                                        for U in p["U"]:
+                                            for tau in p["tau"]:
+                                                for w in p["w"]:
+                                                    for tau_pr in p["tau_pr"]:
+                                                        for w_pr in p["w_pr"]:
+                                                            for g in p["g"]:
+                                                                for t_delay in p["t_delay"]:
+                                                                    params.append({
+                                                                        "Ne": Ne,
+                                                                        "tmin": tmin,
+                                                                        "tmax": tmax,
+                                                                        "Nt": p["Nt"],
+                                                                        "T": T,
+                                                                        "wd": wd,
+                                                                        "s": p["s"],
+                                                                        "m": m,
+                                                                        "ef": ef,
+                                                                        "g": g,
+                                                                        "U": U,
+                                                                        "A0": A0,
+                                                                        "tau": tau,
+                                                                        "w":  w,
+                                                                        "te": p["te"],
+                                                                        "A0_pr": A0_pr,
+                                                                        "tau_pr": tau_pr,
+                                                                        "w_pr": w_pr,
+                                                                        "t_delay": t_delay,
+                                                                        "te_pr": p["te_pr"]
+                                                                    })
+
+print('parameters generated')

### 2020-10-20 multiband/pl_multiband.py
standard commit

@@ -1,0 +1,771 @@
+#%%
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+import scipy
+from scipy.fftpack import fftfreq, fftshift
+import os
+from mpl_toolkits.mplot3d import Axes3D
+from cycler import cycler
+import matplotlib as mpl
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+folder = 'gap-oscillations'
+files = glob.glob(f'{folder}/*.pickle')
+
+save_plots = False
+
+def savefig(fname, transparent=True):
+    if save_plots:
+        plt.savefig(fname, transparent=transparent)
+
+def nmax(x):
+    return np.max(np.abs(x))
+
+def nm(x):
+    return x / np.max(np.abs(x))
+
+def fft(t,f, inverse=False):
+    T = max(t) - min(t)
+    Nt = len(t)
+    dt = T/Nt
+
[…]

### 2020-10-22 multiband/pl_conductivity.py
a

@@ -27,7 +27,7 @@ plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
 plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
 
-folder = 'gap-oscillations'
+folder = 'conductivity'
 files = glob.glob(f'{folder}/*.pickle')
 
 save_plots = False
@@ -55,9 +55,9 @@ def fft(t,f, inverse=False):
         idx = np.argsort(xw)
         xw = xw[idx]
         f = f[idx]
-        fw = scipy.ifft(f, axis=0)/np.sqrt(Nt)*Nt
+        fw = scipy.fft.ifft(f, axis=0)/np.sqrt(Nt)*Nt
     else:
-        fw = scipy.fft(f, axis=0)/np.sqrt(Nt)
+        fw = scipy.fft.fft(f, axis=0)/np.sqrt(Nt)
         xw = np.concatenate([xw[:Nt//2], xw[Nt//2:]-2*np.pi/dt])
         idx = np.argsort(xw)
         xw = xw[idx]
@@ -82,7 +82,7 @@ for f in files:
         reader.close()
 
 #%%
-def values(key):
+def values(key,res=res):
     vals = []
     for r in res:
         entry = r[key]
@@ -156,29 +156,34 @@ def plotHiggs(r, offset = 0.5, plot=True):
     w = r['w']
     d_eq = r['d_eq'][:,0,0]
     g = r['g']
+    A = r['A']
 
-    t_ = t[t>offset]
-    d_ = d[t>offset]
+    # determine left boundary for fft
+    tleft = 3*tau+1
+    tright = 140
+    cond = np.logical_and(t>=tleft, t<=tright)
+
+    t_ = t[cond]
+    d_ = d[cond]
     d_ -= np.mean(d_, axis=0)
     if plot:
-        plt.figure('Higgs')
+        plt.figure('Higgs', figsize=(5,2.5))
         plt.clf()
         plt.subplot(121)
+        plt.axvspan(tleft,tright,facecolor='gray', alpha=0.3)
         plt.plot(t,d)
-        plt.axvline(offset, c='gray', lw=2,ls='--')
[…]

### 2020-10-23 multiband/pl_conductivity.py
a

@@ -213,7 +213,7 @@ def plotHiggsLast(r, offset=0):
     title(r)
 
 def conductivity(r, order=1, plot=True, begin=None, end=None, subtract=True):
-    r2 = sel(A0=r['A0'], g=r['g'], A0_pr=0, tau=r['tau'], w=r['w'])[0]
+    r2 = sel(first=True, A0=r['A0'], g=r['g'], A0_pr=0, tau=r['tau'], w=r['w'], t_delay=r['t_delay'], v=r['v'])
     # r3 = sel(T=0.22, t_delay=r['t_delay'], A0=0, A0_pr=r['A0_pr'])[0]
 
     if order == 1:
@@ -310,7 +310,7 @@ def conductivity(r, order=1, plot=True, begin=None, end=None, subtract=True):
         plt.xlabel(f'$\omega$')
         plt.tight_layout()
     # sl2 = np.logical_and(w>0, w<4*d_eq[0])
-    sl2 = np.logical_and(w>0, w<6*gap)
+    sl2 = np.logical_and(w>0, w<4*gap)
     return w[sl2], s[sl2]
 
 def plotLeggett(r, offset=0):
@@ -548,7 +548,7 @@ def cond_pcolor():
         # return x/(mean)
         return x
 
-    plt.pcolormesh(w*u_e*meV_to_THz, delays*u_t, nm2(np.abs(cc.real)), cmap=cm, shading='gouraud')#, vmin=0.9, vmax=1.1)
+    plt.pcolormesh(w*u_e*meV_to_THz, delays*u_t, nm2(np.abs(cc.real)), cmap=cm)#, shading='gouraud')#, vmin=0.9, vmax=1.1)
     plt.axvline(2*gap*u_e*meV_to_THz)
     plt.xlabel('Frequency (THz)')
     plt.ylabel('$\delta t_{pp}$ (ps)')
@@ -693,6 +693,8 @@ pulses = pulses_sort
 
 save = False
 
+gammas = [0.0001,10]
+
 cleanclean= np.array([gammas[0], gammas[0]])
 cleandirty = np.array([gammas[0], gammas[1]])
 dirtyclean = np.array([gammas[1], gammas[0]])
@@ -779,8 +781,11 @@ cc3 = []
 rr = []
 # delays = delays[1:]
 s_imp = 8
+delays = delays[5:]
 for d in delays:
[…]

### 2020-10-23 singleband/pl_singleband2.py
a

@@ -1,0 +1,742 @@
+#%%
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+import scipy
+from scipy.fftpack import fftfreq, fftshift
+import os
+from mpl_toolkits.mplot3d import Axes3D
+from cycler import cycler
+import matplotlib as mpl
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+folder = 'conductivity-dirty'
+files = glob.glob(f'{folder}/*.pickle')
+
+save_plots = False
+
+def savefig(fname, transparent=True):
+    if save_plots:
+        plt.savefig(fname, transparent=transparent)
+
+def nmax(x):
+    return np.max(np.abs(x))
+
+def nm(x):
+    return x / np.max(np.abs(x))
+
+def fft(t,f, inverse=False):
+    T = max(t) - min(t)
+    Nt = len(t)
+    dt = T/Nt
+
[…]

### 2020-10-23 singleband/pl_temp-dep.py

@@ -1,0 +1,623 @@
+#%%
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+import scipy
+from scipy.fftpack import fftfreq, fftshift
+import os
+from mpl_toolkits.mplot3d import Axes3D
+from cycler import cycler
+import matplotlib as mpl
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+folder = 'temp-dependence'
+files = glob.glob(f'{folder}/*.pickle')
+
+save_plots = True
+
+def savefig(fname, transparent=True):
+    if save_plots:
+        plt.savefig(fname, transparent=transparent)
+
+def nmax(x):
+    return np.max(np.abs(x))
+
+def nm(x):
+    return x / np.max(np.abs(x))
+
+def fft(t,f, inverse=False):
+    T = max(t) - min(t)
+    Nt = len(t)
+    dt = T/Nt
+
[…]

### 2020-10-23 multiband/pl_conductivity.py
a

@@ -212,32 +212,33 @@ def plotHiggsLast(r, offset=0):
     plt.ylabel(f'Re$\delta \Delta$')
     title(r)
 
-def conductivity(r, order=1, plot=True, begin=None, end=None, subtract=True):
+def conductivity(r, order=1, plot=True, begin=None, end=None, subtract=True, wlen=-1):
     r2 = sel(first=True, A0=r['A0'], g=r['g'], A0_pr=0, tau=r['tau'], w=r['w'], t_delay=r['t_delay'], v=r['v'])
-    # r3 = sel(T=0.22, t_delay=r['t_delay'], A0=0, A0_pr=r['A0_pr'])[0]
+    r3 = sel(first=True, A0=0, g=r['g'], A0_pr=r['A0_pr'], tau=r['tau'], w=r['w'], t_delay=r['t_delay'], v=r['v'])
 
     if order == 1:
         jd = r['jd_1']
         jp = r['jp_1']
         jd2 = r2['jd_1']
         jp2 = r2['jp_1']
-        # jd3 = r3['jd_1']
-        # jp3 = r3['jp_1']
+        jd3 = r3['jd_1']
+        jp3 = r3['jp_1']
         lb='$j_1$'
     else:
         jd = r['jd_3']
         jp = r['jp_3']
         jd2 = r2['jd_3']
         jp2 = r2['jp_3']
-        # jd3 = r3['jd_3']
-        # jp3 = r3['jp_3']
+        jd3 = r3['jd_3']
+        jp3 = r3['jp_3']
         lb = '$j_3$'
     j = jd + jp
     j2 = jd2 + jp2
-    # j3 = jd3 + jp3
+    j3 = jd3 + jp3
     if subtract:
-        j = j - j2
+        j = j - j2# - j3
     t = r['t']
+
     tau = r['tau']
     tau_pr = r['tau_pr']
     freq = r['w']
@@ -250,6 +251,8 @@ def conductivity(r, order=1, plot=True, begin=None, end=None, subtract=True):
     else:
         A = A1
         e = e1
+
+
     d_eq = r['d_eq'][:,0,0]
     tmin = np.min(t)
     tmax = np.max(t)
@@ -260,12 +263,11 @@ def conductivity(r, order=1, plot=True, begin=None, end=None, subtract=True):
     T = tmax - tmin
 
     if begin==None:
[…]

### 2020-10-23 multiband/pl_conductivity.py
a

@@ -781,7 +781,7 @@ for i,pulse in z(pulses):
 
                 r0 = sel(first=True, A0=1, A0_pr=0, tau=pulse['tau'], w=pulse['w'], v=v, g=case)
                 plotHiggsLeggett(r0)
-                savefig(f'figs/HL-A{i}-v{j}-imp{k}.pdf')
+                plt.savefig(f'figs/HL-A{i}-v{j}-imp{k}.pdf')
                 cond_3d()
                 plt.figure('cc3d')
                 plt.savefig(f'figs/cond3d_real-A{i}-v{j}-imp{k}.pdf')

### 2020-10-23 multiband/conductivity/mega_script.sh
standard commit

@@ -1,0 +1,34 @@
+#!/bin/bash
+
+MAX=119
+for i in `seq 0 1 ${MAX}`
+do
+	FILENAME=job_file_${i}.ll
+	echo "# @ shell=/bin/bash" > $FILENAME
+
+	echo "# Script for LoadLeveler job steps" >> $FILENAME
+
+	echo "# @ job_name = h-imp" >> $FILENAME
+	echo "# @ error  = error_${i}.err" >> $FILENAME
+	echo "# @ output = log_${i}.out" >> $FILENAME
+	echo "# @ job_type = MPICH" >> $FILENAME
+	echo "# @ node_usage = shared" >> $FILENAME
+
+	echo "# @ node = 1" >> $FILENAME
+	echo "# @ tasks_per_node = 1" >> $FILENAME
+	echo "# @ environment = COPY_ALL" >> $FILENAME
+	echo "# @ notification = never" >> $FILENAME
+	echo "# @ notify_user =" >> $FILENAME
+	echo "# @ class = 20core" >> $FILENAME
+	echo "# @ queue" >> $FILENAME
+
+	echo "# exit on error" >> $FILENAME
+	echo "set -e" >> $FILENAME
+
+	echo "export OMP_NUM_THREADS=1" >> $FILENAME
+
+	echo "python3 higgs_mgb2.py ${i} ${MAX}" >> $FILENAME
+
+
+	llsubmit $FILENAME >> log.out
+done

### 2020-10-23 multiband/conductivity/parameters.py

@@ -1,0 +1,99 @@
+import numpy as np
+
+u_temp = 116.032
+params_ = [
+    {
+        "Ne": [370],
+        "tmin": [-25],
+        "tmax": [120],
+        # "tmax": [450],
+        "Nt": 3000,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10,10]) ],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": [0.2],
+        "A0": [1,0],
+        "tau": [4],
+        "w":  [0.7],
+        "A0_pr": [0.1, 0],
+        "te": 0,
+        "tau_pr": [1.5],
+        "w_pr": [1],
+        "t_delay": np.linspace(0,60,60),
+        "te_pr": 0
+    },
+    {
+        "Ne": [370],
+        "tmin": [-25],
+        "tmax": [120],
+        # "tmax": [450],
+        "Nt": 3000,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([50,50]) ],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": [0,0.2],
+        "A0": [1,0],
+        "tau": [4],
+        "w":  [0.7],
+        "A0_pr": [0.1, 0],
+        "te": 0,
+        "tau_pr": [1.5],
+        "w_pr": [1],
+        "t_delay": np.linspace(0,60,60),
+        "te_pr": 0
+    }
+]
+
+
+params = []
+for p in params_:
+    for Ne in p["Ne"]:
+        for tmin in p["tmin"]:
+            for tmax in p["tmax"]:
+                for T in p["T"]:
+                    for wd in p["wd"]:
+                        for m in p["m"]:
+                            for ef in p["ef"]:
+                                for v in p["v"]:
+                                    for tau in p["tau"]:
+                                        for w in p["w"]:
+                                            for tau_pr in p["tau_pr"]:
+                                                for w_pr in p["w_pr"]:
+                                                    for g in p["g"]:
+                                                        for A0 in p["A0"]:
+                                                            for A0_pr in p["A0_pr"]:
[…]

### 2020-10-23 multiband/conductivity/parameters2.py

@@ -1,0 +1,99 @@
+import numpy as np
+
+u_temp = 116.032
+params_ = [
+    {
+        "Ne": [370],
+        "tmin": [-25],
+        "tmax": [120],
+        # "tmax": [450],
+        "Nt": 3000,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10,10]) ],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": [0, 0.02],
+        "A0": [1,0],
+        "tau": [4],
+        "w":  [0.7],
+        "A0_pr": [0.1, 0],
+        "te": 0,
+        "tau_pr": [1.5],
+        "w_pr": [1],
+        "t_delay": np.linspace(0,60,60),
+        "te_pr": 0
+    },
+    {
+        "Ne": [370],
+        "tmin": [-80],
+        "tmax": [120],
+        # "tmax": [450],
+        "Nt": 3000,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10,10]), np.array([0.001,10]), np.array([10,0.001]), np.array([0.001,0.001]) ],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": [0.2],
+        "A0": [1,0],
+        "tau": [16],
+        "w":  [0.3, 0.7],
+        "A0_pr": [0.1,0],
+        "te": 0,
+        "tau_pr": [1.5],
+        "w_pr": [1],
+        "t_delay": np.linspace(0,60,60),
+        "te_pr": 0
+    }
+]
+
+
+params = []
+for p in params_:
+    for Ne in p["Ne"]:
+        for tmin in p["tmin"]:
+            for tmax in p["tmax"]:
+                for T in p["T"]:
+                    for wd in p["wd"]:
+                        for m in p["m"]:
+                            for ef in p["ef"]:
+                                for v in p["v"]:
+                                    for tau in p["tau"]:
+                                        for w in p["w"]:
+                                            for tau_pr in p["tau_pr"]:
+                                                for w_pr in p["w_pr"]:
+                                                    for g in p["g"]:
[…]

### 2020-10-23 multiband/pl_gap-oscillations.py
a

@@ -1,0 +1,933 @@
+#%%
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+import scipy
+from scipy.fftpack import fftfreq, fftshift
+import os
+from mpl_toolkits.mplot3d import Axes3D
+from cycler import cycler
+import matplotlib as mpl
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+folder = 'gap-oscillations'
+files = glob.glob(f'{folder}/*.pickle')
+
+save_plots = False
+
+def savefig(fname, transparent=True):
+    if save_plots:
+        plt.savefig(fname, transparent=transparent)
+
+def nmax(x):
+    return np.max(np.abs(x))
+
+def nm(x):
+    return x / np.max(np.abs(x))
+
+def fft(t,f, inverse=False):
+    T = max(t) - min(t)
+    Nt = len(t)
+    dt = T/Nt
+
[…]

### 2020-10-24 multiband/conductivity/mega_script.sh
standard commit

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-MAX=119
+MAX=319
 for i in `seq 0 1 ${MAX}`
 do
 	FILENAME=job_file_${i}.ll
@@ -19,7 +19,7 @@ do
 	echo "# @ environment = COPY_ALL" >> $FILENAME
 	echo "# @ notification = never" >> $FILENAME
 	echo "# @ notify_user =" >> $FILENAME
-	echo "# @ class = 20core" >> $FILENAME
+	echo "# @ class = 28core" >> $FILENAME
 	echo "# @ queue" >> $FILENAME
 
 	echo "# exit on error" >> $FILENAME

### 2020-10-24 multiband/conductivity/parameters.py

@@ -13,36 +13,12 @@ params_ = [
         "s": np.array([1,-1]),
         "m": [ np.array([0.85, 1.38]) ],
         "ef": [ np.array([290, 70]) ],
-        "g": [ np.array([10,10]) ],
+        "g": [ np.array([10,10]), np.array([0.001,0.001])  ],
         "pre_d0": np.array([0.3,0.7]),
-        "v": [0.2],
+        "v": [0.01,0.03,0.05],
         "A0": [1,0],
-        "tau": [4],
-        "w":  [0.7],
-        "A0_pr": [0.1, 0],
-        "te": 0,
-        "tau_pr": [1.5],
-        "w_pr": [1],
-        "t_delay": np.linspace(0,60,60),
-        "te_pr": 0
-    },
-    {
-        "Ne": [370],
-        "tmin": [-25],
-        "tmax": [120],
-        # "tmax": [450],
-        "Nt": 3000,
-        "T": [4/u_temp],#,0.5,0.54,0.56],
-        "wd":  [5],
-        "s": np.array([1,-1]),
-        "m": [ np.array([0.85, 1.38]) ],
-        "ef": [ np.array([290, 70]) ],
-        "g": [ np.array([50,50]) ],
-        "pre_d0": np.array([0.3,0.7]),
-        "v": [0,0.2],
-        "A0": [1,0],
-        "tau": [4],
-        "w":  [0.7],
+        "tau": [7],
+        "w":  [0],
         "A0_pr": [0.1, 0],
         "te": 0,
         "tau_pr": [1.5],

### 2020-10-24 multiband/driving/mega_script.sh

@@ -1,0 +1,34 @@
+#!/bin/bash
+
+MAX=159
+for i in `seq 0 1 ${MAX}`
+do
+	FILENAME=job_file_${i}.ll
+	echo "# @ shell=/bin/bash" > $FILENAME
+
+	echo "# Script for LoadLeveler job steps" >> $FILENAME
+
+	echo "# @ job_name = h-imp" >> $FILENAME
+	echo "# @ error  = error_${i}.err" >> $FILENAME
+	echo "# @ output = log_${i}.out" >> $FILENAME
+	echo "# @ job_type = MPICH" >> $FILENAME
+	echo "# @ node_usage = shared" >> $FILENAME
+
+	echo "# @ node = 1" >> $FILENAME
+	echo "# @ tasks_per_node = 1" >> $FILENAME
+	echo "# @ environment = COPY_ALL" >> $FILENAME
+	echo "# @ notification = never" >> $FILENAME
+	echo "# @ notify_user =" >> $FILENAME
+	echo "# @ class = 20core" >> $FILENAME
+	echo "# @ queue" >> $FILENAME
+
+	echo "# exit on error" >> $FILENAME
+	echo "set -e" >> $FILENAME
+
+	echo "export OMP_NUM_THREADS=1" >> $FILENAME
+
+	echo "python3 higgs_mgb2.py ${i} ${MAX}" >> $FILENAME
+
+
+	llsubmit $FILENAME >> log.out
+done

### 2020-10-24 multiband/driving/parameters.py

@@ -1,0 +1,75 @@
+import numpy as np
+
+u_temp = 116.032
+params_ = [
+    {
+        "Ne": [440],
+        "tmin": [-120],
+        "tmax": [100],
+        # "tmax": [450],
+        "Nt": 3000,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10,10]), np.array([0.001,0.001]), np.array([0.001,10]), np.array([10,0.001]) ],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": [0.02, 0.05, 0.2, 0.5],
+        "A0": [1],
+        "tau": [30],
+        "w":  np.linspace(0.1,0.9,81),
+        "A0_pr": [0],
+        "te": 0,
+        "tau_pr": [1.5],
+        "w_pr": [1],
+        "t_delay": [0],
+        "te_pr": 0
+    }
+]
+
+
+params = []
+for p in params_:
+    for Ne in p["Ne"]:
+        for tmin in p["tmin"]:
+            for tmax in p["tmax"]:
+                for T in p["T"]:
+                    for wd in p["wd"]:
+                        for m in p["m"]:
+                            for ef in p["ef"]:
+                                for v in p["v"]:
+                                    for tau in p["tau"]:
+                                        for w in p["w"]:
+                                            for tau_pr in p["tau_pr"]:
+                                                for w_pr in p["w_pr"]:
+                                                    for g in p["g"]:
+                                                        for A0 in p["A0"]:
+                                                            for A0_pr in p["A0_pr"]:
+                                                                for t_delay in p["t_delay"]:
+                                                                    if A0_pr != 0 or A0 != 0:
+                                                                        params.append({
+                                                                            "Ne": Ne,
+                                                                            "tmin": tmin,
+                                                                            "tmax": tmax,
+                                                                            "Nt": p["Nt"],
+                                                                            "T": T,
+                                                                            "wd": wd,
+                                                                            "s": p["s"],
+                                                                            "m": m,
+                                                                            "ef": ef,
+                                                                            "g": g,
+                                                                            "pre_d0": p["pre_d0"],
+                                                                            "v": v,
+                                                                            "A0": A0,
+                                                                            "tau": tau,
+                                                                            "w":  w,
[…]

### 2020-10-25 multiband/pl_driving.py
a

@@ -27,7 +27,7 @@ plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
 plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
 
-folder = 'conductivity'
+folder = 'leggett-driving'
 files = glob.glob(f'{folder}/*.pickle')
 
 save_plots = False
@@ -82,7 +82,7 @@ for f in files:
         reader.close()
 
 #%%
-def values(key,res=res):
+def values(key):
     vals = []
     for r in res:
         entry = r[key]
@@ -212,33 +212,32 @@ def plotHiggsLast(r, offset=0):
     plt.ylabel(f'Re$\delta \Delta$')
     title(r)
 
-def conductivity(r, order=1, plot=True, begin=None, end=None, subtract=True, wlen=-1):
-    r2 = sel(first=True, A0=r['A0'], g=r['g'], A0_pr=0, tau=r['tau'], w=r['w'], t_delay=r['t_delay'], v=r['v'])
-    r3 = sel(first=True, A0=0, g=r['g'], A0_pr=r['A0_pr'], tau=r['tau'], w=r['w'], t_delay=r['t_delay'], v=r['v'])
+def conductivity(r, order=1, plot=True, begin=None, end=None, subtract=True):
+    r2 = sel(A0=r['A0'], g=r['g'], A0_pr=0)[0]
+    # r3 = sel(T=0.22, t_delay=r['t_delay'], A0=0, A0_pr=r['A0_pr'])[0]
 
     if order == 1:
         jd = r['jd_1']
         jp = r['jp_1']
         jd2 = r2['jd_1']
         jp2 = r2['jp_1']
-        jd3 = r3['jd_1']
-        jp3 = r3['jp_1']
+        # jd3 = r3['jd_1']
+        # jp3 = r3['jp_1']
         lb='$j_1$'
     else:
         jd = r['jd_3']
         jp = r['jp_3']
         jd2 = r2['jd_3']
         jp2 = r2['jp_3']
-        jd3 = r3['jd_3']
-        jp3 = r3['jp_3']
+        # jd3 = r3['jd_3']
+        # jp3 = r3['jp_3']
         lb = '$j_3$'
     j = jd + jp
     j2 = jd2 + jp2
-    j3 = jd3 + jp3
[…]

### 2020-10-26 singleband/pl_current.py
a

@@ -1,0 +1,662 @@
+#%%
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+import scipy
+from scipy.fftpack import fftfreq, fftshift
+import os
+from mpl_toolkits.mplot3d import Axes3D
+from cycler import cycler
+import matplotlib as mpl
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+folder = 'conductivity-dirty'
+files = glob.glob(f'{folder}/*.pickle')
+
+save_plots = False
+
+def savefig(fname, transparent=True):
+    if save_plots:
+        plt.savefig(fname, transparent=transparent)
+
+def nmax(x):
+    return np.max(np.abs(x))
+
+def nm(x):
+    return x / np.max(np.abs(x))
+
+def fft(t,f, inverse=False):
+    T = max(t) - min(t)
+    Nt = len(t)
+    dt = T/Nt
+
[…]

### 2020-10-27 multiband/pl_conductivity.py
a

@@ -214,7 +214,7 @@ def plotHiggsLast(r, offset=0):
 
 def conductivity(r, order=1, plot=True, begin=None, end=None, subtract=True, wlen=-1):
     r2 = sel(first=True, A0=r['A0'], g=r['g'], A0_pr=0, tau=r['tau'], w=r['w'], t_delay=r['t_delay'], v=r['v'])
-    r3 = sel(first=True, A0=0, g=r['g'], A0_pr=r['A0_pr'], tau=r['tau'], w=r['w'], t_delay=r['t_delay'], v=r['v'])
+    r3 = sel(first=True, A0=0, g=r['g'], A0_pr=r['A0_pr'], tau=r['tau'], w=r['w'], v=r['v'])
 
     if order == 1:
         jd = r['jd_1']
@@ -706,12 +706,13 @@ cleanclean= np.array([gammas[0], gammas[0]])
 cleandirty = np.array([gammas[0], gammas[1]])
 dirtyclean = np.array([gammas[1], gammas[0]])
 dirtydirty = np.array([gammas[1], gammas[1]])
+superdirty = np.array([gammas[2], gammas[2]])
 cc_ = cleanclean
 cd_ = cleandirty
 dc_ = dirtyclean
 dd_ = dirtydirty
 
-fourcases = [cleanclean, cleandirty, dirtyclean, dirtydirty]
+fourcases = [cleanclean, cleandirty, dirtyclean, dirtydirty, superdirty]
 lwc = 0.2
 lwd = 1
 lw_fourcases = [[lwc,lwc],[lwc,lwd],[lwd,lwc],[lwd,lwd]]
@@ -750,9 +751,11 @@ def lw_imp(lw):
     return a
 
 for i,pulse in z(pulses):
-    r0 = sel(first=True, A0=1, A0_pr=0, tau=pulse['tau'], w=pulse['w'])
+    pulse_tau = pulse['tau']
+    pulse_w = pulse['w']
+    r0 = sel(first=True, A0=1, A0_pr=0, tau=pulse_tau, w=pulse_w)
     plotA(r0)
-    plt.savefig(f'figs2/A{i}.pdf')
+    plt.savefig(f'figs3/A{i}.pdf')
     plt.pause(0.01)
     for j, v in z(vs):
         for k, case in z(fourcases):
@@ -760,7 +763,7 @@ for i,pulse in z(pulses):
             cc3 = []
             for d in delays:
[…]

### 2020-10-27 multiband/pl_driving.py

@@ -9,6 +9,7 @@ import os
 from mpl_toolkits.mplot3d import Axes3D
 from cycler import cycler
 import matplotlib as mpl
+from scipy.signal import find_peaks
 
 CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
 tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
@@ -27,7 +28,8 @@ plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
 plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
 plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
 
-folder = 'leggett-driving'
+folder = 'leggett-driving4'
+# folder = 'driving'
 files = glob.glob(f'{folder}/*.pickle')
 
 save_plots = False
@@ -670,7 +672,7 @@ dirtyclean = np.array([gammas[1], gammas[0]])
 dirtydirty = np.array([gammas[1], gammas[1]])
 
 fourcases = [cleanclean, cleandirty, dirtyclean, dirtydirty]
-fourcases = [cleanclean]
+# fourcases = [cleanclean]
 lwc = 0.3
 lwd = 0.6
 lw_fourcases = [[lwc,lwc],[lwc,lwd],[lwd,lwc],[lwd,lwd]]
@@ -697,7 +699,8 @@ cm = 'rainbow'
 def z(array):
     return zip(np.arange(len(array)), array)
 
-
+vv = []
+en = []
 for j, v in z(vs):
     plt.pause(0.1)
     for i, case in z(fourcases):
@@ -712,15 +715,24 @@ for j, v in z(vs):
             r = r[0]
             j1 = r['jd_1'] + r['jp_1']
             j3 = r['jd_3'] + r['jp_3']
-            # plt.plot(t,nm(j1))
-            # plt.plot(t,nm(j3))
 
             tw, j1w = fft(t,j1)
             tw, j3w = fft(t,j3)
 
-            # plt.plot(tw/w, nm(np.abs(j3w)))
-            # plt.plot(tw/w, np.abs(j3w))
[…]

### 2020-10-27 singleband/pl_current.py

@@ -55,9 +55,9 @@ def fft(t,f, inverse=False):
         idx = np.argsort(xw)
         xw = xw[idx]
         f = f[idx]
-        fw = scipy.ifft(f, axis=0)/np.sqrt(Nt)*Nt
+        fw = scipy.fft.ifft(f, axis=0)/np.sqrt(Nt)*Nt
     else:
-        fw = scipy.fft(f, axis=0)/np.sqrt(Nt)
+        fw = scipy.fft.fft(f, axis=0)/np.sqrt(Nt)
         xw = np.concatenate([xw[:Nt//2], xw[Nt//2:]-2*np.pi/dt])
         idx = np.argsort(xw)
         xw = xw[idx]
@@ -616,47 +616,57 @@ cc1 = []
 cc3 = []
 rr = []
 delays = delays[1:]
-s_imp = 8
+s_imp = 5
+meas1 = []
+meas3 = []
 for d in delays:
     r = sel(first=True, t_delay=d, A0_pr=A0_prs[0], g=gammas[s_imp])
     r_ = sel(first=True, t_delay=0, A0_pr=0, g=gammas[s_imp])
+
+    #1A are 2.38459E-7 Js/Cm
+    u_A = 2.38459E-7
+    A,e = getE(r)
+    Amax = np.max(np.abs(A))
+
+    ############################
+    A0 = 0.5E-8 # Js/Cm
+    ############################
+
+    Ascale = A0 / (Amax * u_A)
+    # Ascale = 0.1
+
     # r2 = sel(A0=r['A0'], g=r['g'], A0_pr=0)[0]
     t = r['t']
-    j1 = r['jp_1'] + r['jp_1']
-    j3 = r['jp_3'] + r['jp_3']
-    j1_ = r_['jp_1'] + r_['jp_1']
-    j3_ = r_['jp_3'] + r_['jp_3']
+    j1 = r['jp_1'] + r['jd_1']
+    j3 = r['jp_3'] + r['jd_3']
+    j1_ = r_['jp_1'] + r_['jd_1']
+    j3_ = r_['jp_3'] + r_['jd_3']
     j1 = j1 - j1_
     j3 = j3 - j3_
 
 
-    begin = t[0] + d - delays[0] + 60
-    end = (d-delays[0]) + t[-1] - (delays[-1] - delays[0]) - 220
+    begin = t[0] + d - delays[0]
[…]

### 2020-10-27 singleband/pl_singleband2.py

@@ -55,9 +55,9 @@ def fft(t,f, inverse=False):
         idx = np.argsort(xw)
         xw = xw[idx]
         f = f[idx]
-        fw = scipy.ifft(f, axis=0)/np.sqrt(Nt)*Nt
+        fw = scipy.fft.ifft(f, axis=0)/np.sqrt(Nt)*Nt
     else:
-        fw = scipy.fft(f, axis=0)/np.sqrt(Nt)
+        fw = scipy.fft.fft(f, axis=0)/np.sqrt(Nt)
         xw = np.concatenate([xw[:Nt//2], xw[Nt//2:]-2*np.pi/dt])
         idx = np.argsort(xw)
         xw = xw[idx]
@@ -579,6 +579,7 @@ cc3 = []
 rr = []
 delays = delays[1:]
 s_imp = 8
+# s_imp = 3
 for d in delays:
     r = sel(first=True, t_delay=d, A0_pr=A0_prs[0], g=gammas[s_imp])
     rr.append(r)

### 2020-10-27 singleband/pl_temp-dep.py

@@ -30,10 +30,10 @@ plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
 folder = 'temp-dependence'
 files = glob.glob(f'{folder}/*.pickle')
 
-save_plots = True
+save_plots = False
 
-def savefig(fname, transparent=True):
-    if save_plots:
+def savefig(fname, transparent=True, plot=save_plots):
+    if plot:
         plt.savefig(fname, transparent=transparent)
 
 def nmax(x):
@@ -539,7 +539,7 @@ for g in gammas_all:
     if len(sel(g=g)) == 129:
         gammas.append(g)
 
-r0 = sel(t_delay=delays[-1])[0]
+r0 = sel(t_delay=delays[-1], T=temps[0])[0]
 d2_ref = r0['d_2'].real
 d_eq = r0['d_eq'][:,0,0]
 gap = np.max(d_eq)
@@ -562,7 +562,7 @@ cm = 'rainbow'
 
 #1A are 2.38459E-7 Js/Cm
 u_A = 2.38459E-7
-A,e = getE(r)
+A,e = getE(r0)
 Amax = np.max(np.abs(A))
 
 ############################
@@ -621,3 +621,50 @@ savefig('cond-temp-imag.pdf')
 
 plt.figure('cond-temp-legend')
 savefig('cond-temp-legend2.pdf')
+
+#%% temp dependence current
+
+plt.figure('j-temp', figsize=(3,2.8))
+plt.clf()
+plt.figure('j-temp-legend', figsize=(5,5))
+plt.clf()
+
+min_j = []
+delta = []
+
+# for temp in temps[[0,3,5,6,7]]:
+for temp in temps:
+    r = sel(first=True, T=temp, t_delay=0, A0_pr=0)
+
+    t = r['t']
+    j1 = r['jp_1'] + r['jd_1']
+    j3 = r['jp_3'] + r['jd_3']
+    j = Ascale*j1 + Ascale**3*j3
+    min_j.append(np.min(-j))
+    delta.append(r['d_eq'][0,0,0])
+
+    plt.figure('j-temp')
+    plt.plot(t*u_t,-j, label=f'$T={np.round(temp*u_temp,1)}$ K')
+    plt.xlabel('$t$ (ps)')
+    plt.xlim(-5,0)
+    # plt.ylim((0,5e4))
+    plt.ylabel('$j$ (a.u.)')
[…]

### 2020-10-27 multiband/BCS/BCS.py
a

@@ -1,0 +1,156 @@
+#%%
+import numpy as np
+from scipy import integrate
+import matplotlib.pyplot as plt
+import pickle
+
+
+hbar=1
+kb=1
+e=1
+
+u_temp = 116.032
+u_en = 10
+meV_to_THz = 0.2417990504024
+
+pre_d0  = np.array([0.3,0.7])
+
+
+
+wd  = 5
+s = np.array([1,-1])
+m = np.array([0.85, 1.38])
+ef = np.array([290, 70])
+v_legget = 0.15
+
+
+T=4/u_temp
+B = 1/(kb*T)
+
+nb = len(m)
+kf = np.sqrt(2*m*ef)/hbar
+vf = kf/m
+n = kf**3/(3*np.pi**2)
+N0 = m*kf/(2*np.pi**2)
+
+Ne = 1000
+ep = np.linspace(-wd, wd, Ne)
+
+#%%
+# if U is set, calculate d0 like this:
+def d0_integrand(x, d):
+    # This is an auxiliary function used in find_d0 to calculate an integral
+    return 0.5*1/np.sqrt(x**2+d**2)*np.tanh(B/2*np.sqrt(x**2+d**2))
+
+def find_d0(UN0):
+    # this function finds the initial gap(s) given U*N(0). Works in the single or multiband case
+    if nb == 2:
+        d = np.array([1, 1])
+        integral = np.zeros(2)
+        for j in [0, 1]:
+            integral[j] = integrate.quad(d0_integrand, -wd, wd, (d[j],))[0]
+        d_new = np.sum(UN0*d*integral, axis=1)
+
+        while (np.linalg.norm(d - d_new) > 1e-15):
+            d = d_new
+            integral = np.zeros(2)
+            for j in [0, 1]:
+                integral[j] = integrate.quad(d0_integrand, -wd, wd, (d[j],))[0]
+            d_new = np.sum(UN0*d*integral, axis=1)
+        return d_new
+    elif nb == 1:
+        UN0 = U[0]*N0
+        d = 1
+        d_new = UN0*d*integrate.quad(d0_integrand, -wd, wd, (d,))[0]
+        while (np.linalg.norm(d - d_new) > 1e-12):
+            d = d_new
[…]

### 2020-10-27 multiband/BCS/BCS.py
standard commit

@@ -21,7 +21,7 @@ wd  = 5
 s = np.array([1,-1])
 m = np.array([0.85, 1.38])
 ef = np.array([290, 70])
-v_legget = 0.15
+v_legget = 0.2
 
 
 T=4/u_temp

### 2020-10-31 paper/paper_v1.tex
a
standard commit

@@
-\documentclass[aps,prb,reprint,noeprint,superscriptaddress]{revtex4-2}
+\documentclass[aps,prb,reprint,noeprint,superscriptaddress]{revtex4-1}
 \pdfoutput=1
@@
 
-\author{Rafael Haenel}
+\author{Rafael Haenel2}
 \affiliation{Max Planck Institute for Solid State Research,
@@
 \label{sec:multiband}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\columnwidth]{figures/m-fig1.pdf}
+	\caption{Real part $\sigma'$ (A,C) and imaginary part $\sigma''$ (B,D)
+		of optical conductivities to first order in $A$ 
+	for various impurity scattering rates at $T=\SI{4}{\kelvin}$ (A,B) and
+various temperatures at $\gamma/2\Delta=10$. $\sigma'$ show a characteristic
+conductivity gap below $T_C$ and both $\sigma'$, $\sigma''$ diverge in the
+static limit.}
+
+$\Delta_{\infty}$ is given by the overlap of the pulse with the density of
+states of the quasiparticel continuum, 
+$$\Delta_{\infty} \propto
+\int_{}^{}d\omega N(\omega) A(\omega) \approx N(\varepsilon_F)
+\int_{\varepsilon_F}^{\infty}d\omega A(\omega)$$.
+\label{fig:singleband-gap}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{figure}[H]
+\begin{figure}[ht]
   \centering
-    \includegraphics[width=\columnwidth]{figures/two_band_cond.png}
-    \caption{\label{fig:two_band_cond}%
-    Equilibrium optical conductivity of a two-band superconductor with gaps in different impurity scattering limits (clean-clean case rescaled as response is much smaller?)}
-\end{figure}%
+  \includegraphics[width=\columnwidth]{figures/fig-cond-2d-fourcases}
+  \caption{Caption}
+\end{figure}
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=\textwidth]{figures/fig-three-pulses}
+  \caption{Caption}
+\end{figure*}
 
@@
 \end{itemize}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/gap_osci.png}
-    \caption{\label{fig:gap_osci}%
-    Higgs oscillations excited by a pump pulse with enough bandwidth to cover both gaps for the different impurity scattering limits shown in Fig.~\ref{fig:two_band_cond}}
-\end{figure}%
 
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/noneq_cond.png}
-    \caption{\label{fig:noneq_cond}%
-    Nonequilibrium optical conductivity of a pump-probe experiment for the different impurity scattering limits shown in Fig.~\ref{fig:two_band_cond}}
-\end{figure}%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/fig-driving}
+  \caption{Caption}
+\end{figure}
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/2_a}
+  \includegraphics[width=\columnwidth]{figures/2_b}
+\end{figure}
 
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/leggett_oscillations.png}
-    \caption{\label{fig:leggett_oscillations}%
-    Induced amplitude (Higgs) and out-of-phase (Leggett) oscillations of a two-band superconductor for different impurity scattering rates}
-\end{figure}%
-
 \begin{itemize}
@@
 Leggett mode has been potentially measured in between the two gaps. Discuss this
-and also refer to Schnyder Nature Comm. Figure out the parameter regime that
-inverted the gaps. Reproduce (or see what was wrong) with Murotani who also
-choose parameters such that the Leggett mode is inside the gap.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/leggett_coupling.png}
-    \caption{\label{fig:leggett_coupling}%
-    Frequency of Leggett mode as function of interband coupling strength in the dirty limit}
-\end{figure}%
+and also refer to Schnyder Nature Comm.
 
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/influence_pump_pulse_freq.png}
-    \caption{\label{fig:influence_pump_pulse_freq}%
-    Influence of pump pulse frequency}
-\end{figure}%
-
 \end{document}

### 2020-11-03 paper/paper_v1.tex
standard commit

@@
 
-\author{Rafael Haenel2}
+\author{Rafael Haenel}
 \affiliation{Max Planck Institute for Solid State Research,
@@
 \begin{itemize}
-	\item Ultrafast spectroscopy
-	\item Collective modes in superconductors: Higgs, Goldstone (shifted to plasma energy due to Anderson-Higgs)
-	\item In two-band superconductors: Additional out-of-phase Leggett mode, can couple to Higgs in nonequilibrium
-	\item Difficulties excitation Higgs mode, in clean-limit only weak coupling
-	\item In dirty superconductors: Coupling is enhanced. Activation of
-		$\mathbf{p} \cdot \mathbf{A}$ term by momentum-converation
-		braking impurity scattering.
-	\item Discussion of Matthis Bardeen theory.
 	\item This work: 1) Higgs oscillations in two-band sc. with bands in different limits, 2) Nonequilibrium optical conductivity, 3) Leggett mode in dirty-limit, 4) Prediction for MgB$_2$
+\end{itemize}
+
+When a global symmetry is spontaneously broken, collective excitations emerge.
+In the case of a superconductor, where the local order parameter $\Delta
+e^{i\varphi}$ acquires a
+finite value below a critical temperature $T_C$, two bosonic modes appear: the
+massive Higgs mode and a massless Goldstone mode. They may be seen as
+longitudinal and phase fluctuations of the complex order parameter in a Mexican
+hat free energy. In the presence of Coulomb interaction, the Goldstone mode is
+shifted to optical frequencies
+by means of the Anderson Higgs mechanism while the Higgs mode remains
+a stable gapped excitation in the Terahertz regime.
+
+In a two-band superconductor, two gapless Higgs modes and two phase modes exist.
+While the global phase fluctuations occur only at energies close to the plasma
+frequency, relative phase fluctuations, termed Leggett mode, 
+persist as a gapped excitation at low energies.
+
+Experimental observation of Higgs and Leggett collective modes is difficult.
+Since the
+Higgs field is a scalar quantity, no linear coupling to the vectorial
+electromagnetic field can exist. Thus, there are no direct experimental signatures in
+linear response and experiments need to be performed in the non-linear
+regime. Here, the challenge is twofold: intense light sources are required
+but experiments also have to be performed on energy scales mostly
+within the superconducting gap such that optical excitation of quasiparticles does not deplete 
+the condensate.
+
+Recent developments in ultrafast Terahertz spectroscopy have caused 
+a surge in interest in collective excitations in superconductors and
+experimental signatures of the Higgs mode have now been observed in various
+materials.
+
+Experiments performed so far consist of two approaches. First, samples are
+illuminated in a pump-probe setup where
+an excitation of the Higgs mode by a single-cycle THz pump appears as an oscillation of the
+probe signal as a function of pump-probe delay. In a second type of experiments, 
+the Higgs mode is resonantly driven
+by an intense multi-cycle pulse that yields a electrical field
+component of three times the pump frequency in the reflected or transmitted
+beam. Theoretically, time-resolved oscillation of the gap in angle-resolved
+photoemission (ARPES) spectra has also been studied as a third characterization
+scheme. Additionally, Higgs excitation has been proposed as
+its own spectroscopic method based on the insight that the gap symmetry of a
+superconductor can be classified from measurements of the condensate
+oscillations in different geometries.
+
+The fact that characteristics of the Higgs boson in superconductors are
+observable in experiments at all was not obvious from the beginning. Initially
+theoretical calculations in the clean limit predicted extremely weak
+experimental signatures unobservable with even today's experimental equipment.
+Only recently the role of impurities has been appreciated in achieving more
+realistic theoretical predictions. [list publications: Silaev, Murotani,
+Benfatto] In the clean limit, the Higgs mode only
+diamagnetically couples to the gauge field. Presence of impurities additionally enables
+a paramagnetic coupling which becomes the dominant contribution even for small disorder. 
+It was
+further shown that impurity scattering yields qualitatively different behavior
+in the polarization dependence of the pump pulses.
+
+An outstanding question MgB2. Murotani. Demler experiment.
+
+[How does this paper go beyond the work of Murotani and Shimano?]
+\begin{itemize}
+  \item time resolved optical conductivity
+  \item discussion of the second gap of MgB2 - why can't we see it in
+    optical experiment?
+  \item Third harmonic generation where pulse frequency is swept. (todo: also
+      sweep the temperature, show decomposition in terms of QP, Higgs, Legget
+    mode)
+  \item (Discussion of four cases)
+  \item Coupling of Higgs and Leggett mode. Do they actually couple?
+  \item Presentation using SI units to make everything easily comparable to
+    experiments.
+  \item Discussion of the paramagnetic activation in terms of diagrams?
 \end{itemize}
@@
 key aspects of the model as introduced by Murotani and Shimano []. We then
-discuss the case of a single-band superconductor in a pump-probe scenario and
-additionally with an assymetric supercurrent-inducing probe pulse in Sec.
-\ref{sec:singleband}. We then extend these results to the two-band case in Sec.
-\ref{sec:multiband} where we give explicit experimental predicitons for
-pump-probe characterization of collective modes in MgB$_2$.
+discuss the case of a single-band superconductor in a pump-probe scenario
+in Sec. \ref{sec:singleband} and make reference to available experimental data. 
+In Sec. \ref{sec:multiband} we study in detail the case of a two-band
+superconductor motivated by material parameters of MgB$_2$ with different 
+impurity concentrations of the conduction bands. We summarize all results in
+Sec. \ref{sec:conclusion}.
 
@@
 \label{sec:model}
+\subsection{Hamiltonian}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{itemize}
-	\item In this section show only the final formula, all derivation into the appendix A as the equations are similar to the Murotani paper.
-	\item Show Hamiltonian, gap equation, Mattis-Bardeen replacement, general approach for calculating time evolution...
-	\item I suggest putting the (final) equations for current, optical conductivity, $\delta\Delta(t)$ into the respective section, but in principle we could also put all equations in this section and show only the results in the following sections
-
-	\item Used parameters (take general parameters for section III and IV where no Leggett mode occurs, Leggett mode is discussed later separately and MgB$_2$ will be also discussed later.
-Show the used parameters in these section)
-	\item Implementation details? Are there any subtle points?
-\end{itemize}
+We consider a meanfield description of a multiband $s$-wave BCS superconductor,
 
 \begin{eqnarray}
-	H_{\text{BCS}} = \sum_{i\mathbf{k}\sigma}  
+  \mathcal{H}_{0} = \sum_{i\mathbf{k}\sigma}  
 	\varepsilon_{i\mathbf{k}}c_{i\mathbf{k}\sigma}^\dagger
@@
 where $\varepsilon_{i\mathbf{k}} = s_i \left(\mathbf{k}^2/2m_i -
-\varepsilon_{F_i}\right)$ and the superconducting order parameter is self-consistently determined by 
+\varepsilon_{F_i}\right)$ is the parabolic dispersion of the $i$-th band with
+Fermi-energy $\varepsilon_{F_i}$ and electron mass $m_i$. 
+$s_i=\pm$ determines electron/hole-like character of the respective band. The intraband 
+order parameter is self-consistently determined by the BCS equation
 $\Delta_i = \sum_{j\mathbf{k}}^{}U_{ij} \langle c_{j-\mathbf{k}\downarrow
-}c_{j\mathbf{k}\uparrow }\rangle$.
+}c_{j\mathbf{k}\uparrow }\rangle$. Interband pairing in BCS superconductors is
+considered weak (discussion, reference) and has been neglected in our model.
 
+Order parameters of different bands are mixed by off-diagonal terms of the
+coupling matrix $U_{ij}$. In the present work, we parametrize
+gap-mixing by a parameter $v$ and define
 \begin{eqnarray*}
-	H_{\text{p-p}} = -\sum_{i\mathbf{kk'}\sigma}^{}
+  U_{ij} = 
+  \begin{pmatrix}
+    U_{11} & v U_{11} \\
+    v U_{11} & U_{22}
+  \end{pmatrix}
+\end{eqnarray*}
+in the case of a two-band superconductor.
+For given $\Delta_i$ and $v$ we can thus find $U_{11}$ and
+$U_{22}$ such that the gap equation is satisfied.
+
+To model an experimental probe with a laser pulse, we introduce a time dependent gauge vector
+potential $\mathbf{A}(t)=\mathbf{e} A(t)$ by means of minimal coupling,
+\begin{eqnarray*}
+	\mathcal{H}_{1} = -\sum_{i\mathbf{kk'}\sigma}^{}
 	\mathbf{J}_{i\mathbf{kk'}} \cdot \mathbf{A} \,
@@
 	\sum_{i\mathbf{k}\sigma}^{} \frac{s_i e^2}{2m_i} \mathbf{A}^2 \,
-	c_{i\mathbf{k}\sigma}^\dagger c_{i\mathbf{k}\sigma}
+	c_{i\mathbf{k}\sigma}^\dagger c_{i\mathbf{k}\sigma}\,.
 \end{eqnarray*}
+$J_{i\mathbf{kk'}}=\bra{i\mathbf{k}}\frac{e\mathbf{p}_i}{m_i}
+\ket{i\mathbf{k'}}$ are intraband transition matrix elements of the current
+operator. (Discussion why we neglect interband transitions). The two terms in
+$\mathcal{H}_1$ corresponds to the paramagnetic and diamagnetc coupling to the laser field,
+respectively.
+The full Hamiltonian is given by $\mathcal{H} = \mathcal{H}_{0} + \mathcal{H}_{1}$.
 
+\subsection{Impurity scattering}
+In a clean system momentum conservation yields $\mathbf{J}_{i\mathbf{kk'}} \sim
+\delta_{\mathbf{kk'}}$, or $\mathbf{J}_{i\mathbf{kk'}} \sim
+\delta_{\mathbf{k,k'}\pm\mathbf{q}}$ if a photon wavevector $\mathbf{q}$ is
+considered. In disordered systems translational invariance is broken, so that
+transitions between states of different momentum are allowed. Here, we adopt the
+approach of Murotani and Shimano [] and model the effects of impurities by
+means of the Mattis-Bardeen (MB) substitution []. It relies on approximating the
+transition matrix elements $J_{i\mathbf{kk'}}$ as a
+Lorentzian in momentum transfer space, explicitly written as
 \begin{eqnarray*}
@@
 	&\approx& \frac{(e v_{F_i})^2}{3 \pi N_i(0)} 
-	\frac{\gamma_i}{(\varepsilon-\varepsilon')^2 + \gamma_i^2}
+	\frac{\gamma_i}{\left(\varepsilon_{i|\mathbf{k}|}-\varepsilon_{i|\mathbf{k}'|}\right)^2
+	+ \gamma_i^2} \,,
+\end{eqnarray*}
+with Fermi velocity $v_{F_i}$ density of states of the Fermi level $N_i(0)$ and
+impurity scattering rate $\gamma_i$. Note that we are considering an effectively
+one-dimensional quantity
+where all angular degrees of freedom have been averaged out.
+Physically, this means that impurity scattering occurs with equal probability
+between all states within a shell around the Fermi sphere.
+A derivation of this matrix element
+following [Murotani] is reviewed in Appendix X.
+
+An optical transition can be resonantly driven only if (1) an energy matching
+condition and (2) a momentum 
+matching condition is satisfied. Assuming a transition energy of $\Delta$,
+condition
+(1) can be satisfied by tuning the optical pulse frequency to $\omega=\Delta$.
+Let us for simplicity consider a one-dimensional system. If
+$\Delta$ is sufficiently small, the parabolic dispersion can be linearized at
+the Fermi level, $\varepsilon_k = v_F k$. Then, a momentum of $\Delta/v_F$ 
+is necessary to satisfy condition (2). In a clean system it then follows that
+photoexcitation within a single band is not possible
+if bandfolding effects are also neglected.
+In a weakly disordered system, momentum is no longer a good quantum
+number. Here, momentum broadening $\delta k$ can be viewed as providing the necessary
+momentum and the transition becomes resonant for $v_F \delta k=\Delta$. For
+strong disorder the concept of momentum is lost and any two states
+can be connected by satisfying condition (1) only.
+
+In the MB approximation, $\mathbf{k}$ is still treated as an exact quantum
+number of the unperturbed system but presence of impurities 
+broadens momentum conservation of the transition matrix element
+$\mathbf{J}_{i\mathbf{kk'}}$ into a Lorentzian momentum transfer distribution of
+width $\gamma_i$ centered at zero momentum transfer. 
+It is straightforward to check that for an excitation of energy $\Delta$ 
+the matrix element gives the largest contribution 
+for an impurity scattering rate of $\gamma_i=\Delta$.
+
+One may picture the Higgs excitation as a two-photon excitation process, where
+the first photon populates a virtual intermediate state at energy $\Delta$ above
+the groundstate and the second photon contributes the remaining $\Delta$ to
+establish resonance with the Higgs mode at $2\Delta$.
+Based on
+these arguments, we can expect the largest enhancement of the Higgs resonance at 
+$\gamma_i = \Delta_i$.
+
+[Discussion of relevant scales $\Delta, \gamma, \omega_D, \varepsilon_F$.
+Specifically, what happens when $\gamma>\omega_D$??]
+
+\subsection{Equations of motion}
+
+We solve for the time dynamics of above Hamiltonian using a density matrix
+approach. To this end, we define the density matrix $\rho =
+\ket{\psi_0}\bra{\psi_0}$, or, in the basis of single-particle/hole excitations,
+$\mathcal{B}=\left\{ c_{i\mathbf{k}\uparrow }\ket{0},\, c_{i-\mathbf{k}\downarrow
+}\ket{0} \right\}$
+\begin{eqnarray*}
+  \rho = 
+  \begin{pmatrix}
+    \rho_{i\mathbf{kk'}}^{11} &
+    \rho_{i\mathbf{kk'}}^{12} \\
+    \rho_{i\mathbf{kk'}}^{21} &
+    \rho_{i\mathbf{kk'}}^{22}
+  \end{pmatrix}
+  =
+  \begin{pmatrix}
+    \langle c_{i\mathbf{k}\uparrow }^\dagger c_{i\mathbf{k}'\uparrow }\rangle
+    &
+    \langle c_{i\mathbf{k}\uparrow }^\dagger c_{i-\mathbf{k}'\downarrow
+    }^\dagger \rangle
+    \\
+    \langle 
+    c_{i-\mathbf{k}\downarrow }c_{i\mathbf{k'}\uparrow }
+    \rangle
+    &
+    \langle 
+    c_{i-\mathbf{k}\downarrow }c_{i\mathbf{-k'}\downarrow }^\dagger 
+    \rangle
+  \end{pmatrix}
 \end{eqnarray*}
 
-Discussion of $A, A^2$.
+The time dependence of $\rho$ is given by the Heisenberg equation of motion,
+\begin{eqnarray*}
+  i\partial_t \rho = \left[ \rho, H \right]
+\end{eqnarray*}
+where $H$ is the operator $\mathcal{H}$ in the basis $\mathcal{B}$.
 
-The full Hamiltonian is given by $H = H_{BCS} + H_{p-p}$.
+We are interested in computing the dynamics of the current
+$ \mathbf{j} = -\big\langle \frac{\delta \mathcal{H}}{\delta
+\mathbf{A}}\big\rangle =
+\mathbf{j}_P + \mathbf{j}_D$, consisting of a paramagnetic and diamagnetic
+contribution,
+\begin{eqnarray*}
+  \mathbf{j}_P 
+	&=&
+  	\sum_{i\mathbf{kk'}}^{}
+	\mathbf{J}_{i\mathbf{kk'}}\,
+	\left( 
+	  \rho_{i\mathbf{kk'}}^{11}
+	  -\rho_{i\mathbf{kk'}}^{22}
+	  +1
+	\right)
+	\\
+  \mathbf{j}_D &=& -\sum_{i\mathbf{k}\sigma}^{} \frac{s_i e^2}{2m_i} 
+  \mathbf{A} \,
+	\left( 
+	  \rho_{i\mathbf{kk}}^{11}
+	  -\rho_{i\mathbf{kk}}^{22}
+	  +1
+	\right)
+\end{eqnarray*}
+and we compute the dynamics of the superconducting order parameter
+\begin{eqnarray*}
+  \Delta_i = \sum_{j\mathbf{k}}^{}U_{ij} 
+  \rho_{j\mathbf{kk}}^{21} \,.
+\end{eqnarray*}
+To apply the MB substitution we further expand above equation of motions in
+orders of $A(t)$. To account for effects of a THG response, we consider terms up to
+third order. As detailed in Appendix X, the current only has odd order
+components $\mathbf{j} = \mathbf{j}\big|_0 +\mathbf{j}\big|_3 + \dots$ and the
+gap only contains even contributions of $A$, $\Delta = \Delta\big|_0 +
+\Delta\big|_2 +\dots$.
 
-Shortcoming of the model. Momentum-angle averaging removes information about
-polarization, momentum of photon. The gap oscillates with its equilibrium value
-and not $\Delta_{\infty}$. Also, the results are an expansion in $A$ up to third
-order. Specifically, the gap in only included up to second order (the only
-nonzero term) which makes it hard to say when this approximation becomes
-invalid. The dependence of the gap on fluence is linear up to this order.
+Finally, we exploit the rotational invariance of our model and perform the
+integral over angular degrees of freedom explicitly. Thus, by replacing all momentum summations
+by an integral 
+$\sum_{\mathbf{k}}^{} \rightarrow
+N_i(0)\int_{}^{}d\varepsilon_{i\mathbf{k}}\int_{}^{}
+\frac{d\Omega_{\mathbf{k}}}{4\pi}$, we effectively reduce the model to a
+one-dimensional system. Note that rotational invariance of our continuum model
+neglects polarization dependence of observable quantities.
+
+We are left to compute the equations of motion of the
+angle-averaged quantities
+\begin{eqnarray*}
+  R^{1/3,n}_{\varepsilon_{|\mathbf{k}|}} &=& 
+  \int_{}^{}\frac{d\Omega_{\mathbf{k}}}{4\pi}
+  \int_{}^{}\frac{d\Omega_{\mathbf{k'}}}{4\pi}
+  \mathbf{J}_{i\mathbf{kk'}} \, \rho_{i\mathbf{kk'}}^{nn}\big|_{1/3}
+  \\
+  r^{nm}_{\varepsilon_{|\mathbf{k}|}} &=& 
+  \int_{}^{}\frac{d\Omega_{\mathbf{k}}}{4\pi}
+  \rho_{i\mathbf{kk}}^{nm}\big|_{2} \,.
+\end{eqnarray*}
+We solve them numerically using a [Runge-Kutta] solver on a discretized energy grid
+$\varepsilon_{|\mathbf{k}_i|}$ of up to $10^3$ points in the interval $\left[
+  -\omega_D, \omega_D
+\right]$ (why do we use $\omega_D$???).
+A detailed derivation and an explicit presentation of the full equations of
+motion is given in Appendix X.
 
 \section{Single-band superconductivity}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\columnwidth]{figures/fig1.pdf}
+	\caption{(a) Pulse field $E(t)$ realizing a quench. (b) Spectral
+	composition $|A(\omega)|$. The gray shaded area illustrates the
+quasi-particle continuum. (c) Spectral compositon $A^2(\omega)$ of the second
+order component $A^2(t)$ responsible for excitation of collective modes. The
+peak around zero frequency corresponds to a DFG process while the peak at finite
+$\SI{1.2}{\tera\hertz}$ is a SFC process. (c) Evolution of the magnitude of the
+order parameter $\left|2\Delta(t)\right|$ for impuritiy strength varying from
+$\gamma/2\Delta=0.5$ to $20$ and Fourier spectrum of the gap oscillations (d).
+(e) Relaxation value $\Delta_{\infty}$ and amplitude of oscillation show a very
+similar dependence as a function of disorder strength which has maximum effect
+at around $\gamma \approx \Delta$.}
+\label{fig:singleband-gap}
+\end{figure}
 \label{sec:singleband}
@@
 measurements and ab-initio calculations on NbN [DFT-reference].
-The Debye energy for NbN is order order of $\omega_D = \SI{5}{\milli\electronvolt}$, but
+The Debye energy for NbN is order order of 
+$\omega_D = \SI{5}{\milli\electronvolt}$, but
 for better numerical resolvability we choose $\omega_D =
@@
 
-A characteristic property of a pump pulse is its pulse length $\tau$ in units of the natural
-timescale of the superconductor, $\hbar/\Delta$. For $\tau \ll \hbar / \Delta$
-the superconductor is \textit{quenched}, while it is adiabatically driven in the
-opposite limit of $\tau \gg  \hbar / \Delta$. Here, we investigate a quench
-scenario with $\hbar\tau/\Delta=x$ by fitting the pulse form $A(t) = A_0 \exp\left( -(t-t')^2/2\tau^2
-\right)\cos \Omega t$ to the reported data of [Matsunaga]. The resulting
-electrical field waveform is shown in panel A of Fig. \ref{fig:singleband-gap}.
+We choose the electromagnetic pulse form $A(t) = A_0 \exp\left( -(t-t')^2/2\tau^2
+\right)\cos \Omega t$ and choose coefficients to match the reported data 
+of [Matsunaga]. The resulting
+electrical field waveform is shown in Fig. \ref{fig:singleband-gap}(a).
 
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=\columnwidth]{figures/fig1.pdf}
-	\caption{(A) Pulse field $E(t)$ realizing a qunech. (B) Spectral
-	composition $|A(\omega)|$. The gray shaded area illustrates the
-quasi-particle continuum. (C) Spectral compositon $A^2(\omega)$ of the second
-order component $A^2(t)$ responsible for excitation of collective modes. The
-peak around zero frequency corresponds to a DFG process while the peak at finite
-$\SI{1.2}{\tera\hertz}$ is a SFC process. (C) Evolution of the magnitude of the
-order parameter $\left|2\Delta(t)\right|$ for impuritiy strength varying from
-$\gamma/2\Delta=0.5$ to $20$ and Fourier spectrum of the gap oscillations (D).
-(E) Relaxation value $\Delta_{\infty}$ and amplitude of oscillation show a very
-similar dependence as a function of disorder strength which has maximum effect
-at around $\gamma \approx \Delta$.}
+A characteristic property of a pump pulse is its pulse 
+length $\tau$ compared to the natural
+timescale of the superconductor, $1/\Delta$. For $\tau \ll \hbar / \Delta$
+the superconductor is \textit{quenched}, while it is \textit{adiabatically
+driven} in the
+opposite limit of $\tau \gg  1 / \Delta$. 
+The different behavior in the two limits can be intuitively understood 
+from the simple relation
+\begin{eqnarray*}
+  \delta \Delta(\omega) \sim K(\omega) A^2(\omega)
+\end{eqnarray*}
+where $K(\omega)$ is the optical nonlinear kernel []. Presence of a collective mode
+translates into a peak of the optical Kernel at the characteristic mode energy
+$\omega=2\Delta$, illustrated in Fig. \ref{fig:singleband-gap}(c) by a vertical
+line.
+$A^2(\omega)$  
+is the Fourier transform of the squared vector
+potential $A(t)^2$ and hence given by a self-convolution of $A(\omega)$. $A^2(\omega)$, shown in Fig. 
+\ref{fig:singleband-gap}(c), has a double-peaked structure. The first peak,
+centered at $\omega=0$, corresponds to a difference frequency process (DFG),
+while the second peak at $\omega=2\Omega$ corresponds to a sum frequency process
+(SFG). For $\Delta\tau\ll 1$, the frequency structure of $A^2(\omega)$ is very
+broad. The response of $\delta\Delta(\omega)$ is then dominated by the sharp
+resonance peak of $K(\omega)$ giving rise to pronounced $2\Delta$-oscillations
+of the superconducting gap in the time domain. 
+Since the DFG peak is 
+guaranteed to overlap with the Higgs resonance,
+these oscillations will always be present,
+independent of the frequency of the optical pulse. The SFG process only contributes
+if the pulse frequency lies in the vicinity of $\Omega \approx \Delta$.
 
-$\Delta_{\infty}$ is given by the overlap of the pulse with the density of
-states of the quasiparticel continuum, 
-$$\Delta_{\infty} \propto
-\int_{}^{}d\omega N(\omega) A(\omega) \approx N(\varepsilon_F)
-\int_{\varepsilon_F}^{\infty}d\omega A(\omega)$$.
-\label{fig:singleband-gap}
-\end{figure}
+In the transient limit, $\Delta \tau\gg 1$, the frequency structure of
+$\delta\Delta(\omega)$ is dominated by the sharp SFG peak of the pulse. The gap
+will show a forced oscillation with frequency $2\Omega$ which, however, is
+resonantly enhanced when $2\Omega\approx2\Delta$.
 
-\begin{figure}[ht]
+Following Matsunaga, we choose a pulse with $\Delta \tau = 0.x$, closest to the
+quench scenario. The superconducting order parameter indeed shows characteristic
+oscillations with frequency $2\Delta=\SI{6.x}{\tera\hertz}$ as shown in Figs.
+\ref{fig:singleband-gap}(d-e). The gap can be seen to respond to the THz pulse
+by a marked drop followed by damped oscillations around a new value
+$\Delta_{\infty}$. [$\left|\Delta^{eq}-\Delta_{\infty}\right| \propto
+  \int_{}^{}d\omega \sigma'(\omega) A(\omega).$, 
+Discussion why it does not oscillate with $\Delta_{\infty}$]
+
+Both the oscillation amplitude and $\Delta_{\infty}$ show a
+strong dependence on the impurity scattering rate. For $\gamma\rightarrow 0$
+they both vanish while they peak at $\gamma\approx
+\Delta^{eq}$, see Fig. \ref{fig:singleband-gap}(f). These results underline the
+importance of impurity scattering for the excitation efficiency of collective
+Higgs modes already uncovered by Refs. [].
+In agreement with the argument from Sec. X this dependence is well approximated by
+the functional form $\gamma/(\Delta_{eq}^2+\gamma^2)$.
+
+Next we compute the optical conductivity
+\begin{eqnarray*}
+\sigma(\omega)=\frac{j(\omega)}{i\omega A(\omega)}
+\end{eqnarray*}
+and plot its real and
+imaginary part in Figs. \ref{fig:cond-lin}(a-b) for various impurity
+concentrations.
+
+\begin{figure}[t]
 	\centering
@@
 static limit.}
+\label{fig:cond-lin}
 \end{figure}
 
-\begin{figure}[ht]
+\begin{figure}[t]
 	\centering
@@
 static limit.}
-
-$\Delta_{\infty}$ is given by the overlap of the pulse with the density of
-states of the quasiparticel continuum, 
-$$\Delta_{\infty} \propto
-\int_{}^{}d\omega N(\omega) A(\omega) \approx N(\varepsilon_F)
-\int_{\varepsilon_F}^{\infty}d\omega A(\omega)$$.
 \label{fig:singleband-gap}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Mattis-Bardeen substitution}
 
+One starts with the following assumption:
+
+\begin{eqnarray*}
+	\rho_k(R) = \langle \phi_\mathbf{k}^*(\mathbf{r})
+	\phi_\mathbf{k}(\mathbf{r}') \rangle_{Av}
+	=
+	\frac{\sin k R}{k R} e^{-R/2l}
+\end{eqnarray*}
+where $R=\left|\mathbf{r}-\mathbf{r}'\right|$ and $\langle \, \rangle_{Av} =
+\int_{}^{}\frac{d\Omega_\mathbf{k}}{4\pi}(\,)$ denotes
+averaging over the angle of $\mathbf{k}$. $l$ is the mean-free path.
+\begin{eqnarray*}
+	&&\langle 
+	\left|J^i_{\mathbf{k}\mathbf{k}'}\right|^2 
+	\rangle_{Av}
+	\\
+	&=&
+	\frac{e^2}{m^2} 
+	\left|
+	\int_{}^{} d^3\mathbf{r} \phi_\mathbf{k}^*(\mathbf{r})
+	\frac{\partial_i}{i} \phi_{\mathbf{k}'}(\mathbf{r})
+	\right|^2
+	\\
+	&=& \frac{e^2}{m^2} 
+	\int_{}^{}\int_{}^{}\frac{d\Omega_\mathbf{k}}{4\pi}
+	\frac{d\Omega_{\mathbf{k}'}}{4\pi}
+		\int_{}^{} d^3\mathbf{r} \phi_\mathbf{k}^*(\mathbf{r})
+		\frac{\partial_i}{i} \phi_{\mathbf{k}'}(\mathbf{r})
+		\int_{}^{} d^3\mathbf{r}' \phi_\mathbf{k}(\mathbf{r}')
+		 \frac{\partial_i'}{i} \phi_{\mathbf{k}'}^*(\mathbf{r'})
+	\\
+	&=& \frac{e^2}{m^2} 
+	\int_{}^{}\int_{}^{}
+	\frac{d\Omega_\mathbf{k}}{4\pi}
+	\frac{d\Omega_{\mathbf{k}'}}{4\pi}
+		\int_{}^{} d^3\mathbf{r} 
+		\phi_\mathbf{k}^*(\mathbf{r})
+		\frac{\partial_i}{i} \phi_{\mathbf{k}'}(\mathbf{r})
+		\int_{}^{} d^3\mathbf{r}' 
+		\left(-\frac{\partial_i'}{i}\phi_\mathbf{k}(\mathbf{r}')\right)
+		\phi_{\mathbf{k}'}^*(\mathbf{r'})
+	\\
+	&=& \frac{e^2}{m^2} 
+		\int_{}^{} d^3\mathbf{r} 
+		d^3\mathbf{r}' 
+	\int_{}^{}
+	\frac{d\Omega_\mathbf{k}}{4\pi}
+		\phi_\mathbf{k}^*(\mathbf{r})
+		\partial_i'\phi_\mathbf{k}(\mathbf{r}')
+	\int_{}^{}
+	\frac{d\Omega_{\mathbf{k}'}}{4\pi}
+		\phi_{\mathbf{k}'}^*(\mathbf{r'})
+		\partial_i \phi_{\mathbf{k}'}(\mathbf{r})
+	\\
+	&=& \frac{e^2}{m^2} 
+		\int_{}^{} d^3\mathbf{r} 
+		d^3\mathbf{r}' 
+		\partial_i'
+		\langle 
+		\phi_\mathbf{k}^*(\mathbf{r})
+		\phi_\mathbf{k}(\mathbf{r}')
+		\rangle_{Av}
+		\partial_i 
+		\langle 
+		\phi_{\mathbf{k}'}^*(\mathbf{r'})
+		\phi_{\mathbf{k}'}(\mathbf{r})
+		\rangle_{Av}
+	\\
+	&=& \frac{e^2}{m^2} V
+		\int_{}^{} d^3\mathbf{R} 
+		\frac{\partial \rho_k(R)}{\partial R_i}
+		\frac{\partial \rho_{k'}(R)}{\partial R_i}
+	\\
+	&=& \frac{e^2}{m^2} V
+		\int_{}^{} d^3\mathbf{R} 
+		\frac{R_i^2}{R^2}
+		\frac{\partial \rho_k(R)}{\partial R}
+		\frac{\partial \rho_{k'}(R)}{\partial R}
+	\\
+	&\approx& \frac{e^2}{m^2} V
+		\int_{}^{} d^3\mathbf{R} 
+		\frac{R_i^2}{R^2}
+		\frac{e^{-R/l}}{2R^2} \cos (k-k')R
+	\\
+	&=& \frac{e^2}{m^2} V
+		\int_{0}^{\infty}dR
+		\int_{0}^{2\pi}d\varphi
+		\int_{0}^{\pi}d\theta
+		R^2 \sin \theta	
+		\frac{R_i^2}{R^2}
+		\frac{e^{-R/l}}{2R^2} \cos (k-k')R
+\end{eqnarray*}
+Now we make use of the fact that
+\begin{eqnarray*}
+		\int_{0}^{2\pi}d\varphi
+		\int_{0}^{\pi}d\theta
+		\sin \theta	
+		\frac{R_i^2}{R^2}
+		= \frac{4\pi}{3}
+\end{eqnarray*}
+We see that the expression is now independent of the component index $i$ of the
+real-space vector $\mathbf{J}_{\mathbf{k}\mathbf{k}'}$. This means that
+averaging over angles in momentum space results in loss of polarization
+dependence in real-space.
+
+Performing the remaining integral gives 
+\begin{eqnarray*}
+	\langle 
+	\left|J^i_{\mathbf{k}\mathbf{k}'}\right|^2 
+	\rangle_{Av}
+	&=& 
+	\frac{2\pi}{3}\frac{e^2}{m^2} V
+		\int_{0}^{\infty}dR
+		e^{-R/l} \cos (k-k')R
+	\\
+	&=& 
+	\frac{2\pi}{3}\frac{e^2}{m^2} V
+	\frac{1/l}{(1/l)^2+ (k-k')^2}
+\end{eqnarray*}
+Close to the Fermi surface we have $\varepsilon_\mathbf{k}=v_F(k-k_F)$ which
+yields
+\begin{eqnarray*}
+	\langle 
+	\left|J^i_{\mathbf{k}\mathbf{k}'}\right|^2 
+	\rangle_{Av}
+	&=& 
+	\frac{2\pi}{3}\frac{e^2}{m^2} V
+	\frac{1/l}{(1/l)^2+ (\varepsilon_k-\varepsilon_{k'})^2/v_F^2}
+\end{eqnarray*}
+
+\section{Model}
+\begin{eqnarray}
+  \mathcal{H}_0 = \sum_{i\mathbf{k}\sigma}  
+	\varepsilon_{i\mathbf{k}}c_{i\mathbf{k}\sigma}^\dagger
+	c_{i\mathbf{k}\sigma} + \sum_{i\mathbf{k}}^{}
+	\left( \Delta_i c_{i\mathbf{-k}\uparrow }^\dagger
+	c_{i\mathbf{k}\downarrow }^\dagger  \right) \,,
+\end{eqnarray}
+
+where $\varepsilon_{i\mathbf{k}} = s_i \left(\mathbf{k}^2/2m_i -
+\varepsilon_{F_i}\right)$ and the superconducting order parameter is self-consistently determined by 
+$\Delta_i = \sum_{j\mathbf{k}}^{}U_{ij} \langle c_{j-\mathbf{k}\downarrow
+}c_{j\mathbf{k}\uparrow }\rangle$.
+
+\begin{eqnarray*}
+	\mathcal{H}_1 = -\sum_{i\mathbf{kk'}\sigma}^{}
+	\mathbf{J}_{i\mathbf{kk'}} \cdot \mathbf{A} \,
+	c_{i\mathbf{k}\sigma}^\dagger  c_{i\mathbf{k}'\sigma} +
+	\sum_{i\mathbf{k}\sigma}^{} \frac{s_i e^2}{2m_i} \mathbf{A}^2 \,
+	c_{i\mathbf{k}\sigma}^\dagger c_{i\mathbf{k}\sigma}
+\end{eqnarray*}
+
+\begin{eqnarray*}
+	\langle \left|\mathbf{e} \cdot
+	\mathbf{J}_{i\mathbf{kk'}}\right|^2\rangle_{\text{Av}}
+	&=& \int \frac{d\Omega_\mathbf{k}}{4\pi} \frac{d\Omega_\mathbf{k}'}{4\pi}
+	\left|\mathbf{e} \cdot \mathbf{J}_{i\mathbf{kk'}}\right|^2
+	\\
+	&\approx& \frac{(e v_{F_i})^2}{3 \pi N_i(0)} 
+	\frac{\gamma_i}{(\varepsilon-\varepsilon')^2 + \gamma_i^2}
+\end{eqnarray*}
+
+Discussion of $A, A^2$.
+
+The full Hamiltonian is given by $\mathcal{H} = \mathcal{H}_0 +
+\mathcal{H}_1$.
+
+\begin{eqnarray*}
+  \mathbf{j} = - \bigg\langle \frac{\delta\mathcal{H}}{\delta
+  \mathbf{A}}\bigg\rangle = \mathbf{j}_P + \mathbf{j}_D
+\end{eqnarray*}
+\begin{eqnarray*}
+  \mathbf{j}_P = \sum_{i\mathbf{kk'}\sigma}^{}
+	\mathbf{J}_{i\mathbf{kk'}} \cdot \mathbf{A} \,
+	\langle 
+	c_{i\mathbf{k}\sigma}^\dagger  c_{i\mathbf{k}'\sigma}
+	\rangle
+\end{eqnarray*}
+\begin{eqnarray*}
+  \mathbf{j}_D = -\sum_{i\mathbf{k}\sigma}^{} \frac{s_i e^2}{2m_i} 
+  \mathbf{A} \,
+  \langle 
+  c_{i\mathbf{k}\sigma}^\dagger c_{i\mathbf{k}\sigma}
+  \rangle
+\end{eqnarray*}
+
+Next we construct the density matrix
+\begin{eqnarray*}
+  \rho = \ket{\psi_0}\bra{\psi_0} = 
+  \begin{pmatrix}
+    \rho_{i\mathbf{kk'}}^{11} &
+    \rho_{i\mathbf{kk'}}^{12} \\
+    \rho_{i\mathbf{kk'}}^{21} &
+    \rho_{i\mathbf{kk'}}^{22}
+  \end{pmatrix}
+  =
+  \begin{pmatrix}
+    \langle c_{i\mathbf{k}\uparrow }^\dagger c_{i\mathbf{k}'\uparrow }\rangle
+    &
+    \langle c_{i\mathbf{k}\uparrow }^\dagger c_{i-\mathbf{k}'\downarrow
+    }^\dagger \rangle
+    \\
+    \langle 
+    c_{i-\mathbf{k}\downarrow }c_{i\mathbf{k'}\uparrow }
+    \rangle
+    &
+    \langle 
+    c_{i-\mathbf{k}\downarrow }c_{i\mathbf{-k'}\downarrow }^\dagger 
+    \rangle
+  \end{pmatrix}
+\end{eqnarray*}
+Writing the density matrix in vector form,
+\begin{eqnarray*}
+  \rho = 
+  \begin{pmatrix}
+    \rho_{i\mathbf{kk'}}^{11} \\
+    \rho_{i\mathbf{kk'}}^{12} \\
+    \rho_{i\mathbf{kk'}}^{21} \\
+    \rho_{i\mathbf{kk'}}^{22}
+  \end{pmatrix} \,,
+\end{eqnarray*}
+the Heisenberg equation of motion can be calculated as follows
+\begin{eqnarray*}
+  i\frac{d \rho_{i\mathbf{k}\mathbf{k}'}}{dt}
+  =
+  \sum_{\mathbf{q}}^{}
+  \left[ 
+    H_{i\mathbf{k}' \mathbf{q}}^{(1)} \rho_{i\mathbf{kq}} -
+    H_{i\mathbf{qk}}^{(2)}
+    \rho_{i\mathbf{qk'}}
+  \right]
+\end{eqnarray*}
+where we have defined the following two matrices:
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(1)}
+  =
+  \begin{pmatrix}
+    h_{i\mathbf{kk'}}^{11} & h_{i\mathbf{kk'}}^{12} & & \\
+    h_{i\mathbf{kk'}}^{21} & h_{i\mathbf{kk'}}^{22} & & \\
+    && h_{i\mathbf{kk'}}^{11} & h_{i\mathbf{kk'}}^{12} \\
+    && h_{i\mathbf{kk'}}^{21} & h_{i\mathbf{kk'}}^{22} & 
+  \end{pmatrix}
+\end{eqnarray*}
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(2)}
+  =
+  \begin{pmatrix}
+    h_{i\mathbf{kk'}}^{11} && h_{i\mathbf{kk'}}^{21} & \\
+    & h_{i\mathbf{kk'}}^{11} && h_{i\mathbf{kk'}}^{21} \\
+    h_{i\mathbf{kk'}}^{12} && h_{i\mathbf{kk'}}^{22} & \\
+    & h_{i\mathbf{kk'}}^{12} && h_{i\mathbf{kk'}}^{22}
+  \end{pmatrix}
+\end{eqnarray*}
+\begin{comment}
+Let us multiply this out:
+\begin{eqnarray*}
+  i \frac{d}{dt}
+  \begin{pmatrix}
+    \rho_{i\mathbf{kk'}}^{11} &
+    \rho_{i\mathbf{kk'}}^{12} \\
+    \rho_{i\mathbf{kk'}}^{21} &
+    \rho_{i\mathbf{kk'}}^{22}
+  \end{pmatrix}
+  =
+  \sum_{\mathbf{q}}^{}
+  \begin{pmatrix}
+    h_{i\mathbf{k'q}}^{11} \rho_{i\mathbf{kq}}^{11}
+    + h_{i\mathbf{k'q}}^{12} \rho_{i\mathbf{kq}}^{12}
+    -h_{i\mathbf{qk}}^{11} \rho_{i\mathbf{qk'}}^{11}
+    -h_{i\mathbf{qk}}^{21} \rho_{i\mathbf{qk'}}^{21}
+    &
+    h_{i\mathbf{k'q}}^{21} \rho_{i\mathbf{kq}}^{11}
+    + h_{i\mathbf{k'q}}^{22} \rho_{i\mathbf{kq}}^{12}
+    -h_{i\mathbf{qk}}^{11} \rho_{i\mathbf{qk'}}^{12}
+    -h_{i\mathbf{qk}}^{21} \rho_{i\mathbf{qk'}}^{22}
+    \\
+    h_{i\mathbf{k'q}}^{11} \rho_{i\mathbf{kq}}^{21}
+    + h_{i\mathbf{k'q}}^{12} \rho_{i\mathbf{kq}}^{22}
+    -h_{i\mathbf{qk}}^{12} \rho_{i\mathbf{qk'}}^{11}
+    -h_{i\mathbf{qk}}^{22} \rho_{i\mathbf{qk'}}^{21}
+    &
+    h_{i\mathbf{k'q}}^{21} \rho_{i\mathbf{kq}}^{21}
+    + h_{i\mathbf{k'q}}^{22} \rho_{i\mathbf{kq}}^{22}
+    -h_{i\mathbf{qk}}^{12} \rho_{i\mathbf{qk'}}^{12}
+    -h_{i\mathbf{qk}}^{22} \rho_{i\mathbf{qk'}}^{22}
+  \end{pmatrix}
+\end{eqnarray*}
+\end{comment}
+
+Now we expand the equation of motion in orders of $\mathbf{A}$. The zeroth-order
+components are:
+\begin{eqnarray*}
+  \rho_{i\mathbf{kk'}}\big|_0 = \delta_{kk'} 
+  \begin{pmatrix}
+    \frac{1}{2}\left(1-\frac{\varepsilon_{i\mathbf{k}}}{E_{i\mathbf{k}}}\right)
+    +\frac{\varepsilon_{i\mathbf{k}}}{ E_{i\mathbf{k}}}f_{i\mathbf{k}}
+    \\
+    -\frac{\Delta^{eq}_i}{2}(1-2f_{i\mathbf{k}})
+    \\
+    -\frac{\Delta^{eq}_i}{2}(1-2f_{i\mathbf{k}})
+    \\
+    \frac{1}{2}\left(1+\frac{\varepsilon_{i\mathbf{k}}}{E_{i\mathbf{k}}}\right)
+    -\frac{\varepsilon_{i\mathbf{k}}}{ E_{i\mathbf{k}}}f_{i\mathbf{k}}
+  \end{pmatrix}
+\end{eqnarray*}
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(1)}\big|_0
+  =
+  \delta_{\mathbf{kk'}}
+  \begin{pmatrix}
+    \varepsilon_{i\mathbf{k}} & \Delta^{eq}_i & & \\
+    \Delta^{eq}_i & -\varepsilon_{i\mathbf{k}} & & \\
+    && \varepsilon_{i\mathbf{k}} & \Delta^{eq}_i \\
+    && \Delta^{eq}_i & -\varepsilon_{i\mathbf{k}} & 
+  \end{pmatrix}
+\end{eqnarray*}
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(2)}\big|_0
+  =
+  \delta_{\mathbf{kk'}}
+  \begin{pmatrix}
+    \varepsilon_{i\mathbf{k}} && \Delta^{eq}_i & \\
+    & \varepsilon_{i\mathbf{k}} && \Delta^{eq}_i \\
+    \Delta^{eq}_i && -\varepsilon_{i\mathbf{k}} & \\
+    & \Delta^{eq}_i && -\varepsilon_{i\mathbf{k}}
+  \end{pmatrix}
+\end{eqnarray*}
+
+Now we proceed with the first order.
+
+\begin{eqnarray*}
+i\frac{d}{dt} \rho_{i\mathbf{k}\mathbf{k}'}\big|_1
+  &=&
+  \left( 
+    H_{i\mathbf{k}' \mathbf{k'}}^{(1)} 
+    -
+    H_{i\mathbf{kk}}^{(2)}
+  \right)\bigg|_0
+    \rho_{i\mathbf{kk'}}\big|_1
+    \\
+  &+&
+  \left(
+    H_{i\mathbf{k}' \mathbf{k}}^{(1)}\big|_1 \rho_{i\mathbf{kk}}\big|_0 
+    -
+    H_{i\mathbf{k'k}}^{(2)}\big|_1
+    \rho_{i\mathbf{k'k'}}\big|_0
+  \right)
+\end{eqnarray*}
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(1)}\big|_0
+  =
+  -\mathbf{J}_{i\mathbf{kk'}} \cdot \mathbf{A} \,
+  \begin{pmatrix}
+    1 &  & & \\
+     & -1 & & \\
+    && 1 &  \\
+    &&  & -1& 
+  \end{pmatrix}
+\end{eqnarray*}
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(2)}\big|_0
+  =
+  -\mathbf{J}_{i\mathbf{kk'}} \cdot \mathbf{A} \,
+  \begin{pmatrix}
+    1 &&  & \\
+    & 1 &&  \\
+     && -1 & \\
+    &  &&-1 
+  \end{pmatrix}
+\end{eqnarray*}
+
+The second order is
+
+\begin{eqnarray*}
+  i\frac{d \rho_{i\mathbf{k}\mathbf{k}}}{dt}
+  &=&
+    \left( 
+      H_{i\mathbf{kk}}^{(1)}  - H_{i\mathbf{kk}}^{(2)} 
+    \right)\bigg|_0
+    \rho_{i\mathbf{kk}}\big|_2
+    \\
+    &+&
+    \sum_{\mathbf{q}}^{}
+    \left( 
+    H_{i\mathbf{kq}}^{(1)}\big|_1 \rho_{i\mathbf{kq}}\big|_1 -
+    H_{i\mathbf{qk}}^{(2)}\big|_1 \rho_{i\mathbf{qk}}\big|_1
+    \right)
+    \\
+    &+&
+    \left( 
+      H_{i\mathbf{kk}}^{(1)} - H_{i\mathbf{kk}}^{(2)} 
+    \right)\bigg|_2
+      \rho_{i\mathbf{kk}}\big|_0
+\end{eqnarray*}
+\begin{eqnarray*}
+  H_{i\mathbf{kk}}^{(1,2)}\big|_2 = 
+  H_{i\mathbf{kk}}^{(1,2)}\big|_{2,D}
+  +H_{i\mathbf{kk}}^{(1,2)}\big|_{2,H}
+  +H_{i\mathbf{kk}}^{(1,2)}\big|_{2,L}
+\end{eqnarray*}
+Diamagnetic quasiparticle current contribution
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(1)}\big|_{0,D}
+  =
+  \delta_{\mathbf{kk'}} \frac{s_ie^2}{2m_i}\mathbf{A}^2
+  \begin{pmatrix}
+    1 &  & & \\
+     & -1 & & \\
+    && 1 &  \\
+    &&  & -1& 
+  \end{pmatrix}
+\end{eqnarray*}
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(2)}\big|_{0,D}
+  =
+  \delta_{\mathbf{kk'}} \frac{s_ie^2}{2m_i}\mathbf{A}^2
+  \begin{pmatrix}
+    1 &&  & \\
+    & 1 &&  \\
+     && -1 & \\
+    &  &&-1 
+  \end{pmatrix}
+\end{eqnarray*}
+Higgs contribution
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(1)}\big|_{0,D}
+  =
+  \delta_{\mathbf{kk'}} \delta \Delta'\big|_2
+  \begin{pmatrix}
+     & 1 & & \\
+    1 &  & & \\
+    &&  & 1 \\
+    && 1 &  & 
+  \end{pmatrix}
+\end{eqnarray*}
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(2)}\big|_{0,D}
+  =
+  \delta_{\mathbf{kk'}} \delta \Delta'\big|_2
+  \begin{pmatrix}
+     && 1 & \\
+    &  && 1 \\
+    1 &&  & \\
+    & 1 && 
+  \end{pmatrix}
+\end{eqnarray*}
+Leggett contribution
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(1)}\big|_{0,D}
+  =
+  \delta_{\mathbf{kk'}} \delta \Delta''\big|_2
+  \begin{pmatrix}
+     & i & & \\
+    -i &  & & \\
+    &&  & i \\
+    && -i &  & 
+  \end{pmatrix}
+\end{eqnarray*}
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(2)}\big|_{0,D}
+  =
+  \delta_{\mathbf{kk'}} \delta \Delta''\big|_2
+  \begin{pmatrix}
+     && -i & \\
+    &  && -i \\
+    i &&  & \\
+    & i && 
+  \end{pmatrix}
+\end{eqnarray*}
+
+And third order
+\begin{eqnarray*}
+i\frac{d}{dt} \rho_{i\mathbf{k}\mathbf{k}'}\big|_3
+  &=&
+  \left( 
+    H_{i\mathbf{k'k'}}^{(1)} - H_{i\mathbf{kk} }^{(2)} 
+  \right)\bigg|_0
+    \rho_{i\mathbf{kk'}}\big|_3
+    \\
+	&+&
+  \sum_{\mathbf{q}}^{}
+  \left( 
+    H_{i\mathbf{k'q}}^{(1)}\big|_1 \rho_{i\mathbf{kq }}\big|_2 -
+    H_{i\mathbf{qk} }^{(2)}\big|_1 \rho_{i\mathbf{qk'}}\big|_2
+  \right)
+  \\
+	&+&
+  \left( 
+    H_{i\mathbf{k'k'}}^{(1)} - H_{i\mathbf{kk} }^{(2)} 
+  \right)\bigg|_2
+    \rho_{i\mathbf{kk'}}\big|_1
+\end{eqnarray*}
+
+\end{document}
+
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(1)}\big|_{0,D}
+  =
+  \begin{pmatrix}
+    h11 & h12 & & \\
+    h21 & h22 & & \\
+    && h11 & h12 \\
+    && h21 & h22 & 
+  \end{pmatrix}
+\end{eqnarray*}
+\begin{eqnarray*}
+  H_{i\mathbf{kk'}}^{(2)}\big|_{0,D}
+  =
+  \begin{pmatrix}
+    h11 && h21 & \\
+    & h11 && h21 \\
+    h12 && h22 & \\
+    & h12 && h22
+  \end{pmatrix}
+\end{eqnarray*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-11-08 paper/paper_v1.tex
a

@@
 
-\begin{itemize}
-	\item This work: 1) Higgs oscillations in two-band sc. with bands in different limits, 2) Nonequilibrium optical conductivity, 3) Leggett mode in dirty-limit, 4) Prediction for MgB$_2$
-\end{itemize}
-
 When a global symmetry is spontaneously broken, collective excitations emerge.
@@
 \subsection{Impurity scattering}
+\label{sec:MB}
 In a clean system momentum conservation yields $\mathbf{J}_{i\mathbf{kk'}} \sim
@@
 Lorentzian in momentum transfer space, explicitly written as
-\begin{eqnarray*}
+\begin{eqnarray}
 	\langle \left|\mathbf{e} \cdot
@@
 	+ \gamma_i^2} \,,
-\end{eqnarray*}
+	\label{eq:MB}
+\end{eqnarray}
 with Fermi velocity $v_{F_i}$ density of states of the Fermi level $N_i(0)$ and
@@
 A derivation of this matrix element
-following [Murotani] is reviewed in Appendix X.
+following [Murotani] is reviewed in Appendix \ref{apdx:MB}.
 
@@
 orders of $A(t)$. To account for effects of a THG response, we consider terms up to
-third order. As detailed in Appendix X, the current only has odd order
+third order. As detailed in Appendix \ref{apdx:model}, the current only has odd order
 components $\mathbf{j} = \mathbf{j}\big|_0 +\mathbf{j}\big|_3 + \dots$ and the
@@
 A detailed derivation and an explicit presentation of the full equations of
-motion is given in Appendix X.
+motion is given in Appendix \ref{apdx:model}.
 
@@
 The Debye energy for NbN is order order of 
-$\omega_D = \SI{5}{\milli\electronvolt}$, but
+$\omega_D = \SI{50}{\milli\electronvolt}$, but
 for better numerical resolvability we choose $\omega_D =
-\SI{2}{\milli\electronvolt}$.
+\SI{20}{\milli\electronvolt}$.
 
@@
 Both the oscillation amplitude and $\Delta_{\infty}$ show a
-strong dependence on the impurity scattering rate. For $\gamma\rightarrow 0$
-they both vanish while they peak at $\gamma\approx
-\Delta^{eq}$, see Fig. \ref{fig:singleband-gap}(f). These results underline the
+strong dependence on the impurity scattering rate peaked at $\gamma\approx
+\Delta^{eq}$, see Fig. \ref{fig:singleband-gap}(f). For $\gamma\rightarrow 0$
+the Higgs resonance vanishes. [Discussion photon $\mathbf{q}$ and $A^2$ term] These results underline the
 importance of impurity scattering for the excitation efficiency of collective
-Higgs modes already uncovered by Refs. [].
-In agreement with the argument from Sec. X this dependence is well approximated by
+Higgs modes uncovered recently [].
+We can understand this result by examining the matrix elements of the current
+operator, Eq. (\ref{eq:MB}), following the discussion of Sec. \ref{sec:MB}.
+Indeed, the $\gamma$-dependence closely follows
 the functional form $\gamma/(\Delta_{eq}^2+\gamma^2)$.
-
-Next we compute the optical conductivity
-\begin{eqnarray*}
-\sigma(\omega)=\frac{j(\omega)}{i\omega A(\omega)}
-\end{eqnarray*}
-and plot its real and
-imaginary part in Figs. \ref{fig:cond-lin}(a-b) for various impurity
-concentrations.
 
@@
 conductivity oscillation is peaked at $2\Delta_{\text{eq}}$.}
+\label{fig:cond-pp}
 \end{figure}
+
+Next we compute the optical conductivity in linear response
+\begin{eqnarray*}
+  \sigma_0(\omega)\big=\frac{j(\omega)\big|_1}{i\omega A(\omega)} \,.
+\end{eqnarray*}
+Real and
+imaginary parts $\sigma'(\omega),\sigma''(\omega)$ are plotted 
+in Fig. \ref{fig:cond-lin}(a-b) for various impurity
+concentrations and in Fig. \ref{fig:cond-lin} for various temperatures.
+At low temperatures $\sigma'$ shows a clear conductivity gap below $2\Delta^{eq}$. 
+In the clean limit, a pronounced coherence peak is observed around $2\Delta$,
+reflecting the additional density of states amassed above the quasiparticle gap. 
+The above-gap absorption reaches a maximum at $\gamma \sim 2\Delta$ and broadens
+into the characteristic dome shape for which the original analytical MB
+expression has been derived []. In the $T\rightarrow 0$ limit, the
+conductivty shows a condensate peak $\sigma'(\omega)
+= \delta(\omega)$ below the gap which is broadened at
+finite temperatures.
+
+Higher orders of the optical conductivity include
+contributions of collective modes that smooth out the absorption
+edge and add spectral weight inside the conductivity gap.
+Here, we calculate the non-linear contribution,
+$$\sigma(\omega, \delta t_{pp})=\frac{j(\omega)\big|_1+j(\omega)\big|_3}{i\omega
+A(\omega)} \,,$$
+in a pump-probe setting. To this end, we pump the system with an intense 
+pulse of fluence $A=X$ and after a delay of $\delta t_{pp}$, apply a probe
+pulse. Following experimental schemes [], we perform two simulations modelling
+both pump and probe, $j_{p-p}$, and a pump only $j_{p}$e. 
+We then compute the optical conductivity
+from the difference in currents $j=j_{p-p}-j_{p}$. This ensures that resilient
+components of the pump do not contribute to the optical conductivity.
+
+Figures \ref{fig:cond-pp}(a-b) show the real and imaginary part of the optical
+conductivity $\sigma(\omega,\delta t_{pp}$ as a function of frequency and
+  pump-probe delay. It can be seen that the additive third-order contribution
+  $j\big|_3$ add spectral weight to the conductivity that slightly fills the
+  absorption gap. These contributions show clear oscillations for all
+  frequencies $\omega$, as can be seen from Fig. \ref{fig:cond-pp}(c) where
+  the dome-shaped envelope has been subtracted. A Fourier transform of these
+  oscillations is shown in Fig. \ref{fig:cond-pp}(e) indicating that the
+  oscillation frequency matches $2\Delta^{eq}$, the resonance frequency of the
+  Higgs mode. Our results show that signatures of the Higgs mode are measureable
+  in the pump-probe response of the optical conductivity. All features are
+  resolvable by present-day experimental techniques. [Discuss agreement with
+  experiment]
+
 %\begin{comment}
@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
 	\centering
 	\includegraphics[width=\columnwidth]{figures/m-fig1.pdf}
-	\caption{Real part $\sigma'$ (A,C) and imaginary part $\sigma''$ (B,D)
+	\caption{Real part $\sigma'$ (a,c) and imaginary part $\sigma''$ (b,d)
 		of optical conductivities to first order in $A$ 
@@
 various temperatures at $\gamma/2\Delta=10$. $\sigma'$ show a characteristic
-conductivity gap below $T_C$ and both $\sigma'$, $\sigma''$ diverge in the
-static limit.}
-\label{fig:singleband-gap}
+conductivity gap below $T_C$ and both $\sigma'$, $\sigma''$ diverges as
+$1/\omega$ in the static limit.}
+\label{fig:cond-lin2}
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Higgs oscillations}
-\label{sec:higgs_oscillations}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{itemize}
-	\item Equation for Current
-	\item Equation for optical conductivity
-	\item Present and discuss equilibrium optical conductivity in Fig. 1 for the four different limit cases, used in the rest of the paper
-\end{itemize}
-
-\begin{figure}[ht]
+\begin{figure}[t]
   \centering
   \includegraphics[width=\columnwidth]{figures/fig-cond-2d-fourcases}
-  \caption{Caption}
+  \caption{Time-resolved optical conductivity for the case were bands are in the
+  limit (a) clean-clean, (b) clean-dirty, (c) dirty-clean, (d) dirty-dirty.}
 \end{figure}
+
+Motivation by the good agreement of the theory with experimental data, we now
+discuss the case of a two-band superconductor. Here, the superconducting state
+of MgB$_2$ is likely the most widely studied example and we adopt it as a
+reference material. We loosely model the
+$\pi$- and $\sigma$-bands believed to be responsible for superconductivity by
+choosing material parameters 
+$\Delta_{\pi}=\SI{3}{\milli\electronvolt}$,
+$\Delta_{\sigma}=\SI{7}{\milli\electronvolt}$, 
+$\varepsilon_{F,\pi}=\SI{2.9}{\electronvolt}$,
+$\varepsilon_{F,\sigma}=\SI{0.7}{\electronvolt}$, 
+$m_\pi=0.85m_e$,
+$m_\sigma=1.38 m_e$, 
+$\omega_D=\SI{50}{\milli\electronvolt}$,
+$s_\pi=1$,
+$s_\sigma=-1$.
+
+\subsection{Optical conductivity}
+
 \begin{figure*}[ht]
@@
   \includegraphics[width=\textwidth]{figures/fig-three-pulses}
-  \caption{Caption}
+  \caption{Time-resolved optical conductivity for three different pulses.}
 \end{figure*}
 
-\begin{itemize}
-	\item Equation for $\delta\Delta(t)$
-	\item Show and discuss Higgs oscillations in Fig. 2 of the four cases with a suitable pump pulse (refer to appendix B for details about the pump pulse)
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Nonequilibrium optical conductivity}
-\label{sec:noneq_cond}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{itemize}
-	\item Equation for nonequilibrium optical conductivity with two pulses. Maybe here more details (instead of appendix), as this is not covered by the Murotani paper
-	\item Show and discuss nonequlibrium conductivity in Fig. 3.
-	\item More figures of nonequilibrium conductivity? Suggestions: Imaginary part, maybe appendix. Nice 3d plot. Oscillations along cuts.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Leggett mode} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Leggett mode and THG} 
 \label{sec:leggett_mode}
@@
 	\item Definition, equation of Leggett mode
-	\item Parameters for Fig.4 where Leggett mode occurs
-	\item Discuss Fig. 4
-	\item Maybe rethink what exactly to show in Fig. 4
-	\item New plot of time-resolved conductivity showing Leggett mode?
+	\item Leggett equation of motion (equation for imaginary part of gap)
+	  completely decouples from the remaining system of equations!
+	\item In light of this - does Leggett mode really couple with Higgs
+	  mode? Here the issue of the Fourier-transform comes up again. Is it
+	  possible that the Fourier-transform of the whole time-range is the
+	  correct approach. A point is that Leggett mode is peaked in between
+	  the two gaps, but all oscillation contirbutions above $2\Delta_1$ are
+	  damped very fast (exponential) so that at later times it looks like
+	  the energy of the mode is $2\Delta_1$.
+	\item TGH experiment. Here, let's decompose the THG signal in
+	  quasiparticle, Higgs, Leggett contributions and show the THG in two
+	  ways. First, a plot as a function of frequency for the four impurity
+	  cases. Second, a plot as a function of temperature for the four cases.
+	  The two plots should agree qualitatively, since changing the
+	  temperature changes the gap (this is what experimentalists do).
+	  Additionally, however, thermal effects contribute which might make
+	  things a bit harder to see.
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{MgB$_2$}
-\label{sec:mgb2}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{itemize}
-	\item Parameters which match MgB$_s$
-	\item Show prediction in Fig. 6 of equilibrium conductivity, Higgs oscillations, nonequilibrium conductivity
-\end{itemize}
-
-\begin{figure}[H]
-    \centering
-    %\includegraphics[width=\columnwidth]{figures/mgb2.png}
-    \Huge{TODO}
-    \caption{\label{fig:mgb2}%
-    Result with parameters for MgB$_2$ a) Equilibrium optical conductivity, b) Higgs oscillations, c) pump-probe conductivity and spectra}
-\end{figure}%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}
@@
 %\end{comment}
+\newpage
 \appendix
@@
 \section{Mattis-Bardeen substitution}
+\label{apdx:MB}
 
@@
 \section{Model}
+
+\label{apdx:model}
 \begin{eqnarray}

### 2020-11-08 multiband/leggett/leggett-averaging.py

@@ -1,0 +1,594 @@
+#%%
+import numpy as np
+from numpy import sqrt
+# import matplotlib as mpl
+# mpl.use('Agg')
+import matplotlib.pyplot as plt
+from scipy import integrate
+from scipy import interpolate
+from scipy.fftpack import fftfreq, fftshift
+import scipy
+import time
+import pickle
+import sys
+import os
+import gc
+
+code_version = {
+    "1.0": "first version",
+    "1.1": "pulse shape modified, now parameter te, te_pr",
+    "1.2": "U calculated from gap and v (gap and v are input parameters), r21e r21o saved"
+}
+
+
+
+u_temp = 116.032
+params_ = [
+    {
+        "Ne": [10],
+        "tmin": [-40],
+        "tmax": [200],
+        # "tmax": [450],
+        "Nt": 450,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [0.015],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10,5])],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": [0.1],
+        "A0": [1],
+        "tau": [5],
+        "w":  [0],
+        "A0_pr": [0],
+        "te": 0,
+        "tau_pr": [1.5],
+        "w_pr": [1],
+        "t_delay": [0],
+        "te_pr": 0
+    }
+]
+
+
+params = []
+for p in params_:
+    for Ne in p["Ne"]:
+        for tmin in p["tmin"]:
+            for tmax in p["tmax"]:
+                for T in p["T"]:
+                    for wd in p["wd"]:
+                        for m in p["m"]:
+                            for ef in p["ef"]:
+                                for v in p["v"]:
+                                    for tau in p["tau"]:
+                                        for w in p["w"]:
+                                            for tau_pr in p["tau_pr"]:
+                                                for w_pr in p["w_pr"]:
+                                                    for g in p["g"]:
+                                                        for A0 in p["A0"]:
+                                                            for A0_pr in p["A0_pr"]:
+                                                                for t_delay in p["t_delay"]:
[…]

### 2020-11-08 multiband/leggett/leggett.py

@@ -1,0 +1,611 @@
+#%%
+import numpy as np
+from numpy import sqrt
+# import matplotlib as mpl
+# mpl.use('Agg')
+import matplotlib.pyplot as plt
+from scipy import integrate
+from scipy import interpolate
+from scipy.fftpack import fftfreq, fftshift
+import scipy
+import time
+import pickle
+import sys
+import os
+import gc
+
+code_version = {
+    "1.0": "first version",
+    "1.1": "pulse shape modified, now parameter te, te_pr",
+    "1.2": "U calculated from gap and v (gap and v are input parameters), r21e r21o saved"
+}
+
+
+
+u_temp = 116.032
+params_ = [
+    {
+        "Ne": [500],
+        "tmin": [-40],
+        "tmax": [200],
+        # "tmax": [450],
+        "Nt": 450,
+        "T": [4/u_temp],#,0.5,0.54,0.56],
+        "wd":  [0.15],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10,5])],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": [0.01],
+        "A0": [1],
+        "tau": [10],
+        "w":  [0.3],
+        "A0_pr": [0],
+        "te": 0,
+        "tau_pr": [1.5],
+        "w_pr": [1],
+        "t_delay": [0],
+        "te_pr": 0
+    }
+]
+
+
+params = []
+for p in params_:
+    for Ne in p["Ne"]:
+        for tmin in p["tmin"]:
+            for tmax in p["tmax"]:
+                for T in p["T"]:
+                    for wd in p["wd"]:
+                        for m in p["m"]:
+                            for ef in p["ef"]:
+                                for v in p["v"]:
+                                    for tau in p["tau"]:
+                                        for w in p["w"]:
+                                            for tau_pr in p["tau_pr"]:
+                                                for w_pr in p["w_pr"]:
+                                                    for g in p["g"]:
+                                                        for A0 in p["A0"]:
+                                                            for A0_pr in p["A0_pr"]:
+                                                                for t_delay in p["t_delay"]:
[…]

### 2020-12-06 diagrammatics/j3-farm.py
standard commit

@@ -43,8 +43,8 @@ filename = 'results-j3.pickle'
 
 params_ = [
     {
-        "Ne": [600],
-        "eta":  [0.01],
+        "Ne": [1200],
+        "eta":  [0.004],
         # "w":  [0.1/u_w],
         "w":  np.linspace(0.1,0.85,25),
         # "T": np.linspace(0,50,32)/u_temp,

### 2020-12-06 diagrammatics/optical-conductivity-analytical.py

@@ -16,6 +16,25 @@ import os
 import gc
 import time
 from multiprocessing import Pool
+from cycler import cycler
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
 
 code_version = {
     "1.0": "first version",
@@ -37,7 +56,7 @@ u_w = u_e*meV_to_THz
 u_temp = 116.032
 params_ = [
     {
-        "Ne": [600],
+        "Ne": [6400],
         "tmin": [-80],
         "tmax": [300],
         # "tmax": [450],
@@ -444,10 +463,10 @@ def integ(x, axis):
     return np.sum(x, axis=axis) * dx
     """
 
-#% optical conductivity first order
+# #%% optical conductivity first order
 
[…]

### 2020-12-06 diagrammatics/plot-figure-fourcases-comparison.py

@@ -960,8 +960,8 @@ plt.figure('cond-imp-imag', figsize=(3,2.8))
 plt.clf()
 plt.figure('cond-imp-legend', figsize=(5,5))
 plt.clf()
-gammas1 = gammas[np.array([16])]
-gammas2 = gammas[np.array([1])]
+gammas1 = gammas[np.array([-1])]
+gammas2 = gammas[np.array([-3])]
 for g1 in gammas1:
     for g2 in gammas2:
         g = np.array([g1,g2])
@@ -977,8 +977,8 @@ for g1 in gammas1:
         u_w = u_e*meV_to_THz
         plt.plot(wg*u_w,np.abs(c.real), label=f'$\gamma/2\Delta={str(np.round(g[0]/2/gap,1))}$',ls=ls)
         plt.xlabel('Frequency (THz)')
-        # plt.xlim((0,5.5))
-        plt.ylim((0,2e5))
+        plt.xlim((0,5.5))
+        plt.ylim((0,1e5))
         plt.ylabel('$\sigma\,\'$ ($\Omega^{-1}$cm$^{-1}$)')
         plt.ticklabel_format(axis="y", style="sci", scilimits=(2,4))
         # plt.legend()

### 2020-12-06 diagrammatics/plot-j3.py

@@ -30,6 +30,7 @@ plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
 
 folder = 'j3_g10_5_v0p2'
 folder = 'j3_g10_5_v0'
+folder = 'j3_g10_5_vall'
 files = glob.glob(f'{folder}/*.pickle')
 
 save_plots = False
@@ -93,16 +94,20 @@ jl2 = []
 jqp = []
 durations = []
 
+vv = [0,0.02,0.05,0.5,0.5]
+v = 0.0
+
 for r in res:
-    w.append(r['w'])
-    T.append(r['T'])
+    if r['v']==v:
+        w.append(r['w'])
+        T.append(r['T'])
 
-    jh.append(r['jH'])
-    jl.append(r['jL'])
-    jl2.append(r['jL2'])
-    jqp.append(r['jQP'])
+        jh.append(r['jH'])
+        jl.append(r['jL'])
+        jl2.append(r['jL2'])
+        jqp.append(r['jQP'])
 
-    durations.append(r['duration'])
+        durations.append(r['duration'])
 
 w = np.array(w)
 T = np.array(T)
@@ -136,7 +141,7 @@ print('eta', r['eta'])
 print('mean duration:', np.mean(durations))
 
 #%%
-plt.figure('j3')
+plt.figure('j3', figsize=(9,8))
 plt.clf()
 plt.ion()
 c = 1/9
@@ -145,7 +150,7 @@ plt.plot(x, np.abs(jh)*c, '.-', label='Higgs')
 plt.plot(x, np.abs(jl)*magn, label='Leggett')
 plt.plot(x, np.abs(jqp_)*c/2, label='QP')
 
-plt.plot(x, np.abs(jh*c-jqp_*c+jl), label='Full')
+# plt.plot(x, np.abs(jh*c-jqp_*c/2+jl), label='Full')
 
 if omega:
     plt.axvline(d_eq0[0], c='gray', lw=0.5)
@@ -155,9 +160,14 @@ plt.xlabel(xlabel)
 
 plt.legend()
 
-compare = True
+compare = True 
 if 'xx' in globals() and compare:
-    plt.plot(xx,JQP*factor, '--', c='r')
-    plt.plot(xx,JH*factor, '--', c='b')
-    plt.plot(xx,JL*factor*magn, '--', c='y')
[…]

### 2020-12-06 diagrammatics/optical-conductivity-analytical.py
standard commit

@@ -613,7 +613,8 @@ w = wsl[ax,ax,:] + 1j*eta
 
 ek,ek2,eek,eek2,d,W12,nfeek,nfeek2,nfeekm,nfeek2m,fk,fk2 = genE(2)
 
-x33_ = 1
+# x33_ = ((d**2 + eek**2 - ek**2)*(nfeek - nfeekm))/(2.*eek*(eek - w)*(eek + w))
+x33_ = -((-d**2 + eek**2 + ek**2)/(2*eek**3 - 2*eek*w**2))
 x33 = N0[:,ax] * integ(x33_, axis=1)
 
 kappa = 8*d_eq0[0]*d_eq0[1]*U[0,1]/np.linalg.det(U)

### 2020-12-06 diagrammatics/optical-conductivity-analytical.py
standard commit

@@ -70,7 +70,7 @@ params_ = [
         # "g": [ r['g'] ],
         "pre_d0": np.array([0.3,0.7]),
         # "pre_d0": np.array([0.29817841,0.70076507]),
-        "v": [0.5],#np.linspace(0.0002,1,40),
+        "v": [0.2],#np.linspace(0.0002,1,40),
         "A0": [1],
         "tau": [10],
         "w":  [0.2],
@@ -533,7 +533,7 @@ def integ(x, axis):
 #%% Leggett current third order
 compare =False 
 
-eta = 0.001
+eta = 0.005
 wsl = np.linspace(0,1,300)
 
 w = 2*(wsl[ax,ax,:] + 1j*eta)
@@ -568,9 +568,9 @@ d_theta = 2 * 2**(-3) * np.einsum('ijw,jw->iw',Linv,x33*si/mi)
 
 
 
-# plt.figure('jL')
-# plt.clf()
-# plt.plot(wsl,np.abs(jL), label='Leggett=QPdia + phase')
+plt.figure('jL')
+plt.clf()
+plt.plot(wsl,np.abs(jL), label='Leggett=QPdia + phase')
 # plt.plot(wsl,np.abs(jL2),'--', label='Leggett2')
 # compare = False
 # if 'xx' in globals(): compare = True
@@ -586,27 +586,27 @@ d_theta = 2 * 2**(-3) * np.einsum('ijw,jw->iw',Linv,x33*si/mi)
 # plt.legend()
 # plt.pause(0.01)
 
-plt.figure('dphi')
+# plt.figure('dphi')
 # plt.title('$\delta\\varphi$')
 # plt.plot(wsl, np.abs(d_phi)/wsl**2/(1/m1-1/m2)/10)
 # plt.axvline(d_eq0[0], c='gray', lw=0.5)
 # plt.axvline(d_eq0[1], c='gray', lw=0.5)
 
-d_phi = (d_theta[0]-d_theta[1]) / (s1/m1-s2/m2)
+# d_phi = (d_theta[0]-d_theta[1]) / (s1/m1-s2/m2)
 
-ddet = w2**2 + kappa*(x33[0]+x33[1])/(x33[0]*x33[1])
-plt.plot(wsl,1/np.abs(ddet))
+# ddet = w2**2 + kappa*(x33[0]+x33[1])/(x33[0]*x33[1])
[…]

### 2020-12-06 diagrammatics/optical-conductivity-analytical.py
standard commit

@@ -614,8 +614,7 @@ w = wsl[ax,ax,:] + 1j*eta
 ek,ek2,eek,eek2,d,W12,nfeek,nfeek2,nfeekm,nfeek2m,fk,fk2 = genE(2)
 
 # x33_ = ((d**2 + eek**2 - ek**2)*(nfeek - nfeekm))/(2.*eek*(eek - w)*(eek + w))
-
-x33_ = -((-d**2 + eek**2 + ek**2)/(2*eek**3 - 2*eek*w**2))
+x33_ = -((d**2 + eek**2 - ek**2)/(2*eek**3 - 2*eek*w**2))
 x33 = N0[:,ax] * integ(x33_, axis=1)
 
 kappa = 8*d_eq0[0]*d_eq0[1]*U[0,1]/np.linalg.det(U)

### 2020-12-06 diagrammatics/optical-conductivity-analytical.py
standard commit

@@ -56,7 +56,7 @@ u_w = u_e*meV_to_THz
 u_temp = 116.032
 params_ = [
     {
-        "Ne": [6400],
+        "Ne": [300],
         "tmin": [-80],
         "tmax": [300],
         # "tmax": [450],
@@ -66,11 +66,12 @@ params_ = [
         "s": np.array([1,-1]),
         "m": [ np.array([0.85, 1.38]) ],
         "ef": [ np.array([290, 70]) ],
-        "g": [ np.array([10,5])],
+        # "g": [ np.array([10,5])],
+        "g": [ np.array([1e-1,1e-1])],
         # "g": [ r['g'] ],
         "pre_d0": np.array([0.3,0.7]),
         # "pre_d0": np.array([0.29817841,0.70076507]),
-        "v": [0.2],#np.linspace(0.0002,1,40),
+        "v": [0.5],#np.linspace(0.0002,1,40),
         "A0": [1],
         "tau": [10],
         "w":  [0.2],
@@ -631,56 +632,12 @@ jphase = 4 * 1/2 * np.einsum('iw,ijw,jw->w',x33*si/(2*mi), Linv, x33*si/(2*mi) )
 jQPdia = 4 * 1/2 * (si/2/mi)**2 * x33 #paramagnetic current at third order
 
 jL = np.sum(jQPdia,0)+jphase
-
-# m1 = m[0]
-# m2 = m[1]
-# s1 = s[0]
-# s2 = s[1]
-
-# jL2 = -4 * 1/2*1/4* kappa * (s1/m1-s2/m2)**2 / (-w2**2 - kappa*(x33[0]+x33[1])/(x33[0]*x33[1]))
-
-
-# d_theta = np.einsum('ijw,jw->iw', Linv, x33*si/(2*mi))
-
-
-
 plt.figure('jL')
-# plt.clf()
-plt.plot(wsl,np.abs(jL), label='Leggett=QPdia + phase')
-# plt.plot(wsl,np.abs(jL2),'--', label='Leggett2')
-# compare = False
-# if 'xx' in globals(): compare = True
-# if compare:
-#     factor=1/np.max(np.abs(JL))*np.max(np.abs(jL))
-#     print(factor)
-#     plt.plot(xx,np.abs(JL)*factor, label='sim-Paul')
[…]

### 2020-12-06 diagrammatics/plot-j3.py

@@ -30,7 +30,8 @@ plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
 
 folder = 'j3_g10_5_v0p2'
 folder = 'j3_g10_5_v0'
-folder = 'j3_g10_5_vall'
+folder = 'j3_g10_5_vall-highres'
+# folder = 'j3_g10_5_vall'
 files = glob.glob(f'{folder}/*.pickle')
 
 save_plots = False
@@ -94,8 +95,8 @@ jl2 = []
 jqp = []
 durations = []
 
-vv = [0,0.02,0.05,0.5,0.5]
-v = 0.0
+vv = [0,0.02,0.05,0.2,0.5]
+v = 0.5
 
 for r in res:
     if r['v']==v:
@@ -171,3 +172,6 @@ if 'xx' in globals() and compare:
     plt.plot(xx,np.abs(JH_)[idx]*factor, '--', c='b')
     plt.plot(xx,np.abs(JL_)[idx]*factor*magn, '--', c='y')
     # plt.plot(xx,np.abs(JFULL_[idx])*factor, '--', c='g')
+plt.title(f'$g=10/5 v={str(v)}$')
+
+plt.savefig(next('comp'))

### 2020-12-09 diagrammatics/THG-comparison.py
a

@@ -10,6 +10,7 @@ from mpl_toolkits.mplot3d import Axes3D
 from cycler import cycler
 import matplotlib as mpl
 from scipy.signal import find_peaks
+from scipy import signal
 
 CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
 tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
@@ -30,6 +31,8 @@ plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
 
 folder = 'leggett-driving-comparison'
 folder2 = 'leggett-driving-comparison-QP'
+# folder = 'leggett-driving-comparison2'
+# folder2 = 'leggett-driving-comparison-QP2'
 # folder = 'driving'
 files = glob.glob(f'../multiband/{folder}/*.pickle')
 files2 = glob.glob(f'../multiband/{folder2}/*.pickle')
@@ -722,6 +725,7 @@ JQP_ = []
 JFULL_ = []
 V_ = []
 
+# for j, v in z([vs[-1]]):
 for j, v in z(vs):
     plt.pause(0.1)
     for i, case in z(fourcases):
@@ -731,7 +735,7 @@ for j, v in z(vs):
         JQP = []
         JFULL = []
         # plt.figure()
-        for k, w in z(wss):
+        for k, w in z(wss[wss>0.15]):
             r = sel(first=False, w=w, v=v, g=case)
             rqp = sel(res=resqp, first=False, w=w, v=v, g=case)
             if r == []:
@@ -746,43 +750,101 @@ for j, v in z(vs):
 
             j3_para = r['jp_3']
             j3L = r['jd_3']
+            jFull = j3_para + j3L
 
             j3QP =j3q_para
             j3H = j3_para - j3QP
 
-            def find3w(j3):
-                tw, j3w = fft(t,np.nan_to_num(j3))
+
+            t0 = 00
+            t1 = 230
+            sl = np.logical_and(t>t0,t<t1)
+            tsl = t[sl]
+            def find3w(t,j3):
+                # fs_tpp = 1/(t[1]-t[0])
+                # filt_order = 8
[…]

### 2020-12-09 diagrammatics/j3-farm.py

@@ -21,28 +21,35 @@ code_version = {
     "1.0": "first version",
 }
 
-if len(sys.argv) != 3:
-    job_ID = -1
-    task_ID = job_ID
-    task_count = 0
-else:
+
+if len(sys.argv) == 4:
     job_ID = int(sys.argv[1])
     task_ID = int(sys.argv[1])
     task_count = int(sys.argv[2])+1
+    parallel = bool(sys.argv[3])
+else:
+    job_ID = -1
+    task_ID = job_ID
+    task_count = 0
+    parallel = False
 
 u_t = 6.58285E-2
 u_e = 10
 u_conductivity = 881.553 #Ohm^-1 cm-1
 meV_to_THz = 0.2417990504024
 u_w = u_e*meV_to_THz
-
 u_temp = 116.032
 
-parallel = False
-filename = 'results-j3.pickle'
+filename = f'results-j3-parallel{parallel}.pickle'
 
-params_ = [
-    {
+if task_ID != -1:
+    # from parameters import params, parallel
+    exec(open("./parameters.py").read())
+    params = params[task_ID::task_count]
+    print('parameters loaded')
+else:
+    params_ = [
+        {
         "Ne": [1200],
         "eta":  [0.004],
         # "w":  [0.1/u_w],
@@ -57,39 +64,31 @@ params_ = [
         "pre_d0": np.array([0.3,0.7]),
         "v": [0,0.02,0.05,0.2,0.5]
     }
-]
-
-
-params = []
-for p in params_:
-    for Ne in p["Ne"]:
-        for T in p["T"]:
-            for wd in p["wd"]:
-                for m in p["m"]:
-                    for ef in p["ef"]:
-                        for v in p["v"]:
-                            for w in p["w"]:
-                                for eta in p["eta"]:
-                                    for g in p["g"]:
-                                        params.append({
-                                                        "Ne": Ne,
-                                                        "T": T,
-                                                        "wd": wd,
-                                                        "s": p["s"],
-                                                        "m": m,
-                                                        "ef": ef,
-                                                        "g": g,
-                                                        "pre_d0": p["pre_d0"],
-                                                        "v": v,
-                                                        "w":  w,
-                                                        "eta": eta
-                                                    })
-
-print(len(params),'parameters generated')
-
-if task_ID != -1:
-    params = params[task_ID::task_count]
-else:
+    ]
+    params = []
+    for p in params_:
+        for Ne in p["Ne"]:
+            for T in p["T"]:
+                for wd in p["wd"]:
[…]

### 2020-12-09 diagrammatics/j3_T/mega_script.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-MAX=99
+MAX=4
 for i in `seq 0 1 ${MAX}`
 do
 	FILENAME=job_file_${i}.ll

### 2020-12-09 diagrammatics/j3_T/parallel_mega_script.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
-
-MAX=31
+rm *.pickle
+MAX=7
 for i in `seq 0 1 ${MAX}`
 do
 	FILENAME=job_file_${i}.ll
@@ -15,7 +15,7 @@ do
 	echo "# @ node_usage = shared" >> $FILENAME
 
 	echo "# @ node = 1" >> $FILENAME
-	echo "# @ tasks_per_node = 14" >> $FILENAME
+	echo "# @ tasks_per_node = 56" >> $FILENAME
 	echo "# @ environment = COPY_ALL" >> $FILENAME
 	echo "# @ notification = never" >> $FILENAME
 	echo "# @ notify_user =" >> $FILENAME
@@ -25,7 +25,7 @@ do
 	echo "# exit on error" >> $FILENAME
 	echo "set -e" >> $FILENAME
 
-	echo "python3 ../j3-farm.py ${i} ${MAX}" >> $FILENAME
+	echo "python3 ../j3-farm.py ${i} ${MAX} True" >> $FILENAME
 
 
 	llsubmit $FILENAME >> log.out

### 2020-12-09 diagrammatics/leggett-higgs-analytical.py

@@ -558,3 +558,5 @@ plt.tight_layout()
 # plt.savefig('higgs-kernel.png', dpi=600)
 
 plt.plot(vsn,peaks_numerical*u_w,'D', markersize=3, c='red')
+plt.savefig(f'THGfigs/v{int(v*100)}by100.png', dpi=800)
+plt.savefig(f'THGfigs/v{int(v*100)}by100.pdf')

### 2020-12-09 diagrammatics/plot-j3.py

@@ -31,12 +31,21 @@ plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
 folder = 'j3_g10_5_v0p2'
 folder = 'j3_g10_5_v0'
 folder = 'j3_g10_5_vall-highres'
+folder = 'j3_T'
+folder = 'j3_Higgs'
 # folder = 'j3_g10_5_vall'
 files = glob.glob(f'{folder}/*.pickle')
 
 save_plots = False
 
 plt.ion()
+
+u_t = 6.58285E-2
+u_e = 10
+u_conductivity = 881.553 #Ohm^-1 cm-1
+meV_to_THz = 0.2417990504024
+u_w = u_e*meV_to_THz
+u_temp = 116.032
 
 def savefig(fname, transparent=True):
     if save_plots:
@@ -87,91 +96,182 @@ for f in files:
     except:
         reader.close()
 
-w = []
-T = []
-jh = []
-jl = []
-jl2 = []
-jqp = []
-durations = []
 
-vv = [0,0.02,0.05,0.2,0.5]
-v = 0.5
+v_list = [0.01,0.02,0.05,0.1,0.2,0.4]
+v_list = [0.02]
+w_list = np.array([0.3,0.4,0.5,0.6,0.7])
+w_list = [0.3]
+v = 0.02
+w_sel = 0.6
+gammas = [np.array([10, 0.00001]), np.array([0.00001, 10]),  np.array([10,5]), np.array([0.00001,0.00001])]
+gammas = [np.array([10, 0.0001]), np.array([0.00001, 10]),  np.array([10,5]), np.array([0.00001,0.00001])]
 
-for r in res:
-    if r['v']==v:
-        w.append(r['w'])
-        T.append(r['T'])
+ii = 0
+for v in v_list:
+    ii += 1
+    kk = 0
+    for w_sel in w_list:
+        kk += 1
 
-        jh.append(r['jH'])
-        jl.append(r['jL'])
-        jl2.append(r['jL2'])
-        jqp.append(r['jQP'])
+        w = []
+        T = []
+        jh = []
+        jl = []
+        jl2 = []
+        jqp = []
+        durations = []
+        d_eq = []
+        for r in res:
+            if r['v']==v and r['w'].real*u_w==w_sel and (r['g']==gammas[0]).all():
+                r2 = r
+                w.append(r['w'])
+                T.append(r['T'])
 
-        durations.append(r['duration'])
+                jh.append(r['jH'])
[…]

### 2020-12-09 multiband/leggett-driving-comparison2/parameters.py

@@ -1,6 +1,13 @@
 import numpy as np
 
 u_temp = 116.032
+u_t = 6.58285E-2
+u_e = 10
+u_conductivity = 881.553 #Ohm^-1 cm-1
+meV_to_THz = 0.2417990504024
+u_w = u_e*meV_to_THz
+
+u_temp = 116.032
 params_ = [
     {
         "Ne": [840],

### 2020-12-09 diagrammatics/2d-leggett.py
standard commit

@@ -1,0 +1,616 @@
+#%%
+from operator import mul
+import numpy as np
+from numpy import sqrt
+import matplotlib as mpl
+# mpl.use('Agg')
+import matplotlib.pyplot as plt
+from scipy import integrate
+from scipy import interpolate
+from scipy.fftpack import fftfreq, fftshift
+import scipy
+import time
+import pickle
+import sys
+import os
+import gc
+import time
+from multiprocessing import Pool
+from cycler import cycler
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+
+code_version = {
+    "1.0": "first version",
+    "1.1": "pulse shape modified, now parameter te, te_pr",
+    "1.2": "U calculated from gap and v (gap and v are input parameters), r21e r21o saved"
+}
+
+job_ID = -1
+task_ID = job_ID
+task_count = 0
+
+
+u_t = 6.58285E-2
+u_e = 10
+u_conductivity = 881.553 #Ohm^-1 cm-1
[…]

### 2020-12-09 diagrammatics/THG-comparison-temp.py

@@ -1,0 +1,928 @@
+#%%
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+import scipy
+from scipy.fftpack import fftfreq, fftshift
+import os
+from mpl_toolkits.mplot3d import Axes3D
+from cycler import cycler
+import matplotlib as mpl
+from scipy.signal import find_peaks
+from scipy import signal
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+folder = 'leggett-driving-comparisonT'
+files = glob.glob(f'../multiband/{folder}/*.pickle')
+
+save_plots = False
+
+def savefig(fname, transparent=True):
+    if save_plots:
+        plt.savefig(fname, transparent=transparent)
+
+def nmax(x):
+    return np.max(np.abs(x))
+
+def nm(x):
+    return x / np.max(np.abs(x))
+
+def fft(t,f, inverse=False):
[…]

### 2020-12-09 diagrammatics/j3-farm-Higgs.py

@@ -1,0 +1,456 @@
+#%%
+from operator import mul
+import numpy as np
+from numpy import sqrt
+import matplotlib as mpl
+mpl.use('Agg')
+import matplotlib.pyplot as plt
+from scipy import integrate
+from scipy import interpolate
+from scipy.fftpack import fftfreq, fftshift
+import scipy
+import time
+import pickle
+import sys
+import os
+import gc
+import time
+from multiprocessing import Pool
+
+code_version = {
+    "1.0": "first version",
+}
+
+
+if len(sys.argv) ==4:
+    job_ID = int(sys.argv[1])
+    task_ID = int(sys.argv[1])
+    task_count = int(sys.argv[2])+1
+    parallel = bool(sys.argv[3])
+    parallel = False
+else:
+    job_ID = -1
+    task_ID = job_ID
+    task_count = 0
+    parallel = False
+
+u_t = 6.58285E-2
+u_e = 10
+u_conductivity = 881.553 #Ohm^-1 cm-1
+meV_to_THz = 0.2417990504024
+u_w = u_e*meV_to_THz
+u_temp = 116.032
+
+filename = f'results-j3-parallel{parallel}.pickle'
+
+if task_ID != -1:
+    # from parameters import params, parallel
+    exec(open("./parameters.py").read())
+    params = params[task_ID::task_count]
+    print('parameters loaded')
+else:
+    params_ = [
+        {
+        "Ne": [1200],
+        "eta":  [0.004],
+        # "w":  [0.1/u_w],
+        "w":  np.linspace(0.1,0.85,25),
+        # "T": np.linspace(0,50,32)/u_temp,
+        "T": [50/u_temp],
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10,5])],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": [0.05,0.05,0.2,0.5]
+    }
+    ]
+    params = []
+    for p in params_:
+        for Ne in p["Ne"]:
+            for T in p["T"]:
+                for wd in p["wd"]:
+                    for m in p["m"]:
+                        for ef in p["ef"]:
+                            for v in p["v"]:
+                                for w in p["w"]:
[…]

### 2020-12-09 diagrammatics/j3_Higgs/mega_script.sh

@@ -1,0 +1,34 @@
+#!/bin/bash
+rm *.pickle
+MAX=447
+for i in `seq 0 1 ${MAX}`
+do
+	FILENAME=job_file_${i}.ll
+	echo "# @ shell=/bin/bash" > $FILENAME
+
+	echo "# Script for LoadLeveler job steps" >> $FILENAME
+
+	echo "# @ job_name = h-imp" >> $FILENAME
+	echo "# @ error  = error_${i}.err" >> $FILENAME
+	echo "# @ output = log_${i}.out" >> $FILENAME
+	echo "# @ job_type = MPICH" >> $FILENAME
+	echo "# @ node_usage = shared" >> $FILENAME
+
+	echo "# @ node = 1" >> $FILENAME
+	echo "# @ tasks_per_node = 1" >> $FILENAME
+	echo "# @ environment = COPY_ALL" >> $FILENAME
+	echo "# @ notification = never" >> $FILENAME
+	echo "# @ notify_user =" >> $FILENAME
+	echo "# @ class = 28core" >> $FILENAME
+	echo "# @ queue" >> $FILENAME
+
+	echo "# exit on error" >> $FILENAME
+	echo "set -e" >> $FILENAME
+
+	echo "export OMP_NUM_THREADS=1" >> $FILENAME
+
+	echo "python3 ../j3-farm-Higgs.py ${i} ${MAX} False" >> $FILENAME
+
+
+	llsubmit $FILENAME >> log.out
+done

### 2020-12-09 diagrammatics/j3_Higgs/parameters.py

@@ -1,0 +1,68 @@
+import numpy as np
+
+u_temp = 116.032
+u_t = 6.58285E-2
+u_e = 10
+u_conductivity = 881.553 #Ohm^-1 cm-1
+meV_to_THz = 0.2417990504024
+u_w = u_e*meV_to_THz
+
+params_ = [
+    {
+        # "Ne": [4000],
+        # "eta":  [0.004],
+        # # "w":  np.array([0.3,0.4,0.5,0.6])/u_w,
+        # # "w":  [0.3],
+        # "w": np.linspace(0,1,100),
+        # "T": [0.21],
+        # # "T": np.array([0.01, 15, 30, 50])/u_temp,
+        # "wd":  [5],
+        # "s": np.array([1,-1]),
+        # "m": [ np.array([0.85, 1.38]) ],
+        # "ef": [ np.array([290, 70]) ],
+        # "g": [ np.array([0.001, 10]) ],
+        # "pre_d0": np.array([0.3,0.7]),
+        # "v": [0.02]
+        "Ne": [4000],
+        "eta":  [0.005],
+        # "w":  np.array([0.3,0.4,0.5,0.6])/u_w,
+        "w":  np.linspace(0.00001,1,100),
+        "T": np.linspace(0.00001,50,100)/u_temp,
+        # "T": np.array([0.01, 15, 30, 50])/u_temp,
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10, 0.001]), np.array([0.001, 10]),  np.array([10,5])],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": [0.02,0.05,0.2,0.4]
+    }
+]
+
+
+params = []
+for p in params_:
+    for Ne in p["Ne"]:
+        for wd in p["wd"]:
+            for m in p["m"]:
+                for ef in p["ef"]:
+                    for g in p["g"]:
+                        for v in p["v"]:
+                            for w in p["w"]:
+                                for T in p["T"]:
+                                    for eta in p["eta"]:
+                                        params.append({
+                                                        "Ne": Ne,
+                                                        "T": T,
+                                                        "wd": wd,
+                                                        "s": p["s"],
+                                                        "m": m,
+                                                        "ef": ef,
+                                                        "g": g,
+                                                        "pre_d0": p["pre_d0"],
+                                                        "v": v,
+                                                        "w":  w,
[…]

### 2020-12-09 diagrammatics/j3_T/parameters.py

@@ -1,0 +1,55 @@
+import numpy as np
+
+u_temp = 116.032
+u_t = 6.58285E-2
+u_e = 10
+u_conductivity = 881.553 #Ohm^-1 cm-1
+meV_to_THz = 0.2417990504024
+u_w = u_e*meV_to_THz
+
+params_ = [
+    {
+        "Ne": [600],
+        "eta":  [0.01],
+        # "w":  np.array([0.3,0.4,0.5,0.6])/u_w,
+        "w":  np.linspace(0.1,0.85,16),
+        # "T": np.linspace(0,50,16)/u_temp,
+        "T": np.array([0.01, 15, 30, 50])/u_temp,
+        "wd":  [5],
+        "s": np.array([1,-1]),
+        "m": [ np.array([0.85, 1.38]) ],
+        "ef": [ np.array([290, 70]) ],
+        "g": [ np.array([10, 0.00001]), np.array([0.00001, 10]),  np.array([10,5]), np.array([0.00001,0.00001])],
+        # "g": [ np.array([10,5]) ],
+        "pre_d0": np.array([0.3,0.7]),
+        "v": [0.01,0.02,0.05,0.1,0.2,0.4]
+    }
+]
+
+
+params = []
+for p in params_:
+    for Ne in p["Ne"]:
+        for T in p["T"]:
+            for wd in p["wd"]:
+                for m in p["m"]:
+                    for ef in p["ef"]:
+                        for v in p["v"]:
+                            for w in p["w"]:
+                                for eta in p["eta"]:
+                                    for g in p["g"]:
+                                        params.append({
+                                                        "Ne": Ne,
+                                                        "T": T,
+                                                        "wd": wd,
+                                                        "s": p["s"],
+                                                        "m": m,
+                                                        "ef": ef,
+                                                        "g": g,
+                                                        "pre_d0": p["pre_d0"],
+                                                        "v": v,
+                                                        "w":  w,
+                                                        "eta": eta
+                                                    })
+
+print(len(params),'parameters generated')

### 2020-12-09 diagrammatics/plot-2D-Higgs.py

@@ -1,0 +1,280 @@
+
+#%%
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+import scipy
+from scipy.fftpack import fftfreq, fftshift
+import os
+from mpl_toolkits.mplot3d import Axes3D
+from cycler import cycler
+import matplotlib as mpl
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+folder = 'j3_g10_5_v0p2'
+folder = 'j3_g10_5_v0'
+folder = 'j3_g10_5_vall-highres'
+folder = 'j3_T'
+folder = 'j3_Higgs'
+# folder = 'j3_g10_5_vall'
+files = glob.glob(f'{folder}/*.pickle')
+
+save_plots = False
+
+plt.ion()
+
+u_t = 6.58285E-2
+u_e = 10
+u_conductivity = 881.553 #Ohm^-1 cm-1
+meV_to_THz = 0.2417990504024
+u_w = u_e*meV_to_THz
+u_temp = 116.032
+
[…]

### 2020-12-09 diagrammatics/plot-j3-Higgs.py

@@ -1,0 +1,279 @@
+
+#%%
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+import scipy
+from scipy.fftpack import fftfreq, fftshift
+import os
+from mpl_toolkits.mplot3d import Axes3D
+from cycler import cycler
+import matplotlib as mpl
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+folder = 'j3_g10_5_v0p2'
+folder = 'j3_g10_5_v0'
+folder = 'j3_g10_5_vall-highres'
+folder = 'j3_T'
+folder = 'j3_Higgs'
+# folder = 'j3_g10_5_vall'
+files = glob.glob(f'{folder}/*.pickle')
+
+save_plots = False
+
+plt.ion()
+
+u_t = 6.58285E-2
+u_e = 10
+u_conductivity = 881.553 #Ohm^-1 cm-1
+meV_to_THz = 0.2417990504024
+u_w = u_e*meV_to_THz
+u_temp = 116.032
+
[…]

### 2020-12-09 diagrammatics/plot-j3-w.py

@@ -1,0 +1,273 @@
+
+#%%
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+import scipy
+from scipy.fftpack import fftfreq, fftshift
+import os
+from mpl_toolkits.mplot3d import Axes3D
+from cycler import cycler
+import matplotlib as mpl
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+folder = 'j3_g10_5_v0p2'
+folder = 'j3_g10_5_v0'
+folder = 'j3_g10_5_vall-highres'
+folder = 'j3_T'
+# folder = 'j3_g10_5_vall'
+files = glob.glob(f'{folder}/*.pickle')
+
+save_plots = False
+
+plt.ion()
+
+u_t = 6.58285E-2
+u_e = 10
+u_conductivity = 881.553 #Ohm^-1 cm-1
+meV_to_THz = 0.2417990504024
+u_w = u_e*meV_to_THz
+u_temp = 116.032
+
+def savefig(fname, transparent=True):
[…]

### 2020-12-09 diagrammatics/plot-2D-Higgs.py
standard commit

@@ -98,183 +98,67 @@ for f in files:
 
 #%%
 
-v_list = [0.01,0.02,0.05,0.1,0.2,0.4]
-v_list = [0.02]
-w_list = np.array([0.3,0.4,0.5,0.6,0.7])
-w_list = [0.3]
-v = 0.02
-w_sel = 0.6
-gammas = [np.array([10, 0.00001]), np.array([0.00001, 10]),  np.array([10,5]), np.array([0.00001,0.00001])]
-gammas = [np.array([10, 0.0001]), np.array([0.00001, 10]),  np.array([10,5]), np.array([0.00001,0.00001])]
+v_list = [0.02,0.05,0.2,0.4]
 
-ii = 0
+w_list = np.linspace(0.00001,1,100)
+T_list = np.linspace(0.00001,50,100)/u_temp
+gammas = [ np.array([10, 0.001]), np.array([0.001, 10]),  np.array([10,5])]
+
+
+vind = 0
 for v in v_list:
-    ii += 1
-    kk = 0
-    for w_sel in w_list:
-
-        print(v, w_sel)
-        kk += 1
-
-        w = []
-        T = []
-        jh = []
-        jl = []
-        jl2 = []
-        jqp = []
-        durations = []
-        d_eq = []
+    vind += 1
+    gind = 0
+    for g in gammas:
+        gind += 1
+        JH2D = np.zeros((len(w_list),len(T_list)), dtype=complex)
         for r in res:
-            if True or r['v']==v and r['w'].real*u_w==w_sel and (r['g']==gammas[0]).all():
-                r2 = r
-                w.append(r['w'])
-                T.append(r['T'])
-
-                jh.append(r['jH'])
-                # jl.append(r['jL'])
-                # jl2.append(r['jL2'])
-                # jqp.append(r['jQP'])
-
-                d_eq.append(r['d_eq0'])
-
-                durations.append(r['duration'])
-        if len(w) == 0:
-            continue
-        r = r2
-
-        w = np.array(w)
-        T = np.array(T)
-        # jl = np.array(jl)
-        # jl2 = np.array(jl2)
-        jh = np.array(jh)
-        # jqp = np.stack(jqp)
-        d_eq = np.stack(d_eq)
-
-        if len(np.unique(w))>1:
-            x = np.copy(w)
-            xlabel = '$\omega$'
[…]

### 2020-12-10 diagrammatics/optical-conductivity-analytical.py
a

@@ -56,7 +56,7 @@ u_w = u_e*meV_to_THz
 u_temp = 116.032
 params_ = [
     {
-        "Ne": [300],
+        "Ne": [100],
         "tmin": [-80],
         "tmax": [300],
         # "tmax": [450],
@@ -66,8 +66,8 @@ params_ = [
         "s": np.array([1,-1]),
         "m": [ np.array([0.85, 1.38]) ],
         "ef": [ np.array([290, 70]) ],
-        # "g": [ np.array([10,5])],
-        "g": [ np.array([1e-1,1e-1])],
+        "g": [ np.array([10,5])],
+        # "g": [ np.array([1e-1,1e-1])],
         # "g": [ r['g'] ],
         "pre_d0": np.array([0.3,0.7]),
         # "pre_d0": np.array([0.29817841,0.70076507]),
@@ -707,7 +707,7 @@ print(np.max(np.abs(x100r)))
 
 #%% QP current third order (parallelized code)
 
-eta = 0.01
+eta = 0.06
 ws = np.linspace(0.1,0.85,20)
 
 # Higgs propagator
@@ -725,7 +725,8 @@ def multiprocess(ik):
     eek3 = eek[:,ik,:,ax]
     W13 = W12[:,:,ik]
     # Tr[g[ek, eek, z].g[ek3, eek3, z - w].g[ek, eek, z - 2 w].g[ek2, eek2, z + w]]
[…]

### 2020-12-10 multiband/pl_conductivity-twogaposcillations.py

@@ -1,0 +1,807 @@
+#%%
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+import scipy
+from scipy.fftpack import fftfreq, fftshift
+import os
+from mpl_toolkits.mplot3d import Axes3D
+from cycler import cycler
+import matplotlib as mpl
+
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a', '#f781bf', '#a65628', '#984ea3', '#999999', '#e41a1c', '#dede00']
+tableau10 = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f', '#edc948', '#b07aa1', '#ff9da7', '#9c755f']#, '#bab0ac']
+tableauCB = ['#1170aa', '#fc7d0b', '#a3acb9', '#57606c', '#5fa2ce', '#c85200', '#7b848f', '#a3cce9', '#ffbc79', '#c8d0d9']
+mpl.rcParams['axes.prop_cycle'] = cycler(color=tableau10)
+
+SMALL_SIZE = 11
+MEDIUM_SIZE = 13
+BIGGER_SIZE = 15
+
+plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
+
+folder = 'conductivity-quench2'
+files = glob.glob(f'{folder}/*.pickle')
+
+save_plots = False
+
+def savefig(fname, transparent=True):
+    if save_plots:
+        plt.savefig(fname, transparent=transparent)
+
+def nmax(x):
+    return np.max(np.abs(x))
+
+def nm(x):
+    return x / np.max(np.abs(x))
+
+def fft(t,f, inverse=False):
+    T = max(t) - min(t)
+    Nt = len(t)
+    dt = T/Nt
+
[…]

### 2020-12-10 multiband/pl_conductivity-twogaposcillations.py
a

@@ -432,26 +432,26 @@ def plotHiggsLeggett(r):
 
     color = 'tab:red'
     # ax2.set_ylabel('$\delta\\varphi, v=$'+str(np.round(v,3)), color=color)
-    ax2.tick_params(axis='y', labelcolor=color)
-    ax2.plot(w_*u_e*meV_to_THz, np.abs(dpw_), color=color, alpha=alpha, lw=lww)
+    # ax2.tick_params(axis='y', labelcolor=color)
+    # ax2.plot(w_*u_e*meV_to_THz, np.abs(dpw_), color=color, alpha=alpha, lw=lww)
     plt.xlim((0,3*u_e*meV_to_THz))
 
 
-    axl.set_ylabel('$\delta\\varphi, v=$'+str(np.round(v,3)))
-    axl.set_xlabel('$t$')
-    axl.axvspan(tleft,tright,facecolor='gray', alpha=0.3)
-    axl.plot(t,dphase, c='tab:red', lw=0.8, alpha=alpha)
+    # axl.set_ylabel('$\delta\\varphi, v=$'+str(np.round(v,3)))
+    # axl.set_xlabel('$t$')
+    # axl.axvspan(tleft,tright,facecolor='gray', alpha=0.3)
+    # axl.plot(t,dphase, c='tab:red', lw=0.8, alpha=alpha)
     axl.set_xlim((min(t)+10, tright))
 
     plt.tight_layout()
 
-    dpw_[w_<0] = 0
-    ileggett = np.argmax(np.abs(dpw_))
-    wlegget = w_[ileggett]
-    vallegget = np.abs(dpw_[ileggett])
+    # dpw_[w_<0] = 0
+    # ileggett = np.argmax(np.abs(dpw_))
+    # wlegget = w_[ileggett]
+    # vallegget = np.abs(dpw_[ileggett])
     # ax2.plot([wlegget], [vallegget], 'rx')
 
-    return wlegget
+    # return wlegget
 # plotHiggsLeggett(res[14])
 # plt.pause(0.01)
 # plt.figure()
@@ -744,6 +744,59 @@ cm = 'rainbow'
 def z(array):
     return zip(np.arange(len(array)), array)
 
+def plotHiggsLeggett(r):
+    d = r['d_2'].real
+    d_im = r['d_2'].real
+    t = r['t']
+    tau = r['tau']
+    e = r['efield']
+    w = r['w']
+    d_eq = r['d_eq'][:,0,0]
+    g = r['g']
[…]

### 2020-12-11 diagrammatics/plot-j3-w.py
standard commit

@@ -32,6 +32,7 @@ folder = 'j3_g10_5_v0p2'
 folder = 'j3_g10_5_v0'
 folder = 'j3_g10_5_vall-highres'
 folder = 'j3_T'
+folder = 'j3_QP'
 # folder = 'j3_g10_5_vall'
 files = glob.glob(f'{folder}/*.pickle')
 
@@ -101,6 +102,9 @@ v_list = [0.01,0.02,0.05,0.1,0.2,0.4]
 T_list = np.array([0.01, 15, 30, 50])/u_temp
 v = 0.02
 gammas = [np.array([10, 0.00001]), np.array([0.00001, 10]),  np.array([10,5]), np.array([0.00001,0.00001])]
+v_list = [0.02]
+gammas = [np.array([10,5])]
+T_list = [0.4/u_temp]
 
 ii = 0
 for v in v_list:

### 2020-12-12 singleband/pl_temp-dep.py
a

@@ -596,11 +596,11 @@ for temp in temps[[0,3,5,6,7]]:
     # plt.legend()
 
     plt.figure('cond-temp-imag')
-    plt.plot(wg*u_e*meV_to_THz,np.abs(c.imag), label=f'$T={np.round(temp*u_temp,1)}$ K')
+    plt.loglog(wg*u_e*meV_to_THz,np.abs(c.imag), label=f'$T={np.round(temp*u_temp,1)}$ K')
     plt.xlabel('Frequency (THz)')
-    plt.xlim((0,4*gap*u_e*meV_to_THz))
-    plt.ylim((0,60e4))
-    plt.ticklabel_format(axis="y", style="sci", scilimits=(2,4))
+    plt.xlim((0,6*gap*u_e*meV_to_THz))
+    plt.ylim((0,800e4))
+    # plt.ticklabel_format(axis="y", style="sci", scilimits=(2,4))
     plt.ylabel('$\sigma\,\'\'$ ($\Omega^{-1}$cm$^{-1}$)')
     # plt.legend()
 
@@ -617,7 +617,7 @@ savefig('cond-temp-real.pdf')
 plt.figure('cond-temp-imag')
 # plt.axvline(2*gap*u_e*meV_to_THz, c='k', lw=0.3)
 plt.tight_layout()
-savefig('cond-temp-imag.pdf')
+savefig('cond-temp-imag.pdf', plot=True)
 
 plt.figure('cond-temp-legend')
 savefig('cond-temp-legend2.pdf')

### 2020-12-14 diagrammatics/2d-leggett.py
standard commit

@@ -597,7 +597,7 @@ for ii in range(len(res)):
     plt.xlim((0,1.4))
     plt.ylim((0,50))
     plt.tight_layout()
-    plt.savefig(f'leggett-2d/{ii}_abs.png', dpi=800)
+    plt.savefig(f'leggett-2d/{ii}_abs.png', dpi=300)
     plt.savefig(f'leggett-2d/{ii}_abs.pdf', transparent=True)
 
     plt.figure('Leggett2d', figsize=(3,2.8))
@@ -612,5 +612,5 @@ for ii in range(len(res)):
     plt.xlim((0,1.4))
     plt.ylim((0,50))
     plt.tight_layout()
-    plt.savefig(f'leggett-2d/{ii}_phase.png', dpi=800)
+    plt.savefig(f'leggett-2d/{ii}_phase.png', dpi=300)
     plt.savefig(f'leggett-2d/{ii}_phase.pdf', transparent=True)

### 2020-12-14 diagrammatics/plot-2D-Higgs.py

@@ -106,14 +106,16 @@ gammas = [ np.array([10, 0.001]), np.array([0.001, 10]),  np.array([10,5])]
 
 
 vind = 0
-for v in v_list:
+# for v in v_list:
+for v in [0.4]:
     vind += 1
     gind = 0
-    for g in gammas:
+    # for g in gammas:
+    for g in gammas[0:1]:
         gind += 1
         JH2D = np.zeros((len(w_list),len(T_list)), dtype=complex)
         for r in res:
-            if r['v']==v and (r['g']==gammas[0]).all():
+            if r['v']==v and (r['g']==g).all():
                 def indexof(x, array):
                     return np.where(x==array)[0][0]
                 JH2D[indexof(r['w'].real, w_list), indexof(r['T'],T_list)] = r['jH']
@@ -132,7 +134,7 @@ for v in v_list:
         # plt.xlim((0,1.4))
         plt.ylim((0,50))
         plt.tight_layout()
-        plt.savefig(f'higgs-2d/v{vind}-g{gind}_abs.png', dpi=800)
+        plt.savefig(f'higgs-2d/v{vind}-g{gind}_abs.png', dpi=300)
         plt.savefig(f'higgs-2d/v{vind}-g{gind}_abs.pdf', transparent=True)
 
         plt.figure('Higgs-2d-phase', figsize=(3,2.8))
@@ -148,7 +150,7 @@ for v in v_list:
         # plt.xlim((0,1.4))
         plt.ylim((0,50))
         plt.tight_layout()
-        plt.savefig(f'higgs-2d/v{vind}-g{gind}_phase.png', dpi=800)
+        plt.savefig(f'higgs-2d/v{vind}-g{gind}_phase.png', dpi=300)
         plt.savefig(f'higgs-2d/v{vind}-g{gind}_phase.pdf', transparent=True)
 
 plt.figure('a')
